### 2019-09-24 albatros_paper.tex
updated with the jai files

\documentclass[12pt]{article}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[bottom]{footmisc}
%\usepackage{palatino}
%\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%\usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry}
%\usepackage[small,compact]{titlesec}
\usepackage{setspace}
\usepackage{hyperref,cleveref}
\usepackage{cite}
\usepackage{color}
%\usepackage{tikz}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{siunitx}
%\usepackage{natbib}
\usepackage[authoryear]{natbib}
\usepackage{gensymb}
%\usepackage{lipsum}
\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

\newenvironment{sciabstract}{%
\begin{quote} }
{\end{quote}}

\title{Title}

\author
{Author 1,$^{1\ast}$ Author 2,$^{1}$ Author 3$^{2}$\\
\\
\normalsize{$^{1}$Department, University and Address 1}\\
\normalsize{$^{2}$Department, University and Address 2}\\
}

\begin{document}

% Double-space the manuscript.

\baselineskip24pt

% Make the title.

\maketitle

\begin{sciabstract}
    The low frequency radio astronomy has the highest potential in discovering the history of the Universe, this includes observations of the first stars and the mapping of dark ages. The Array of Long Baseline Antennas for Taking Radio Observations from the Sub-Antarctic (ALBATROS) is a new interferometric array. It consists of autonomous antenna stations that will map the low-frequency sky from Marion Island. One autonomous station was deployed in Marion Island in April 2019. The operating frequency range is 1.2–81 MHz with baselines of $\approx$20 km. A two element inteferometer, the ALBATROS - Exploratory Gizmo on the Ground (ALBATROS-EGG) was deployed in Marion Island in April 2018. So far, the inteferometer is functional and is detecting different sources. \\
\end{sciabstract}

\section*{Introduction}
The 21 cm wavelength of hydrogen gas is being observed by several experiments which are modelled for the purpose of Hydrogen mapping in our Universe. This hydrogen line is a significant mechanism as it helps in the probing of the dark ages to the epoch of reionization (EoR)  \citep{2013PhRvD..87d3002L,2014ApJ...782...66P}.

Comprehensive reviews of experimental efforts exist elsewhere but none of them have made measurements at the lowest frequencies of $\lessapprox$ 30 MHz. This is due to the challenges namely, the ionospheric effects, radio frequency intereference (RFI), Galactic emission and instrumental systematics \citep{2018arXiv180609531P}. Two of these experiments represent the lowest frequencies measured to date (Reber’s antenna, RAE-B), and the other two represent the highest resolutions achieved in this frequency range (DRAO, OVRO-LWA).\\

Measurements of the radio sky at $\approx$ 100 MHz and below have the capability of unlocking the new observational window in the history of the universe. At the lowest frequencies (tens of MHz), subsequent observations may permit us to probe the cosmic "dark ages," one day, which is an epoch that is obscure to date \citep{2019arXiv190710853C}. The state of the art among ground-based measurements dates from the 1960s, when Grote Reber caught brief glimpses of the $\approx$ 2 MHz sky at low resolution. This paper will describe a new project that aims to map the low-frequency sky from Marion island using an array of autonomous antenna stations. The final array will consist of  $\approx$ 10 antennas operating at 1.2-81 MHz with baselines up to 20 km. A two-element pathfinder was deployed in April 2018, the first autonomous station was deployed in April 2019 and there'll be discussion of the preliminary observations and upcoming hardware development plans.

\section*{Overview of the Instrument}
	\citep{2019arXiv190804296K}

\section*{Pathfinder Installations and Preliminary Observations}

\section*{Future Work}

\newpage		
\bibliography{ALBATROS_Paper}		
\bibliographystyle{apalike}

\end{document}

### 2019-09-24 ws-jai.tex
updated with the jai files

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Trim Size : 11in x 8.5in
%% Text Area : 9.6in (include Runningheads) x 7in
%% ws-jai.tex, 26 April 2012
%% Tex file to use with ws-jai.cls written in Latex2E.
%% The content, structure, format and layout of this style file is the
%% property of World Scientific Publishing Co. Pte. Ltd.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%

%\documentclass[draft]{ws-jai}
\documentclass{ws-jai}
\usepackage[flushleft]{threeparttable}
\begin{document}

\catchline{}{}{}{}{} % Publisher's Area please ignore

\markboth{Author's Name}{Paper Title}

\title{Instructions for Typesetting Manuscript\\
Using \LaTeX\footnote{For the title, try not to use more than
three lines. Typeset the title in 11 pt Times Roman,
boldface, with the first letter of important words capitalized.}}

\author{First Author$^{2}$, Second Author$^{3}$, Third Author$^{3}$ and Fourth Author$^{4}$}

\address{
$^{2}$Department, University Name, City, State ZIP/Zone, Country, fauthor@university.com\\
$^{3}$Group, Company, Address, City, State ZIP/Zone, Country\\
$^{4}$Group, Company, Address, City, State ZIP/Zone, Country, fauthor@company.com
}

\maketitle

\corres{$^{2}$Corresponding author.}

\begin{history}
\received{(to be inserted by publisher)};
\revised{(to be inserted by publisher)};
\accepted{(to be inserted by publisher)};
\end{history}

\begin{abstract}
The abstract should summarize the context, content and conclusions
of the paper. It should not contain any references or displayed
equations. Typeset the abstract in 8~pt Times Roman with
baselineskip of 10 pt, making an indentation of 1.6~cm on the left
and right margins.
\end{abstract}

\keywords{Keyword 1; keyword 2; keyword 3.}

\section{The Main Text}
\noindent Contributions are to be in English. Authors are
encouraged to have their contribution checked for grammar.
American spelling should be used. Abbreviations are allowed but
should be spelt out in full when first used. Integers ten and
below are to be spelt out. Italicize foreign language phrases
({\it e.g.}~Latin, French).

The text is to be typeset in 11~pt Times Roman,
single-spaced with baselineskip of 13~pt. Text area is 17.8~cm (7
inches) across and 24.4~cm (9.6 inches) deep (including running
title). Final pagination and insertion of running titles will be
done by the publisher.

\section{Major Headings}
Major headings should be typeset in boldface, with the first
letter of important words capitalized.

\subsection{Subheadings}
Subheadings should be typeset in bold italics, with the first
letter of first word capitalized and the section number in
boldface.

\subsubsection{Sub-subheadings}
Typeset in italics (section number to be in roman) and capitalize
the first letter of the first word only.

\subsection{Numbering and spacing}
Sections, subsections and sub-subsections are numbered with Arabic
numerals. Use double spacing after major and subheadings, and
single spacing after sub-subheadings.

\section{Lists of Items}
Lists are broadly classified into four major categories that can
randomly be used as desired by the author:
\begin{alphlist}[(d)]
\item Numbered list.
\item Lettered list.
\item Unnumbered list.
\item Bulleted list.
\end{alphlist}

\subsection{Numbered and lettered list}

\begin{arabiclist}[(5)]
\item The \verb|\begin{arabiclist}[]| command is used for the arabic
number list (arabic numbers appearing within parenthesis), {\it e.g.},
(1), (2), {\it etc.}

\smallskip

\item The \verb|\begin{romanlist}[]| command is used for the roman
number list (roman numbers appearing within parenthesis), {\it e.g.}, (i),
(ii), {\it etc.}

\smallskip

\item The \verb|\begin{Romanlist}[]| command is used for the cap roman
\hbox{number list} (cap roman numbers appearing within parenthesis),
{\it e.g.}, (I), (II), {\it etc.}

\smallskip

\item The \verb|\begin{alphlist}[]| command is used for the alphabetic
list (alphabets appearing within parenthesis), {\it e.g.}, (a), (b), {\it etc.}

\smallskip

\item The \verb|\begin{Alphlist}[]| command is used for the cap
alphabetic list (cap alphabets appearing within parenthesis),
{\it e.g.}, (A), (B), {\it etc.}
\end{arabiclist}
Note: For all the above mentioned lists (with the exception of
alphabetic list), it is obligatory to enter the last entry's number
in the list within the square bracket, to enable unit alignment.

\subsection{Bulleted and unnumbered list}

\begin{enumerate}[-]
\item[-] The \verb|\begin{itemlist}| command is used for the bulleted list.

\smallskip

\item[-] The \verb|\begin{unnumlist}| command is used for creating the
  unnumbered list with the turnovers hangindent by 1\,pica.
\end{enumerate}

Lists may be laid out with each item marked by a dot:
\begin{itemlist}
\item item one
\item item two
\item item three.
\end{itemlist}

Items may also be numbered with lowercase Roman numerals:
\begin{romanlist}[(iii)]
\item item one
\item item two
    \begin{alphlist}[(b)]
    \item lists within lists can be numbered with lowercase Roman letters
    \item second item.
    \end{alphlist}
\item item three.
\end{romanlist}

\section{Theorems and Definitions}
\noindent{\bf Input:}

\begin{verbatim}
\begin{theorem}
We have $\# H^2 (M \supset N) < \infty$ for an inclusion ...
\end{theorem}
\end{verbatim}

\noindent{\bf Output:}

\begin{theorem}
We have $\# H^2 (M \supset N) < \infty$ for an inclusion $M \supset
N$ of factors of finite index.
\end{theorem}

\noindent{\bf Input:}

\begin{verbatim}
\begin{theorem}[Longo, 1998]
For a given $Q$-system...
\end{theorem}
\end{verbatim}

\noindent{\bf Output:}

\begin{theorem}[Longo, 1998]
For a given $Q$-system...
\end{theorem}

\subsection{Proofs}
The WSPC document styles also provide a predefined proof environment
for proofs. The proof \hbox{environment} produces the heading
`Proof' with appropriate spacing and punctuation. It also appends a
`Q.E.D.' symbol, $\blacksquare$, at the end of a proof, {\it e.g.}

\begin{verbatim}
\begin{proof}
This is just an example.
\end{proof}
\end{verbatim}

\noindent to produce

\begin{proof}
This is just an example.
\end{proof}

The proof environment takes an argument in curly
braces, which allows you to substitute a different name for the standard
`Proof'. If you want to display, `Proof of Lemma', then write {\it e.g.}

\begin{verbatim}
\begin{proof}[Proof of Lemma]
This is just an example.
\end{proof}
\end{verbatim}

\noindent produces

\begin{proof}[Proof of Lemma]
This is just an example.
\end{proof}

\section{Equations}
\noindent Displayed equations should be numbered consecutively in
each section, with the number set flush right and enclosed in
parentheses:
\begin{equation}
\mu(n, t) = \frac{\displaystyle\sum^\infty_{i=1} 1(d_i < t, N(d_i) = n)}
{\displaystyle\int^t_{\sigma=0} 1(N(\sigma) = n)d\sigma}\,\,
.\label{aba:eq1}
\end{equation}

\noindent Equations should be referred to in abbreviated form,
{\it e.g.}~``Eq.~(\ref{aba:eq1})'' or ``(2)''. In multiple-line equations,
the number should be given on the last line.

Displayed equations are to be centered on the page width. Standard
English letters like x are to appear as $x$ (italicized) in the
text if they are used as mathematical symbols. Punctuation marks
are used at the end of equations as if they appeared directly in
the text.

\section{Illustrations and Photographs}
Figures are to be inserted in the text nearest their
first reference. Please send one set of originals with copies. If the
publisher is required to reduce the figures, ensure that the
figures (including lettering and numbers) are large enough to be
clearly seen after reduction.

\begin{figure}[h]
\begin{center}
\includegraphics{jaif1} %100 percent
\end{center}
\caption{Labeled tree {\it T}.}
\label{aba:fig1}
\end{figure}

\begin{rotatefigure}
\begin{center}
\includegraphics[width=7in]{jaif2}
\end{center}
\caption{The bifurcating response curves of system
$\alpha=0.5, \beta=1.8; \delta=0.2, \gamma=0$: (a)
$\mu=-1.3$; and (b) $\mu=0.3$.}
\label{aba:fig2}
\end{rotatefigure}

Figures are to be sequentially numbered with Arabic
numerals. The caption must be placed below the figure. For those
figures with multiple parts which appear on different pages, it is
best to place the full caption below the first part, and have
{\it e.g.}~``Fig.~1 ({\it continued})'' below the last part. Typeset in
9 pt Times Roman with baselineskip of 11 pt. Use double spacing
between a caption and the text that follows immediately.
Previously published material must be accompanied by written
permission from the author and publisher.

Very large figures and tables should be placed on a separate page
by themselves. Landscape tables and figures can be typeset with the following environments:
\begin{itemlist}
\item \verb|rotatetable| and
\item \verb|rotatefigure|.
\end{itemlist}

\section{Tables}
Tables should be inserted in the text as close to the
point of reference as possible. Some space should be left above
and below the table. Tables should be numbered sequentially in the
text with Arabic numerals. Captions are to be centered above the
tables. Typeset tables and captions in 9 pt Times Roman with
baselineskip of 11 pt.

If tables need to extend over to a second page, the continuation
of the table should be preceded by a caption, {\it e.g.}~``Table~\ref{aba:tbl1} ({\it
continued})''.

\begin{wstable}[h]
\caption{Comparison of acoustic for frequencies for piston-cylinder problem.}
\begin{tabular}{@{}cccc@{}} \toprule
Piston mass & Analytical frequency & TRIA6-$S_1$ model &
\% Error \\
& (Rad/s) & (Rad/s) \\ \colrule
1.0\hphantom{00} & \hphantom{0}281.0 & \hphantom{0}280.81 & 0.07 \\
0.1\hphantom{00} & \hphantom{0}876.0 & \hphantom{0}875.74 & 0.03 \\
0.01\hphantom{0} & 2441.0\tnote{a} & 2441.0\hphantom{0} & 0.0\hphantom{0} \\
0.001 & 4130.0\tnote{b} & 4129.3\hphantom{0} & 0.16\\ \botrule
\end{tabular}
\begin{tablenotes}
\item[a] Sample table notes.
\item[b] Sample table notes.
\end{tablenotes}
\label{aba:tbl1}
\end{wstable}

\def\p{\phantom{$-$}}
\def\pc{\phantom{,}}
\def\p0{\phantom{0}}
\begin{rotatetable}
\caption{Positive values of $X_0$ by eliminating $Q_0$ from Eqs.~(15)
and (16) for different values of the parameters $f_0$, $\lambda_0$
and $\alpha_0$ in various dimension.}
\begin{tabular}{@{}ccccccccccc@{}}
\toprule\\[-6pt]
$f_0$ &$\lambda_0$ &$\alpha_0$
&\multicolumn{8}{c}{Positive roots ($X_0$)}\\[3pt]
\hline\\[-6pt]
&& &4D &5D &6D &7D &8D &10D &12D &16D\\[3.5pt]
\hline\\[-6pt]
\phantom{1}$-0.033$ &0.034 &\phantom{0}0.1\phantom{.01} &6.75507\p0
&4.32936\p0 &3.15991\p0 &2.44524\p0
&1.92883\p0 &0.669541 &--- &---\\[3.5pt]
&&&1.14476\pc\p0 &1.16321\pc\p0 &1.1879\pc\phantom{00}
&1.22434\pc\p0 &1.29065\pc\p0
&0.415056\pc\\[3.5pt]
\phantom{1}$-0.1$\phantom{33} &0.333 &\phantom{0}0.2\phantom{.01}
&3.15662\p0 &1.72737\p0 &--- &--- &--- &--- &--- &---\\[3.5pt]
&&&1.24003\pc\p0 &1.48602\pc\p0\\[3.5pt]
\phantom{1}$-0.301$ &0.302 &0.001
&2.07773\p0 &--- &--- &--- &--- &--- &--- &---\\[3.5pt]
&&&1.65625\pc\p0\\[3.5pt]
\phantom{1}$-0.5$\phantom{01} &0.51\phantom{2} &\phantom{0}0.001
&--- &--- &--- &--- &--- &--- &--- &---\\[3.5pt]
$\phantom{1-}$0.1\phantom{01} &0.1\phantom{02}
&\phantom{0}2\phantom{.001} &1.667\phantom{000}
&1.1946\phantom{00,}
&--- &--- &--- &--- &--- &---\\[3.5pt]
&&&0.806578\pc &0.858211\pc\\[3.5pt]
$\phantom{1-}$0.1\phantom{01} &0.1\phantom{33} &10\phantom{.001}
&0.463679\pc &0.465426\pc &0.466489\pc &0.466499\pc
&0.464947\pc &0.45438\pc\p0 &0.429651\pc &0.35278\pc\\[3.5pt]
$\phantom{1-}$0.1\phantom{01} &1\phantom{.333}
&\phantom{0}0.2\phantom{01}
&--- &--- &--- &--- &--- &--- &--- &---\\[3.5pt]
$\phantom{1-}$0.1\phantom{01} &5\phantom{.333}
&\phantom{0}5\phantom{.001}
&--- &--- &--- &--- &--- &--- &--- &---\\[3.5pt]
$\phantom{-0}$1\phantom{.033} &0.001 &\phantom{0}2\phantom{.001}
&0.996033 &0.968869 &0.91379\p0 &0.848544&0.783787 &0.669541
&0.577489 &---\\[3.5pt]
&&&0.414324\pc &0.41436\pc\p0 &0.414412\pc &0.414489\pc &0.414605\pc
&0.415056\pc &0.416214\pc\\[3.5pt]
\phantom{10}\phantom{.033} &0.001 &\phantom{0}0.2\phantom{01}
&0.316014 &0.309739 &--- &--- &--- &--- &--- &---\\[3.5pt]
&&&0.275327\pc &0.275856\pc\\[3.5pt]
\phantom{10}\phantom{.033} &0.1\phantom{33}
&\phantom{0}5\phantom{.001} &0.089435\pc &0.089441\pc &0.089435\pc
&0.089409\pc &0.08935\pc\p0
&0.089061\pc &0.088347\pc &0.084352\pc\\[3.5pt]
\phantom{10}\phantom{.033} &1\phantom{.333}
&\phantom{0}3\phantom{.001} &0.128192\pc &0.128966\pc &0.19718\p0
&0.169063 &0.142103
&--- &--- &---\\[3.5pt]
&&&& &0.41436\pc\p0 &0.414412\pc &0.414489\pc\\[3pt]
\Hline
\end{tabular}
\label{aba:tbl2}
\end{rotatetable}

By using \verb|wstable| environment, long captions will be justified to the table width while the short or single line captions are centered.

For most tables, the horizontal rules are obtained by:

\begin{tabular}{ll}
{\bf toprule} & one rule at the top\\
{\bf colrule}& one rule separating column heads from data cells\\
{\bf botrule}& one bottom rule\\
{\bf Hline} & one thick rule at the top and bottom of the tables with multiple column heads\\
\end{tabular}

To avoid the rules sticking out at either end
of the table, add \verb|@{}| before the first and after the last descriptors, {\it e.g.}
{@{}llll@{}}. Please avoid vertical rules in tables.
But if you think the vertical rule is a must,
you can use the standard \LaTeX{} \verb|tabular| environment.
Headings which span for more than one column should be set using
\verb|\multicolumn{#1}{#2}{#3}| where \verb|#1| is the number of
columns to be spanned, \verb|#2| is the argument for the alignment
of the column head which may be either {c} --- for center
alignment; {l} --- for left alignment; or {r} --- for right
alignment, as desired by the users. Use {c} for column heads as
this is the WS style and \verb|#3| is the heading.

\section{Cross-references}
Use \verb|\label| and \verb|\ref| for cross-references to
equations, figures, tables, sections, subsections, {\it etc.}, instead
of plain numbers. Every numbered part to which one wants to refer,
should be labeled with the instruction \verb|\label|.
For example:
\begin{verbatim}
\begin{equation}
\mu(n, t)=\frac{\sum\limits^\infty_{i=1}1 (d_i < t, N(d_i)=n)}...\label{aba:eq1}
\end{equation}
\end{verbatim}
With the instruction \verb|\ref| one can refer to a numbered part
that has been labeled:
\begin{verbatim}
..., see also Eq. (\ref{aba:eq1})
\end{verbatim}

The \verb|\label| instruction should be typed
\begin{itemlist}
\item immediately after (or one line below), but not inside the argument of
a number-generating instruction such as \verb|\section| or \verb|\caption|, {\it e.g.}:
\verb|\caption{ ... caption ... }\label{aba:fig1}|.
\item roughly in the position where the number appears, in environments
such as an equation,
\item labels should be unique, {\it e.g.}, equation 1 can be labeled as
\verb|\label{aba:eq1}|, where `{\tt aba}' is author's initial and
`{\tt eq1}' the equation number.
\end{itemlist}

\section{Footnotes}
Footnotes should be numbered sequentially in superscript
lowercase alphabets.\footnote{Footnotes should be
typeset in 8~pt Times Roman at the bottom of the page.}

\section{References}
References cited in the text should be placed within parentheses and stated as (surname of author(s), year of
publication), {\it e.g.}, \cite{Golub89} and, with three
or more authors, \cite{blain02}. If the reference reads as part of
the sentence, the square brackets enclose only the year of
publication, {\it e.g.}, ``According to \citet{Golub89}, \ldots''

\section*{Note Added}
A note can be added before Acknowledgments.

\section*{Acknowledgments}
This part should come before References. Funding information may also be included here.

\section*{Appendices}
Appendices should be used only
when absolutely necessary. They should come immediately before
References.

\appendix{} % optional title or empty braces must
If there is more than one appendix, number them alphabetically.

\noindent
\begin{equation}
\mu(n, t) = \frac{\displaystyle\sum^\infty_{i=1} 1(d_i < t, N(d_i) = n)}
{\displaystyle\int^t_{\sigma=0} 1(N(\sigma) = n)d\sigma}\,\,
.\label{aba:a.1}
\end{equation}
Number displayed equations occurring in the appendix as (\ref{aba:a.1}),
(A.2), {\it etc.}

\begin{theorem}
Sample.
\end{theorem}

\begin{lemma}
Sample.
\end{lemma}

\section*{References}
\noindent A complete list of references cited, arranged in
alphabetical order according to the surname of the first author,
should be provided. References by the same author will follow a
chronological sequence, {\it i.e.}, \cite{Lie00} precedes \cite{Lie01}.
Article titles should be stated in full but standard abbreviations
should be used for journal names. Typeset reference in 10 pt Times
Roman, single spaced with baselineskip of 12 pt.

\begin{thebibliography}{9}

\bibitem[Blain {\it et al.}(2002)]{blain02} Blain, A. W., Smail, I., Ivison, R., Kneib, J.-P., Frayer, D. T. [2002] {\it Phys. Rep.} {\bf 369}, 111.

\bibitem[Devlin M. {\it et al.} (2001)]{devlin01} Devlin, M. [2001]  {\it Deep Millimetre Surveys, Implications for Galaxy Formation and Evolution}, eds. Lowenthal, J., Hughes, D. H. (World Scientific, Singapore), p. 59 (astro-ph/0012327).

\bibitem[Capak {\it et al.}(2011)]{capak2011} Capak, P., {\it et al.} [2011] {\it Nature} {\bf 470}, 233.

\bibitem[Coppin {\it et al.}(2010)]{coppin2010} Coppin, K. E. K., {\it et al.} [2010] {\it MNRAS} {\bf 407}, L103.

\bibitem[Golub \& Van Loan(1989)]{Golub89} Golub, G. H. \& Van Loan, C. F. [1989] {\it Matrix Computations}, 2nd Ed. (Johns Hopkins University Press, USA).

\bibitem[Greenhill {et al.}(2004a)]{green04a} Greenhill, L. J., Gezari, D. Y., Danchi, W. C., {\it et al.} [2004a], {\it ApJ\/} {\bf 605}, L57.

\bibitem[Greenhill {et al.}(2004b)]{green04b} Greenhill, L. J., Reid, M. J., Chandler, C. J., Diamond, P. J. \& Elitzur, M. [2004b] ``Star Formation at High Angular Resolution,'' in {\it IAU Symp. 221}, eds. Burton, M., Jayawardhana, R. \& Bourke, T. (Cambridge University Press, Cambridge), p.~155.

\bibitem[Lie \& Wang(2000)]{Lie00} Lie, D. Y. C. \& Wang, K. L. [2000]
{\it Handbook of Advanced Electronic and Photonic Devices and
Materials}, ed.~Nalwa, H. S. (Academic Press, San Diego), p.~1.

\bibitem[Lie \& Wang(2001)]{Lie01} Lie, D. Y. C. \& Wang, K. L. [2001]
{\it Semiconductors and Semimetals} {\bf 73}, eds.~Willardson, R.
\& Weber, E. (Academic Press, San Diego), p.~151.

\bibitem[Parssinen {\it et al.}(1999)]{Par99} P\"arssinen, A., Jussila, J., Ryyn\"anen, J.,
Sumanen, L. \& Halonen, K. A. I. [1999] {\it IEEE J. Solid-State
Circuits} {\bf 34}, 1893.

\bibitem[Zhu~\& Leung, 1999]{EKF_DrLeung3}
Zhu, Z. \& Leung, H. [1999] {\it IEEE Trans. Circ. Syst.-I\/$:$ Fund. Th. Appl.} {\bf 46},
1320.

\end{thebibliography}
\end{document}

### 2019-09-25 albatros_paper.tex
Add files via upload

@@
-\documentclass[12pt]{article}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Trim Size : 11in x 8.5in
+%% Text Area : 9.6in (include Runningheads) x 7in
+%% ws-jai.tex, 26 April 2012
+%% Tex file to use with ws-jai.cls written in Latex2E.
+%% The content, structure, format and layout of this style file is the
+%% property of World Scientific Publishing Co. Pte. Ltd.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+
+%\documentclass[draft]{ws-jai}
+\documentclass{ws-jai}
+\usepackage[flushleft]{threeparttable}
 \usepackage{siunitx}
 \usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage[bottom]{footmisc}
-%\usepackage{palatino}
-%\usepackage{wrapfig}
-\usepackage{graphicx}
-\usepackage{url}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-%\usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry}
-%\usepackage[small,compact]{titlesec}
-\usepackage{setspace}
-\usepackage{hyperref,cleveref}
-\usepackage{cite}
-\usepackage{color}
-%\usepackage{tikz}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{siunitx}
-%\usepackage{natbib}
-\usepackage[authoryear]{natbib}
 \usepackage{gensymb}
-%\usepackage{lipsum}
-\topmargin 0.0cm
-\oddsidemargin 0.2cm
-\textwidth 16cm 
-\textheight 21cm
-\footskip 1.0cm
-
-\newenvironment{sciabstract}{%
-\begin{quote} }
-{\end{quote}}
-
-\title{Title}
-
-\author
-{Author 1,$^{1\ast}$ Author 2,$^{1}$ Author 3$^{2}$\\
-\\
-\normalsize{$^{1}$Department, University and Address 1}\\
-\normalsize{$^{2}$Department, University and Address 2}\\
-}
+\usepackage[colorlinks=true,allcolors=blue]{hyperref}
 
@@
 
-% Double-space the manuscript.
+\catchline{}{}{}{}{} % Publisher's Area please ignore
 
-\baselineskip24pt
+\markboth{Author's Name}{Paper Title}
 
-% Make the title.
+\title{Instructions for Typesetting Manuscript\\
+Using \LaTeX\footnote{For the title, try not to use more than
+three lines. Typeset the title in 11 pt Times Roman,
+boldface, with the first letter of important words capitalized.}}
+
+\author{First Author$^{2}$, Second Author$^{3}$, Third Author$^{3}$ and Fourth Author$^{4}$}
+
+\address{
+$^{2}$Department, University Name, City, State ZIP/Zone, Country, fauthor@university.com\\
+$^{3}$Group, Company, Address, City, State ZIP/Zone, Country\\
+$^{4}$Group, Company, Address, City, State ZIP/Zone, Country, fauthor@company.com
+}
 
@@
 
-\begin{sciabstract}
+\corres{$^{2}$Corresponding author.}
+
+\begin{history}
+\received{(to be inserted by publisher)};
+\revised{(to be inserted by publisher)};
+\accepted{(to be inserted by publisher)};
+\end{history}
+
+\begin{abstract}
 The low frequency radio astronomy has the highest potential in discovering the history of the Universe, this includes observations of the first stars and the mapping of dark ages.
@@
 One autonomous station was deployed in Marion Island in April 2019.
-The operating frequency range is 1.2–81 MHz with baselines of $\approx$20 km.
+The operating frequency range is \SIrange{1.2}{81}{\MHz} with baselines of $\approx \SI{20}{\km}$.
 A two element inteferometer, the ALBATROS - Exploratory Gizmo on the Ground (ALBATROS-EGG) was deployed in Marion Island in April 2018.
@@
 \\
-\end{sciabstract}
+\end{abstract}
 
-\section*{Introduction}
-The 21 cm wavelength of hydrogen gas is being observed by several experiments which are modelled for the purpose of Hydrogen mapping in our Universe.
-This hydrogen line is a significant mechanism as it helps in the probing of the dark ages to the epoch of reionization (EoR)  \citep{2013PhRvD..87d3002L,2014ApJ...782...66P}.
+\keywords{Keyword 1; keyword 2; keyword 3.}
 
-Comprehensive reviews of experimental efforts exist elsewhere but none of them have made measurements at the lowest frequencies of $\lessapprox$ 30 MHz.
-This is due to the challenges namely, the ionospheric effects, radio frequency intereference (RFI), Galactic emission and instrumental systematics \citep{2018arXiv180609531P}.
-Two of these experiments represent the lowest frequencies measured to date (Reber’s antenna, RAE-B), and the other two represent the highest resolutions achieved in this frequency range (DRAO, OVRO-LWA).\\
+\section{Introduction}
+\noindent The \SI{21}{\cm} wavelength of hydrogen gas is being observed by several experiments which are modelled for the purpose of Hydrogen mapping in our Universe.
+This hydrogen line is a significant mechanism as it helps in the probing of the dark ages to the epoch of reionization (EoR) \cite{2013PhRvD..87d3002L,2014ApJ...782...66P}.\\
+
+Comprehensive reviews of experimental efforts exist elsewhere but none of them have made measurements at the lowest frequencies of $\lessapprox$ \SI{30}{\MHz}.
+This is due to the challenges namely, the ionospheric effects, radio frequency intereference (RFI), Galactic emission and instrumental systematics which is non transparent below \SI{10}{\MHz} \cite{2019JAI.....850004P}.
+Two of these experiments represent the lowest frequencies measured to date (Reber’s antenna, RAE-2), and the other two represent the highest resolutions achieved in this frequency range (DRAO, OVRO-LWA).\\
+
+Grote Reber came up with the state of art by constructing a telescope which operated at very low frequencies between 0.52 MHz and 2.1 MHz, which had 192 dipoles.
+At \SI{2.1}{\MHz} it had a resolution of as low as $\approx$ 5 \degree.
+The key map of the sky was created by this experiment at \SI{2.1}{\MHz}.
+He also mentioned that his measurements were influenced by galactic emission and the ionosphere \cite{article, 1988A&A...195..372W}.
+The Radio Astronomoy Explorer-2 (RAE-2) have very low operating frequency ranges between \SIrange{0.025}{13}{\MHz}, it main science goal was to do radio astronomy evaluation of our Galaxy (the Milkyway), the Sun and all the planets including Earth.
+The resolution of this experiment is $\approx$ 10 \degree at \SI{4.7}{\MHz} \cite{1975A&A....40..365A}.
+Both of these experiments made very low resolution measurements.\\
+
+The experiments which made the high resolution measurements are the  Dominion Radio Astrophysical Observatory (DRAO) \SI{22}{\MHz} telescope and the OVRO-LWA \SI{36}{\MHz} experiment.
+The DRAO telescope operated at \SI{22}{\MHz} and its resolution ranges between $\approx$ \SIrange{1.1}{1.7}{\degree}.
+Its main science goal was to measure the emission from discrete sources and to observe our Galaxy's emission from its environment \cite{1999A&AS..137....7R}.
+The OVRO-LWA operates at frequency ranges of 36.528 MHz and 73.152 MHz.
+At these frequencies it has an angular resolution of \SI{15}{\arcminute} \cite{2018AJ....156...32E}.
+ALBATROS aims at attempting to do high resolution measurements at a frequency of $<$20 MHz which do not yet exist.\\
 
 Measurements of the radio sky at $\approx$ 100 MHz and below have the capability of unlocking the new observational window in the history of the universe.
-At the lowest frequencies (tens of MHz), subsequent observations may permit us to probe the cosmic "dark ages," one day, which is an epoch that is obscure to date \citep{2019arXiv190710853C}.
-The state of the art among ground-based measurements dates from the 1960s, when Grote Reber caught brief glimpses of the $\approx$ 2 MHz sky at low resolution.
+At the lowest frequencies (tens of MHz), subsequent observations may permit us to probe the cosmic "dark ages," one day, which is an epoch that is obscure to date \cite{2019arXiv190710853C, 2019arXiv190804296K}.
 This paper will describe a new project that aims to map the low-frequency sky from Marion island using an array of autonomous antenna stations.
@@
 
-\section*{Overview of the Instrument}
-	\citep{2019arXiv190804296K}
+\section{Overview of the Instrument}
 
-\section*{Pathfinder Installations and Preliminary Observations}
+\cite{2019arXiv190804296K}
 
-\section*{Future Work}
+\section{Pathfinder Installations and Preliminary Observations}
 
-\newpage		
-\bibliography{ALBATROS_Paper}		
-\bibliographystyle{apalike}
+\section{Future Work}
 
+\section*{Acknowledgments}
+
+\begin{thebibliography}{9}
+
+\bibitem[Liu {et al.}(2013)]{2013PhRvD..87d3002L} Liu, A., Pritchard, J.~R., Tegmark, M., {\it et al.} [2013], {\bf 87}, 043002
+
+\bibitem[Pober {et al.}(2014)]{2014ApJ...782...66P} Pober, J.~C., Liu, A., Dillon, J.~S., {\it et al.} [2014], {\bf 782}, 66
+
+\bibitem[Philip {et al.}(2019)]{2019JAI.....850004P} Philip, L., Abdurashidova, Z., Chiang, H.~C., {\it et al.} [2019], Journal of Astronomical Instrumentation, {\bf 8}, 19500
+
+\bibitem[Chen {et al.}(2019)]{2019arXiv190710853C} Chen, X., Burns, J., Koopmans, L., {\it et al.} [2019], arXiv e-prints, arXiv:1907.10853
+
+\bibitem[Koopmans {et al.}(2019)]{2019arXiv190804296K} Koopmans, L., Barkana, R., Bentum, M., {\it et al.} [2019], arXiv e-prints, arXiv:1908.04296
+
+\bibitem[Weiler {et al.}(1988)]{1988A&A...195..372W} Weiler, K.~W., Johnston, K.~J., Simon, R.~S., {\it et al.} [1988], {\it aap\/}, {\bf 195}, 372
+
+\bibitem[George {et al.}(2018)] {article} George, M., Orchiston, W., Wielebinsk, R., {\it et al.} [2018], Journal of Astronomical History and Heritage, {\bf 21}, 37
+
+\bibitem[Alexander et al.(1975)]{1975A&A....40..365A} Alexander, J.~K., Kaiser, M.~L., Novaco, J.~C., et al.\ 1975, {\it aap\/}, {\bf 40}, 365
+
+\bibitem[Roger et al.(1999)]{1999A&AS..137....7R} Roger, R.~S., Costain, C.~H., Landecker, T.~L., et al.\ 1999, {\it aaps\/}, {\bf 137}, 7
+
+\bibitem[Eastwood et al.(2018)]{2018AJ....156...32E} Eastwood, M.~W., Anderson, M.~M., Monroe, R.~M., et al.\ 2018, {\it aj\/}, {\bf 156}, 32
+
+\end{thebibliography}
 \end{document}

### 2019-09-30 albatros_paper.tex
Add files via upload
Add files via upload
Still working on reshuffling text according to the outline, changing and/or updating some figures.

@@
 \usepackage[colorlinks=true,allcolors=blue]{hyperref}
+\usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage[bottom]{footmisc}
+\usepackage{url}
 
@@
 A two element inteferometer, the ALBATROS - Exploratory Gizmo on the Ground (ALBATROS-EGG) was deployed in Marion Island in April 2018.
-So far, the inteferometer is functional and is detecting different sources.
 \\
@@
 
-\cite{2019arXiv190804296K}
+%The ALBATROS-EGG schematic is shown in \autoref{Fig:ALBATROS-EGG Schematic}.
+The system uses the dual polarisation dipole like antennas which are omidirectionally patterned.
+The front end electonics (FEE) are configured in a printed circuit board (PCB) which makes it easy for them to be mounted on the supporting structure of the antennas.
+The gain of the FEE is $\approx$35 dB and its noise figure (NF) ranges between $\approx$2.7 dB and 2.9 dB.
+From the FEE PCB, a coaxial cable sends the signal thnrough to the bias tee which extracts both the RF and the DC without any degradation.
+\newline The high pass and the low pass filter rejects the low frequency signals and high frequency signals respectively.
+The signal is then amplified by a $\approx$20 dB amplifier which then send the amplified signals to the Smart Network ADC Processor (SNAP) board which does the readouts and does a series of processing step.
+The raspberry pi interacts with the SNAP board for data storage.
+%
+%
+%\begin{figure}[!ht]
+%	\begin{center}
+%		\includegraphics[width=0.9\linewidth]{Figures/ALBATROS-EGG-Schematic.PNG}
+%		\caption{ALBATROS - EGG pathfinder schematic which consists of the dual polarisation antennas, the 35 dB gain FEE, the 100 m coaxial cable which connects the FEE to the back end Faraday cage which comprises of the bias tee, HPF, LPF, amplifier, snap board and regulated voltage outputs which are powered by 12 VDC batteries.}
+%		\label{Fig:ALBATROS-EGG Schematic}
+%	\end{center}
+%\end{figure}
+%
+%
+%
+The ALBATROS-EGG is a two element inteferometer which is making exploratory measurements at a frequency range of \SI{1.2}{MHz}- \SI{81}{MHz} separated by a baseline of \SI{110}{m}.
+It was deployed in Marion Island in April 2018 as shown in \autoref{Fig:ALBATROS-EGG}.
+This experiment (ALBATROS-EGG) uses the Long Wavelength Array (LWA) hardware.\\
+
+The final project (ALBATROS) will consist of autonomous antenna stations that will map the low frequency sky.
+Since these experiments are exploratory, they are taking steps towards achieving the future objective of probing the Dark Ages.The ALBATROS stations (huts) will be separated by baselines of \SI{\approx {20}}{km} as shown in \autoref{Fig:Marion}.
+The two-element interferomentric pathfinder is not yet operating autonomously, it uses the direct cross correlation technique whereas the yet to be ALBATROS will write the lowest 10 - 20 MHz baseband to disk then gets correlated afterwards.
+One ALBATROS fully autonomous station was deployed in Marion Island in April 2019 as shown in \autoref{Fig:autonomous}.
+\\
+
+	\begin{figure}[h]
+		\begin{center}
+			\includegraphics[width=0.7\linewidth]{Figures/ALBATROS-EGG.PNG}
+			\caption{The ALBATROS-EGG pathfinder on Marion Island.
+The pathfinder comprises two dual-polarization antennas separated by roughly 110 m on an east-west baseline.
+Long coaxial cables connect the antennas to	an orange shipping container that houses the readout electronics and serves as our "command module".}
+			\label{Fig:ALBATROS-EGG}
+		\end{center}
+	\end{figure}
+
+The single antenna analog signal chain is shown in \autoref{Fig:Signal Chain}.
+The components of the system are discussed in detail as per the block diagram illustrated in \autoref{Fig:Signal Chain}.
+This analog signal chain is a an illustration of how the first autonomous station is configured.
+There might be changes to the block diagram at a later stage should there be a need to revise it for the stations.
+
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[width=1.0\linewidth]{Figures/Signal-Chain.png}
+		\caption{Analog signal chain block diagram for the newly deployed autonomous station the ALBATROS}
+		\label{Fig:Signal Chain}
+	\end{center}
+\end{figure}
+
+\subsection{Antenna}	
+The system uses the dual polarisation dipole like antennas which are omidirectionally patterned.
+The dipole like antennas are of high preference for this project because they are relatively simple and they are omnidirectionally patterned \cite{Memo28}.
+
+\subsection{Front End Electronics (FEE)}
+All the front end components were incorporated for in a double sided printed circuit board (PCB) as shown in \autoref{Fig:Balun} and the block diagram is shown in \autoref{Fig:Balun Schematic}.
+The Monolithic Microwave Integrated Circuits (MMICs) is the used design for the PCB.
+One side of the PCB is populated with components and the other side is a solid copper ground plane aperiodically stitched to the grounded copper on the side populated with components.
+The receiver system is made up of the active balun, filter and the gain stage that connects to the \SI{100}{m} coaxial cable which is connected to the back end \cite{2012PASP..124.1090H}.\\
+The input impedance (Z\textsubscript{o}) of \SI{50}{\ohm} is introduced to the dipole by the active balun.
+The signal is then fed through an amplifier which amplifies it by +24 dB of gain.
+The balanced signal is then converted to unbalanced through a 180 \degree hybrid coupler.
+The band pass filter (BPF) receives the single ended signal in order for it to reject all the frequencies which are not within the range of interest.
+The signal gets fed to a second amplifier which again amplies it by +24 dB of gain and the output impedance of the FEE is matched to a \SI{50}{\ohm} coaxial cable.
+The bias tee is responsible for providing power to the FEE and extracts the RF signal by the use of the coaxial cable.
+This unit has an overall gain of $\approx$ 35 dB and an overall noise figure of $\approx$ 2.7 dB to $\approx$ 2.9 dB \cite{Memo35}.
+
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[width=0.5\linewidth]{Figures/balun.jpg}
+		\caption{Unenclosed FEE mounted on the ALBATROS-EGG antenna supporting structure.} 
+		\label{Fig:Balun}
+	\end{center}
+\end{figure}
+
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[width=0.7\linewidth]{Figures/Balun_Block.png}
+		\caption{One Polarisation Block Diagram of the FEE \cite{2012PASP..124.1090H}}
+		\label{Fig:Balun Schematic}
+	\end{center}
+\end{figure}
+
+\subsection{Back End Electronics}	
+The back end electronics consists of the bias tee, high pass filter (HPF), low pass filter (LPF) and the Smart Network ADC Processor (SNAP) board. \\
+
+\textbf{Bias Tee} - The bias tee is a network made up of 3 ports \footnote{https://www.pasternack.com/bias-tees-category.aspx}.
+It is used to extract the RF signal from a \SI{100}{m} LMR400 coaxial cable which has a nominal attenuation of \SI{\approx 0.4}{dB/\SI{100}{m}} - \SI{\approx 3.7}{dB/\SI{100}{m}} at \SI{1.2}{MHz} - \SI{81}{MHz} respectively \footnote{https://www.timesmicrowave.com/documents/resources/LMR-400.pdf}.
+The bias tee which is used is the Mini Circuits device ZFBT-4R2GW-FT+ which operates between \SI{0.14}{MHz} - \SI{4200}{MHz}.
+It has an insertion loss of 0.16 dB at centre frequency of  \SI{\approx 10}{MHz} as per the datasheet \footnote{https://www.minicircuits.com/pdfs/ZFBT-4R2GW-FT+.pdf}.\\
+
+\textbf{HPF} - The HPF rejects any signals with low frequencies and allow through signals with high frequencies \footnote{http://www.learningaboutelectronics.com/Articles/High-pass-filter.php}.
+The HPF used is the ZFHP-1R2+ Mini Circuits device which operates between  \SI{1.2}{MHz} - \SI{800}{MHz}.
+It has a nominal insertion loss of $\approx$ 0.2 dB at centre frequency of  \SI{\approx10}{MHz} as per the datasheet \footnote{https://www.minicircuits.com/pdfs/ZFHP-1R2+.pdf}.\\
+
+\textbf{LPF} - The LPF rejects all signals with high frequencies and allows all signals with low frequencies \footnote{http://www.learningaboutelectronics.com/Articles/Low-pass-filter.php}.
+The LPF used is the SLP-90+ Mini Circuits device which operates between \SI{1}{MHz} - \SI{400}{MHz}.
+It has a nominal insertion loss of $\approx$ 0.14 dB at the centre frequency of  \SI{\approx 10}{MHz} \footnote{https://www.minicircuits.com/pdfs/SLP-90+.pdf}.\\
+
+\textbf{Amplifier} - The amplifier at the backend amplifies the signal which is sent through to the snapboard by the gain of +20 dB.
+The amplifier used is the Mini Circuits device ZX60-V63+ which operates at a frequency range of \SI{0.05}{GHz} - \SI{6}{GHz}.
+It has a noise figure of $\approx$ 3.6 dB at its lowest operating frequency of \SI{\approx 50}{MHz} \footnote{https://www.minicircuits.com/pdfs/ZX60-V63+.pdf}.\\
+
+\textbf{SNAP Board} - The SNAP board used is specified by Xilinx Inc.
+\footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}.
+The  SNAP board samples the signals it receives by 250 Msampl/s using internal ADCs where the signal of the clock is from the Valon 5007 frerquency synthesizer module.
+This creates a frequency range between 0 - 125 MHz which contains 2048 channels.
+A SNAP board interacts with a raspberry pi and that is where the data is saved.\\
+
+\subsection{Solar Power Supply System}
 
@@
 
+	\begin{figure}[h]
+		\begin{center}
+			\includegraphics[width=1\linewidth]{Figures/autonomous.jpg}
+			\caption{}
+			\label{Fig:autonomous}
+		\end{center}
+	\end{figure}
+
 \section{Future Work}
+
+Marion Island huts which are potential stations for the ALBATROS have a ring-like pattern which is appropriate for imaging and produces a FWHM synthesized beam of 8' at 5 MHz as shown in \autoref{Fig:10}.
+This beam is a notable advancement over existing measurements to date.The ALBATROS main goal thus far will be to attempt to map high resolutions at low frequencies which is crucial before moving to measuring the dark ages.
+
+\begin{figure}[h]
+	\centering
+	\begin{subfigure}[t]{0.5\textwidth}
+		\centering
+		\includegraphics[width=.9\linewidth]{Figures/site.PNG}
+		\caption{Marion Island huts which are potential stations for the ALBATROS. The ring-like pattern is appropriate for imaging and produces a FWHM synthesized beam of 8' at 5 MHz.}
+		\label{Fig:Marion}
+	\end{subfigure}%
+	~~~			
+	\begin{subfigure}[t]{0.5\textwidth}
+		\centering
+		\includegraphics[width=.9\linewidth]{Figures/beam.png}
+		\caption{Omnidirectional, dome shaped beam pattern which promises an improved resolution over the existing experiments to date.}
+		\label{Fig:beam}
+	\end{subfigure}
+	\caption{Potential stations and a beam encouraging enough to implement ALBATROS experiment}
+	\label{Fig:10}
+\end{figure}
 
@@
 
+\bibitem[Alexander et al.(1975)]{1975A&A....40..365A} Alexander, J.~K., Kaiser, M.~L., Novaco, J.~C., et al.\ 1975, {\it aap\/}, {\bf 40}, 365
+
+\bibitem[Chen {et al.}(2019)]{2019arXiv190710853C} Chen, X., Burns, J., Koopmans, L., {\it et al.} [2019], arXiv e-prints, arXiv:1907.10853
+
+\bibitem[Eastwood et al.(2018)]{2018AJ....156...32E} Eastwood, M.~W., Anderson, M.~M., Monroe, R.~M., et al.\ 2018, {\it aj\/}, {\bf 156}, 32
+
+\bibitem[Ellingson and Kramer (2004)]{Memo28} Ellingson, S.~W., {Kramer}, W.~T. \ 2004, {\it Long Wavelength Array Memo (28)}
+
+\bibitem[George {et al.}(2018)] {article} George, M., Orchiston, W., Wielebinsk, R., {\it et al.} [2018], Journal of Astronomical History and Heritage, {\bf 21}, 37
+
+\bibitem[Hicks et al.(2012)]{2012PASP..124.1090H} Hicks, B.~C., Paravastu-Dalal, N., Stewart, K.~P., et al.\ 2012, {\it pasp\/}, {\bf 124}, 1090
+
+\bibitem[Koopmans {et al.}(2019)]{2019arXiv190804296K} Koopmans, L., Barkana, R., Bentum, M., {\it et al.} [2019], arXiv e-prints, arXiv:1908.04296
+
 \bibitem[Liu {et al.}(2013)]{2013PhRvD..87d3002L} Liu, A., Pritchard, J.~R., Tegmark, M., {\it et al.} [2013], {\bf 87}, 043002
+
+\bibitem[Philip {et al.}(2019)]{2019JAI.....850004P} Philip, L., Abdurashidova, Z., Chiang, H.~C., {\it et al.} [2019], Journal of Astronomical Instrumentation, {\bf 8}, 19500
 
@@
 
-\bibitem[Philip {et al.}(2019)]{2019JAI.....850004P} Philip, L., Abdurashidova, Z., Chiang, H.~C., {\it et al.} [2019], Journal of Astronomical Instrumentation, {\bf 8}, 19500
+\bibitem[Ray et al.(2006)]{Memo35} Ray, P.~S., Ellingson, S.~W., Fisher R., {\it et al.} [2006] {\it Long Wavelength Array Memo (35)}
 
-\bibitem[Chen {et al.}(2019)]{2019arXiv190710853C} Chen, X., Burns, J., Koopmans, L., {\it et al.} [2019], arXiv e-prints, arXiv:1907.10853
-
-\bibitem[Koopmans {et al.}(2019)]{2019arXiv190804296K} Koopmans, L., Barkana, R., Bentum, M., {\it et al.} [2019], arXiv e-prints, arXiv:1908.04296
+\bibitem[Roger et al.(1999)]{1999A&AS..137....7R} Roger, R.~S., Costain, C.~H., Landecker, T.~L., et al.\ 1999, {\it aaps\/}, {\bf 137}, 7
 
@@
 
-\bibitem[George {et al.}(2018)] {article} George, M., Orchiston, W., Wielebinsk, R., {\it et al.} [2018], Journal of Astronomical History and Heritage, {\bf 21}, 37
-
-\bibitem[Alexander et al.(1975)]{1975A&A....40..365A} Alexander, J.~K., Kaiser, M.~L., Novaco, J.~C., et al.\ 1975, {\it aap\/}, {\bf 40}, 365
-
-\bibitem[Roger et al.(1999)]{1999A&AS..137....7R} Roger, R.~S., Costain, C.~H., Landecker, T.~L., et al.\ 1999, {\it aaps\/}, {\bf 137}, 7
-
-\bibitem[Eastwood et al.(2018)]{2018AJ....156...32E} Eastwood, M.~W., Anderson, M.~M., Monroe, R.~M., et al.\ 2018, {\it aj\/}, {\bf 156}, 32
-
 \end{thebibliography}

### 2019-10-08 albatros_paper.tex
Add files via upload

@@
 
-\textbf{Bias Tee} - The bias tee is a network made up of 3 ports \footnote{https://www.pasternack.com/bias-tees-category.aspx}.
-It is used to extract the RF signal from a \SI{100}{m} LMR400 coaxial cable which has a nominal attenuation of \SI{\approx 0.4}{dB/\SI{100}{m}} - \SI{\approx 3.7}{dB/\SI{100}{m}} at \SI{1.2}{MHz} - \SI{81}{MHz} respectively \footnote{https://www.timesmicrowave.com/documents/resources/LMR-400.pdf}.
+\textbf{Bias Tee} - It is used to extract the RF signal from a \SI{100}{m} LMR400 coaxial cable which has a nominal attenuation of \SI{\approx 0.4}{dB/\SI{100}{m}} - \SI{\approx 3.7}{dB/\SI{100}{m}} at \SI{1.2}{MHz} - \SI{81}{MHz} respectively \footnote{https://www.timesmicrowave.com/documents/resources/LMR-400.pdf}.
 The bias tee which is used is the Mini Circuits device ZFBT-4R2GW-FT+ which operates between \SI{0.14}{MHz} - \SI{4200}{MHz}.

### 2019-11-05 albatros_paper.tex
Add files via upload

@@
 One side of the PCB is populated with components and the other side is a solid copper ground plane aperiodically stitched to the grounded copper on the side populated with components.
-The receiver system is made up of the active balun, filter and the gain stage that connects to the \SI{100}{m} coaxial cable which is connected to the back end \cite{2012PASP..124.1090H}.\\
+The receiver system is made up of the active balun, filter and the gain stage that connects to the \SI{100}{\metre} coaxial cable which is connected to the back end \cite{2012PASP..124.1090H}.\\
 The input impedance (Z\textsubscript{o}) of \SI{50}{\ohm} is introduced to the dipole by the active balun.
-The signal is then fed through an amplifier which amplifies it by +24 dB of gain.
+The signal is then fed through an amplifier which amplifies it by \SI{+24}{\decibel} of gain.
 The balanced signal is then converted to unbalanced through a 180 \degree hybrid coupler.
 The band pass filter (BPF) receives the single ended signal in order for it to reject all the frequencies which are not within the range of interest.
-The signal gets fed to a second amplifier which again amplies it by +24 dB of gain and the output impedance of the FEE is matched to a \SI{50}{\ohm} coaxial cable.
+The signal gets fed to a second amplifier which again amplies it by \SI{+24}{\decibel} of gain and the output impedance of the FEE is matched to a \SI{50}{\ohm} coaxial cable.
 The bias tee is responsible for providing power to the FEE and extracts the RF signal by the use of the coaxial cable.
-This unit has an overall gain of $\approx$ 35 dB and an overall noise figure of $\approx$ 2.7 dB to $\approx$ 2.9 dB \cite{Memo35}.
+This unit has an overall gain of $\approx$ \SI{35}{\decibel} and an overall noise figure of $\approx$ \SI{2.7}{\decibel} to $\approx$ \SI{2.9}{\decibel} \cite{Memo35}.
 
@@
 
-\textbf{Bias Tee} - It is used to extract the RF signal from a \SI{100}{m} LMR400 coaxial cable which has a nominal attenuation of \SI{\approx 0.4}{dB/\SI{100}{m}} - \SI{\approx 3.7}{dB/\SI{100}{m}} at \SI{1.2}{MHz} - \SI{81}{MHz} respectively \footnote{https://www.timesmicrowave.com/documents/resources/LMR-400.pdf}.
+\textbf{Bias Tee} - It is used to extract the RF signal from a \SI{100}{\metre} LMR400 coaxial cable which has a nominal attenuation of \SI{\approx 0.4}{\decibel/\SI{100}{m}} - \SI{\approx 3.7}{dB/\SI{100}{\metre}} at \SI{1.2}{MHz} - \SI{81}{MHz} respectively \footnote{https://www.timesmicrowave.com/documents/resources/LMR-400.pdf}.
 The bias tee which is used is the Mini Circuits device ZFBT-4R2GW-FT+ which operates between \SI{0.14}{MHz} - \SI{4200}{MHz}.
-It has an insertion loss of 0.16 dB at centre frequency of  \SI{\approx 10}{MHz} as per the datasheet \footnote{https://www.minicircuits.com/pdfs/ZFBT-4R2GW-FT+.pdf}.\\
+It has an insertion loss of \SI{0.16}{\decibel} at centre frequency of  \SI{\approx 10}{MHz} as per the datasheet \footnote{https://www.minicircuits.com/pdfs/ZFBT-4R2GW-FT+.pdf}.\\
 
@@
 The HPF used is the ZFHP-1R2+ Mini Circuits device which operates between  \SI{1.2}{MHz} - \SI{800}{MHz}.
-It has a nominal insertion loss of $\approx$ 0.2 dB at centre frequency of  \SI{\approx10}{MHz} as per the datasheet \footnote{https://www.minicircuits.com/pdfs/ZFHP-1R2+.pdf}.\\
+It has a nominal insertion loss of $\approx$ \SI{0.2}{\decibel} at centre frequency of  \SI{\approx10}{MHz} as per the datasheet \footnote{https://www.minicircuits.com/pdfs/ZFHP-1R2+.pdf}.\\
 
@@
 The LPF used is the SLP-90+ Mini Circuits device which operates between \SI{1}{MHz} - \SI{400}{MHz}.
-It has a nominal insertion loss of $\approx$ 0.14 dB at the centre frequency of  \SI{\approx 10}{MHz} \footnote{https://www.minicircuits.com/pdfs/SLP-90+.pdf}.\\
+It has a nominal insertion loss of $\approx$ \SI{0.14}{\decibel} at the centre frequency of  \SI{\approx 10}{MHz} \footnote{https://www.minicircuits.com/pdfs/SLP-90+.pdf}.\\
 
-\textbf{Amplifier} - The amplifier at the backend amplifies the signal which is sent through to the snapboard by the gain of +20 dB.
+\textbf{Amplifier} - The amplifier at the backend amplifies the signal which is sent through to the snapboard by the gain of \SI{+20}{\decibel}.
 The amplifier used is the Mini Circuits device ZX60-V63+ which operates at a frequency range of \SI{0.05}{GHz} - \SI{6}{GHz}.
-It has a noise figure of $\approx$ 3.6 dB at its lowest operating frequency of \SI{\approx 50}{MHz} \footnote{https://www.minicircuits.com/pdfs/ZX60-V63+.pdf}.\\
+It has a noise figure of $\approx$ \SI{3.6}{\decibel} at its lowest operating frequency of \SI{\approx 50}{MHz} \footnote{https://www.minicircuits.com/pdfs/ZX60-V63+.pdf}.\\
 
@@
 The  SNAP board samples the signals it receives by 250 Msampl/s using internal ADCs where the signal of the clock is from the Valon 5007 frerquency synthesizer module.
-This creates a frequency range between 0 - 125 MHz which contains 2048 channels.
+This creates a frequency range between \SI{0}{MHz} - \SI{125}{MHz} which contains 2048 channels.
 A SNAP board interacts with a raspberry pi and that is where the data is saved.\\
@@
 \subsection{Solar Power Supply System}
+The power system of the ALBATROS-EGG uses generators to charge the batteries manually every once in a number of days.
+From the observation that has been made, the batteries take $\approx$ 2 days to discharge to a point where the system shuts down.
+Because of the weather conditions in Marion Island, an individual can sometimes be unable to go to the site to charge the batteries, which means that if the weather does not allow, the system can be shut down for a long period.
+Thus, a solar power system solution was introduced to the ALBATROS so that the system can continously run without having to be recharged manually and often.\\
+
+The ALBATROS system is powered using \SI{24}{\volt} power which is stored and provided by two series-connected \SI{12}{\volt} deep-cycle lead-acid storage batteries.
+This power comes from the solar panel array consisting of nine flexible solar panels, each with a standard test condition capacity of \SI{110}{\watt}.
+The solar panel type is SunPower SPE-E-Flex-110.
+The panels are grouped in three parallel connected strings of three panels.
+Each group of three is mounted on its own structure.
+The panels include diodes to bypass shaded or defective cells, and also to prevent backwards current flow in the event an entire string of three panels is not illuminated while the others are producing power.
+\\
+
+The Victron BlueSolar MPPT 50$\vert$35 charge controller outputs a data packet every second, to an Arduino based data logger, which controls a switch that determines when the rest of the system runs.
+It also converts the solar panel voltage to \SI{24}{\volt} to control the battery charging.
+The observed parameters are then stored to the raspberry pi.
 
 \section{Pathfinder Installations and Preliminary Observations}
+\subsection{Marion Island}
+ Marion Island is a research location managed by the South African National Antarctic Programme (SANAP) and is located at \ang{46;54;45}S, \ang{37;44;37}E on the sub-antarctic of the Southern Indian Ocean.
+It is $\approx$\SI{2000}{\kilo\metre} from the nearest continental landmass which is also an approximate maximum distance for meteor scattering.
+The island has an area of \SI{290}{\kilo\metre\squared} and is only accessible once in April of every year by means of the S.
+A.
+Agulhas vessel owned by the Department of Environmental Affairs.
+
+ \subsection{Experiments}
+
+ The ALBATROS main goal thus far will be to attempt to map high resolutions at low frequencies which is crucial before moving in to the cosmology of measuring the dark ages.
 

### 2019-11-17 albatros_paper.tex
Add files via upload

@@
 
-%The ALBATROS-EGG schematic is shown in \autoref{Fig:ALBATROS-EGG Schematic}.
-The system uses the dual polarisation dipole like antennas which are omidirectionally patterned.
+The ALBATROS-EGG is a two element inteferometer which is making exploratory measurements at a frequency range of \SI{1.2}{MHz}- \SI{81}{MHz} separated by a baseline of \SI{110}{m} as shown in \autoref{Fig:ALBATROS-EGG}.
+It was deployed in Marion Island in April 2018.
+Its schematic is shown in \autoref{Fig:ALBATROS-EGG Schematic}.
+The system uses the dual polarisation dipole like antennas which are omidirectional patterned.
 The front end electonics (FEE) are configured in a printed circuit board (PCB) which makes it easy for them to be mounted on the supporting structure of the antennas.
-The gain of the FEE is $\approx$35 dB and its noise figure (NF) ranges between $\approx$2.7 dB and 2.9 dB.
-From the FEE PCB, a coaxial cable sends the signal thnrough to the bias tee which extracts both the RF and the DC without any degradation.
-\newline The high pass and the low pass filter rejects the low frequency signals and high frequency signals respectively.
+From the FEE PCB, a coaxial cable sends the signal through to the bias tee which extracts both the RF and the DC without any degradation.
+\\
+
+The high pass and the low pass filter rejects the low frequency signals and high frequency signals respectively.
 The signal is then amplified by a $\approx$20 dB amplifier which then send the amplified signals to the Smart Network ADC Processor (SNAP) board which does the readouts and does a series of processing step.
-The raspberry pi interacts with the SNAP board for data storage.
-%
-%
-%\begin{figure}[!ht]
-%	\begin{center}
-%		\includegraphics[width=0.9\linewidth]{Figures/ALBATROS-EGG-Schematic.PNG}
-%		\caption{ALBATROS - EGG pathfinder schematic which consists of the dual polarisation antennas, the 35 dB gain FEE, the 100 m coaxial cable which connects the FEE to the back end Faraday cage which comprises of the bias tee, HPF, LPF, amplifier, snap board and regulated voltage outputs which are powered by 12 VDC batteries.}
-%		\label{Fig:ALBATROS-EGG Schematic}
-%	\end{center}
-%\end{figure}
-%
-%
-%
-The ALBATROS-EGG is a two element inteferometer which is making exploratory measurements at a frequency range of \SI{1.2}{MHz}- \SI{81}{MHz} separated by a baseline of \SI{110}{m}.
-It was deployed in Marion Island in April 2018 as shown in \autoref{Fig:ALBATROS-EGG}.
-This experiment (ALBATROS-EGG) uses the Long Wavelength Array (LWA) hardware.\\
+The raspberry pi interacts with the SNAP board for data storage.\\
 
-The final project (ALBATROS) will consist of autonomous antenna stations that will map the low frequency sky.
-Since these experiments are exploratory, they are taking steps towards achieving the future objective of probing the Dark Ages.The ALBATROS stations (huts) will be separated by baselines of \SI{\approx {20}}{km} as shown in \autoref{Fig:Marion}.
-The two-element interferomentric pathfinder is not yet operating autonomously, it uses the direct cross correlation technique whereas the yet to be ALBATROS will write the lowest 10 - 20 MHz baseband to disk then gets correlated afterwards.
-One ALBATROS fully autonomous station was deployed in Marion Island in April 2019 as shown in \autoref{Fig:autonomous}.
-\\
+\begin{figure}[h!]
+	\begin{center}
+		\includegraphics[width=0.55\linewidth]{Figures/ALBATROS-EGG-Schematic.PNG}
+		\caption{ALBATROS - EGG pathfinder schematic which consists of the dual polarisation antennas, the 35 dB gain FEE, the 100 m coaxial cable which connects the FEE to the back end Faraday cage which comprises of the bias tee, HPF, LPF, amplifier, snap board and regulated voltage outputs which are powered by 12 VDC batteries.}
+		\label{Fig:ALBATROS-EGG Schematic}
+	\end{center}
+\end{figure}
 
@@
 
+The final project (ALBATROS) will consist of autonomous antenna stations that will map the low frequency sky.
+Since these experiments are exploratory, they are taking steps towards achieving the future objective of probing the Dark Ages.The ALBATROS stations (huts) will be separated by baselines of \SI{\approx {20}}{km} as shown in \autoref{Fig:Marion}.
+The two-element interferomentric pathfinder is not yet operating autonomously, it uses the direct cross correlation technique whereas the yet to be ALBATROS will write the lowest 10 - 20 MHz baseband to disk then gets correlated afterwards.
+One ALBATROS fully autonomous station was deployed in Marion Island in April 2019 as shown in \autoref{Fig:autonomous}.
+\\
+
 The single antenna analog signal chain is shown in \autoref{Fig:Signal Chain}.
 The components of the system are discussed in detail as per the block diagram illustrated in \autoref{Fig:Signal Chain}.
-This analog signal chain is a an illustration of how the first autonomous station is configured.
+This analog signal chain is an illustration of how the first autonomous station is configured.
 There might be changes to the block diagram at a later stage should there be a need to revise it for the stations.
@@
 	\begin{center}
-		\includegraphics[width=1.0\linewidth]{Figures/Signal-Chain.png}
+		\includegraphics[width=0.7\linewidth]{Figures/Signal-Chain.png}
 		\caption{Analog signal chain block diagram for the newly deployed autonomous station the ALBATROS}
@@
  \subsection{Experiments}
-
- The ALBATROS main goal thus far will be to attempt to map high resolutions at low frequencies which is crucial before moving in to the cosmology of measuring the dark ages.
+ The ALBATROS-EGG shown in \autoref{Fig:ALBATROS-EGG} was installed on the PRI\textsuperscript{z}M \cite{2019JAI.....850004P} site which is located at \ang{46;53;13}S, \ang{37;49;10.7}E and the first ALBATROS station shown in \autoref{Fig:autonomous} is located \ang{46;52.205;}S, \ang{37;50.612;}E.\\
 
@@
 		\begin{center}
-			\includegraphics[width=1\linewidth]{Figures/autonomous.jpg}
+			\includegraphics[width=0.7\linewidth]{Figures/autonomous.jpg}
 			\caption{}
 			\label{Fig:autonomous}
+		\end{center}
+	\end{figure}
+
+ \subsection{Preliminary Observations}
+
+\autoref{Fig:auto} and \autoref{Fig:fringes} shows the initial results from the two interferometric array.
+These results are an encouraging factor to proceed with the development of the autonomous stations.\autoref{Fig:auto} shows the raw ALBATROS-EGG autospectra which where the waterfall plot was taken from one polarization (pol0) over an interval of 3 days.
+The Galaxy rising/setting is clearly visible in the structure.
+There are also ripples in frequency because of uncalibrated data, and the ripples arise from reflections in the cables.
+There is a qualitative difference between daytime and nighttime data and this shows that the contamination from shortwave radio drops off significantly at night, when the ionosphere becomes quieter.
+
+\begin{figure}[h!]
+	\begin{center}
+		\includegraphics[width=0.8\linewidth]{Figures/Raw-ALBATROS-autospectra.PNG}
+		\caption{Raw ALBATROS-EGG Autospectra}
+		\label{Fig:auto}
+	\end{center}
+\end{figure}
+
+\autoref{Fig:fringes} shows the first fringes that were detected by the the ALBATROS-EGG.
+It is dinstictly visible from \autoref{Fig:fringes} that fringes show recurrent structure down to a frequency of as low as 10 MHz without data processing or data cuts.
+
+\begin{figure}[ht!]
+	\begin{center}
+		\includegraphics[width=0.7\linewidth]{Figures/First-fringes-of-ALBATROS-EGG.PNG}
+		\caption{First Fringes from ALBATROS-EGG}
+		\label{Fig:fringes}
 	\end{center}

### 2020-03-30 albatros_paper.tex
HCC: starting to edit intro text

@@
 
-\title{Instructions for Typesetting Manuscript\\
-Using \LaTeX\footnote{For the title, try not to use more than
-three lines. Typeset the title in 11 pt Times Roman,
-boldface, with the first letter of important words capitalized.}}
+\title{The Array of Long-Baseline Antennas for Taking Radio
+  Observations from the Sub-Antarctic}
 
@@
 \section{Introduction}
-\noindent The \SI{21}{\cm} wavelength of hydrogen gas is being observed by several experiments which are modelled for the purpose of Hydrogen mapping in our Universe.
-This hydrogen line is a significant mechanism as it helps in the probing of the dark ages to the epoch of reionization (EoR) \cite{2013PhRvD..87d3002L,2014ApJ...782...66P}.\\
+
+Measurements of redshifted \SI{21}{\cm} emission of neutral hydrogen
+across a wide range of radio frequencies have the potential to
+elucidate the universe's history from the cosmic ``dark ages'' up to
+the formation of large-scale structures (see,
+e.g.,~\citep{ska_physics,2013PhRvD..87d3002L,2014ApJ...782...66P}.
+The dark ages, which occurred after recombination and correspond to a
+period when the universe was filled with neutral hydrogen, are
+unexplored to date and represent one of the final observational
+frontiers in cosmology.  This epoch contains a potential wealth of
+cosmological information~\citep{loeb_zaldarriaga}, but the required
+redshifted frequencies of $\lesssim 30$~MHz are exceptionally
+difficult to observe.  The primary challenges include Galactic
+foreground emission, ionospheric interference, and terrestrial
+radio-frequency interference (RFI). \\
+
+% At the very lowest frequencies, the state of the art among
+% ground-based measurements dates from the 1950s, when Reber and Ellis
+% caught brief glimpses of the $\sim 2$~MHz sky at low
+% resolution~\citep{reber}.  The lowest frequency to date for
+% high-resolution sky imaging has been achieved by the LWA, which
+% reported observations at 36.5~MHz using only 28 hours of
+% data~\citep{lwa}.  Preliminary observations from Marion Island
+% (\S\ref{s:dark_method}) suggest that despite the present-day RFI
+% environment, low-frequency observations may still be accessible from
+% carefully selected locations and with new technology developments.
 

### 2020-04-01 albatros_paper.tex
HCC: added new ALBATROS 2-element schematic
HCC fixed duplicate text in 2-element figure
HCC overhauled intro, working on pathfinder text

@@
 
+% Define stuff here
+\def\albatros{ALBATROS}
+
 \begin{document}
@@
 
-\markboth{Author's Name}{Paper Title}
+\markboth{Author's Name}{ALBATROS instrument}
 
@@
 
-\keywords{Keyword 1; keyword 2; keyword 3.}
+\keywords{cosmology: observations; dark ages; instrumentation: interferometers}
 
@@
 frontiers in cosmology.  This epoch contains a potential wealth of
-cosmological information~\citep{loeb_zaldarriaga}, but the required
-redshifted frequencies of $\lesssim 30$~MHz are exceptionally
-difficult to observe.  The primary challenges include Galactic
-foreground emission, ionospheric interference, and terrestrial
-radio-frequency interference (RFI). \\
+cosmological information~\citep{loeb_zaldarriaga, 2019arXiv190710853C,
+  2019arXiv190804296K}, but the required redshifted frequencies of
+$\lesssim 30$~MHz are exceptionally difficult to observe.  The primary
+experimental challenges include Galactic foreground emission,
+ionospheric interference, and terrestrial radio-frequency interference
+(RFI).
 
-% At the very lowest frequencies, the state of the art among
-% ground-based measurements dates from the 1950s, when Reber and Ellis
-% caught brief glimpses of the $\sim 2$~MHz sky at low
-% resolution~\citep{reber}.  The lowest frequency to date for
-% high-resolution sky imaging has been achieved by the LWA, which
-% reported observations at 36.5~MHz using only 28 hours of
-% data~\citep{lwa}.  Preliminary observations from Marion Island
-% (\S\ref{s:dark_method}) suggest that despite the present-day RFI
-% environment, low-frequency observations may still be accessible from
-% carefully selected locations and with new technology developments.
+Very few experiments have measured the radio sky at $\lesssim 30$~MHz.
+Comprehensive reviews exist elsewhere ({\bf citation?}), and here, we
+highlight only a few specific examples.  At the very lowest
+frequencies, the state of the art among ground-based measurements
+dates from the 1950s, when Reber and Ellis caught brief glimpses of
+the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an array of
+192~dipoles~\citep{reber, article, 1988A&A...195..372W}.  A few
+space-based missions have also performed measurements at similarly low
+frequency ranges; for example, the Radio Astronomy Explorer-2 operated
+at \SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
+\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
+resolution finer than few-degree scales exist only at higher
+frequencies.  For example, the Dominion Radio Astrophysical
+Observatory surveyed the northern sky at \SI{22}{\MHz} with
+\SIrange{1.1}{1.7}{\degree} resolution~\citep{1999A&AS..137....7R},
+and most recently, the Owens Valley Long Wavelength Array mapped the
+sky with \SI{15}{\arcminute} resolution between 36.528~MHz and
+73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
+list is not comprehensive, it does illustrate the dearth of
+information about the $\lesssim 30$~MHz sky and the lack of high
+resolution measurements at the lowest frequencies.
 
-Comprehensive reviews of experimental efforts exist elsewhere but none of them have made measurements at the lowest frequencies of $\lessapprox$ \SI{30}{\MHz}.
-This is due to the challenges namely, the ionospheric effects, radio frequency intereference (RFI), Galactic emission and instrumental systematics which is non transparent below \SI{10}{\MHz} \cite{2019JAI.....850004P}.
-Two of these experiments represent the lowest frequencies measured to date (Reber’s antenna, RAE-2), and the other two represent the highest resolutions achieved in this frequency range (DRAO, OVRO-LWA).\\
+Preliminary observations from Marion
+Island~\citep{2019JAI.....850004P} suggest that despite the
+present-day RFI environment, low-frequency observations may still be
+accessible from carefully selected locations and with new technology
+developments.  In this paper, we present the Array of Long Baseline
+Antennas for Taking Radio Observations from the Sub-Antarctic
+(\albatros), a new experimental effort that aims to map the
+low-frequency sky using an array of autonomous antenna stations.  We
+describe the overall instrument design and preliminary measurements
+from engineering runs that were performed on Marion Island during
+2018--2019.
 
-Grote Reber came up with the state of art by constructing a telescope which operated at very low frequencies between 0.52 MHz and 2.1 MHz, which had 192 dipoles.
-At \SI{2.1}{\MHz} it had a resolution of as low as $\approx$ 5 \degree.
-The key map of the sky was created by this experiment at \SI{2.1}{\MHz}.
-He also mentioned that his measurements were influenced by galactic emission and the ionosphere \cite{article, 1988A&A...195..372W}.
-The Radio Astronomoy Explorer-2 (RAE-2) have very low operating frequency ranges between \SIrange{0.025}{13}{\MHz}, it main science goal was to do radio astronomy evaluation of our Galaxy (the Milkyway), the Sun and all the planets including Earth.
-The resolution of this experiment is $\approx$ 10 \degree at \SI{4.7}{\MHz} \cite{1975A&A....40..365A}.
-Both of these experiments made very low resolution measurements.\\
+\section{ALBATROS overview}
 
-The experiments which made the high resolution measurements are the  Dominion Radio Astrophysical Observatory (DRAO) \SI{22}{\MHz} telescope and the OVRO-LWA \SI{36}{\MHz} experiment.
-The DRAO telescope operated at \SI{22}{\MHz} and its resolution ranges between $\approx$ \SIrange{1.1}{1.7}{\degree}.
-Its main science goal was to measure the emission from discrete sources and to observe our Galaxy's emission from its environment \cite{1999A&AS..137....7R}.
-The OVRO-LWA operates at frequency ranges of 36.528 MHz and 73.152 MHz.
-At these frequencies it has an angular resolution of \SI{15}{\arcminute} \cite{2018AJ....156...32E}.
-ALBATROS aims at attempting to do high resolution measurements at a frequency of $<$20 MHz which do not yet exist.\\
+{\bf Write text here about the overall final configuration.  Describe
+  the site, show synthesized beam, discuss high level system
+  requirements (power, data storage, etc).  Include deployment
+  schedule and introduce 2-element pathfinder in the following
+  section.}
 
-Measurements of the radio sky at $\approx$ 100 MHz and below have the capability of unlocking the new observational window in the history of the universe.
-At the lowest frequencies (tens of MHz), subsequent observations may permit us to probe the cosmic "dark ages," one day, which is an epoch that is obscure to date \cite{2019arXiv190710853C, 2019arXiv190804296K}.
-This paper will describe a new project that aims to map the low-frequency sky from Marion island using an array of autonomous antenna stations.
-The final array will consist of  $\approx$ 10 antennas operating at 1.2-81 MHz with baselines up to 20 km.
-A two-element pathfinder was deployed in April 2018, the first autonomous station was deployed in April 2019 and there'll be discussion of the preliminary observations and upcoming hardware development plans.
+The final array will consist of $\approx$ 10 antennas operating at
+1.2-81 MHz with baselines up to 20 km. A two-element pathfinder was
+deployed in April 2018, the first autonomous station was deployed in
+April 2019.
 
-\section{Overview of the Instrument}
+\section{Two-element pathfinder}
 
-The ALBATROS-EGG is a two element inteferometer which is making exploratory measurements at a frequency range of \SI{1.2}{MHz}- \SI{81}{MHz} separated by a baseline of \SI{110}{m} as shown in \autoref{Fig:ALBATROS-EGG}.
-It was deployed in Marion Island in April 2018.
-Its schematic is shown in \autoref{Fig:ALBATROS-EGG Schematic}.
-The system uses the dual polarisation dipole like antennas which are omidirectional patterned.
-The front end electonics (FEE) are configured in a printed circuit board (PCB) which makes it easy for them to be mounted on the supporting structure of the antennas.
-From the FEE PCB, a coaxial cable sends the signal through to the bias tee which extracts both the RF and the DC without any degradation.
-\\
-
-The high pass and the low pass filter rejects the low frequency signals and high frequency signals respectively.
-The signal is then amplified by a $\approx$20 dB amplifier which then send the amplified signals to the Smart Network ADC Processor (SNAP) board which does the readouts and does a series of processing step.
-The raspberry pi interacts with the SNAP board for data storage.\\
-
-\begin{figure}[h!]
+\begin{figure}
   \begin{center}
-		\includegraphics[width=0.55\linewidth]{Figures/ALBATROS-EGG-Schematic.PNG}
-		\caption{ALBATROS - EGG pathfinder schematic which consists of the dual polarisation antennas, the 35 dB gain FEE, the 100 m coaxial cable which connects the FEE to the back end Faraday cage which comprises of the bias tee, HPF, LPF, amplifier, snap board and regulated voltage outputs which are powered by 12 VDC batteries.}
-		\label{Fig:ALBATROS-EGG Schematic}
+    \includegraphics[width=0.7\linewidth]{Figures/ALBATROS-EGG.PNG}
+    \caption{The two-element \albatros\ pathfinder on Marion Island.
+      Two dual-polarization LWA antennas are separated by roughly
+      110~m on an east--west baseline. Coaxial cables connect the
+      antennas to an orange shipping container that houses the readout
+      electronics and serves as our ``command module.''}
+    \label{Fig:albatros2}
   \end{center}
@@
 
-	\begin{figure}[h]
+\begin{figure}
   \begin{center}
-			\includegraphics[width=0.7\linewidth]{Figures/ALBATROS-EGG.PNG}
-			\caption{The ALBATROS-EGG pathfinder on Marion Island.
-The pathfinder comprises two dual-polarization antennas separated by roughly 110 m on an east-west baseline.
-Long coaxial cables connect the antennas to	an orange shipping container that houses the readout electronics and serves as our "command module".}
-			\label{Fig:ALBATROS-EGG}
+    \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
+    \caption{Schematic for the two-element \albatros\ pathfinder.
+      Signals from two dual-polarzation LWA antennas are amplified by
+      front-end active baluns ({\bf citation for FEE}), and 100-m
+      coaxial cables connect the antennas to the back-end readout
+      electronics, which are housed in a Faraday cage denoted by the
+      dashed box.  Each of the four antenna outputs is passed to a
+      second-stage electronics chain consisting of a bias tee,
+      amplifier, and high- and low-pass filters.  The signals are
+      digitized at 250~Msamp/s by a SNAP board, and the on-board FPGA
+      is programmed with firmware to perform a full cross-correlation
+      of all four inputs.  A Raspberry Pi controls the SNAP board and
+      also saves the computed spectra to an SD card.  Power to the
+      system is provided by a bank of 12~V batteries and several
+      regulated voltage outputs.}
+    \label{Fig:albatros2_schem}
   \end{center}
 \end{figure}
+
+The ALBATROS-EGG is a two element inteferometer which is making
+exploratory measurements at a frequency range of \SI{1.2}{MHz}-
+\SI{81}{MHz} separated by a baseline of \SI{110}{m} as shown in
+\autoref{Fig:albatros2}. It was deployed in Marion Island in April
+2018. Its schematic is shown in \autoref{Fig:albatros2_schem}. The
+system uses the dual polarisation dipole like antennas which are
+omidirectional patterned. The front end electonics (FEE) are
+configured in a printed circuit board (PCB) which makes it easy for
+them to be mounted on the supporting structure of the antennas. From
+the FEE PCB, a coaxial cable sends the signal through to the bias tee
+which extracts both the RF and the DC without any degradation.
+
+The high pass and the low pass filter rejects the low frequency
+signals and high frequency signals respectively. The signal is then
+amplified by a $\approx$20 dB amplifier which then send the amplified
+signals to the Smart Network ADC Processor (SNAP) board which does the
+readouts and does a series of processing step. The raspberry pi
+interacts with the SNAP board for data storage.
 

### 2020-04-01 albatros_paper.tex
HCC updated albatros pathfinder glamor shot, more section 2 text updates

@@
 
-{\bf Write text here about the overall final configuration.  Describe
-  the site, show synthesized beam, discuss high level system
-  requirements (power, data storage, etc).  Include deployment
-  schedule and introduce 2-element pathfinder in the following
-  section.}
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.5\linewidth]{Figures/site.PNG}
+    \caption{{\bf UPDATE THIS FIGURE} Marion Island huts which are
+      potential stations for the ALBATROS. The ring-like pattern is
+      appropriate for imaging and produces a FWHM synthesized beam of
+      8' at 5 MHz.}
+    \label{Fig:marion}
+  \end{center}
+\end{figure}
+
+% Write text here about the overall final configuration.  Describe the
+% site, show synthesized beam, discuss high level system requirements
+% (power, data storage, etc).  Include deployment schedule and introduce
+% 2-element pathfinder in the following section.
+
+The primary requirements that drive the design for a low-frequency
+imaging experiment are 1) desired resolution, 2) low RFI, and 3) quiet
+ionospheric conditions.  As a benchmark, an interferometer operating
+at 30~MHz requires order-of-magnitude baseline lengths of $\sim 1$~km
+to achieve a resolution of $\sim 1$\degree.  This length scales
+inversely with frequency, and therefore $\sim 10$-km lengths are
+required at few-MHz frequencies in order to improve upon the
+resolutions achieved to date.  {\bf More words here about RFI and
+  ionosphere.}
 
@@
 
+Marion Island is a research location managed by the South African
+National Antarctic Programme (SANAP) and is located at
+\ang{46;54;45}S, \ang{37;44;37}E on the sub-antarctic of the Southern
+Indian Ocean. It is $\approx$\SI{2000}{\kilo\metre} from the nearest
+continental landmass which is also an approximate maximum distance
+for meteor scattering. The island has an area of
+\SI{290}{\kilo\metre\squared} and is only accessible once in April of
+every year by means of the S. A. Agulhas vessel owned by the
+Department of Environmental Affairs.
+
+Marion Island huts which are potential stations for the ALBATROS have
+a ring-like pattern which is appropriate for imaging and produces a
+FWHM synthesized beam of 8' at 5 MHz as shown in
+\autoref{Fig:10}. This beam is a notable advancement over existing
+measurements to date.The ALBATROS main goal thus far will be to
+attempt to map high resolutions at low frequencies which is crucial
+before moving to measuring the dark ages.
+
 \section{Two-element pathfinder}
@@
   \begin{center}
-    \includegraphics[width=0.7\linewidth]{Figures/ALBATROS-EGG.PNG}
+    \includegraphics[width=0.7\linewidth]{Figures/albatros_2elem/albatros_2elem.pdf}
     \caption{The two-element \albatros\ pathfinder on Marion Island.
@@
 \section{Pathfinder Installations and Preliminary Observations}
-\subsection{Marion Island}
- Marion Island is a research location managed by the South African National Antarctic Programme (SANAP) and is located at \ang{46;54;45}S, \ang{37;44;37}E on the sub-antarctic of the Southern Indian Ocean.
-It is $\approx$\SI{2000}{\kilo\metre} from the nearest continental landmass which is also an approximate maximum distance for meteor scattering.
-The island has an area of \SI{290}{\kilo\metre\squared} and is only accessible once in April of every year by means of the S.
-A.
-Agulhas vessel owned by the Department of Environmental Affairs.
 
@@
 
-\section{Future Work}
-
-Marion Island huts which are potential stations for the ALBATROS have a ring-like pattern which is appropriate for imaging and produces a FWHM synthesized beam of 8' at 5 MHz as shown in \autoref{Fig:10}.
-This beam is a notable advancement over existing measurements to date.The ALBATROS main goal thus far will be to attempt to map high resolutions at low frequencies which is crucial before moving to measuring the dark ages.
-
-\begin{figure}[h]
-	\centering
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=.9\linewidth]{Figures/site.PNG}
-		\caption{Marion Island huts which are potential stations for the ALBATROS. The ring-like pattern is appropriate for imaging and produces a FWHM synthesized beam of 8' at 5 MHz.}
-		\label{Fig:Marion}
-	\end{subfigure}%
-	~~~			
-	\begin{subfigure}[t]{0.5\textwidth}
-		\centering
-		\includegraphics[width=.9\linewidth]{Figures/beam.png}
-		\caption{Omnidirectional, dome shaped beam pattern which promises an improved resolution over the existing experiments to date.}
-		\label{Fig:beam}
-	\end{subfigure}
-	\caption{Potential stations and a beam encouraging enough to implement ALBATROS experiment}
-	\label{Fig:10}
-\end{figure}
+% \section{Future Work}
 

### 2020-04-01 albatros_paper.tex
HCC made a brand spanking new map of the island

@@
   \begin{center}
-    \includegraphics[width=0.5\linewidth]{Figures/site.PNG}
-    \caption{{\bf UPDATE THIS FIGURE} Marion Island huts which are
+    \includegraphics[width=0.7\linewidth]{Figures/marion_map/marion_map_annotated.jpg}
+    \caption{Marion Island huts which are
       potential stations for the ALBATROS. The ring-like pattern is
       appropriate for imaging and produces a FWHM synthesized beam of
-      8' at 5 MHz.}
+      8' at 5 MHz.  {\bf add text here about which ones are huts vs current install sites}}
     \label{Fig:marion}

### 2020-04-02 albatros_paper.tex
HCC tweaked marion map figure, reorganized a bunch of text and added nominal writing assignments

@@
 \def\albatros{ALBATROS}
+\def\prizm{PRI$^{\rm Z}$M}
 
@@
 \begin{abstract}
-The low frequency radio astronomy has the highest potential in discovering the history of the Universe, this includes observations of the first stars and the mapping of dark ages.
-The Array of Long Baseline Antennas for Taking Radio Observations from the Sub-Antarctic (ALBATROS) is a new interferometric array.
-It consists of autonomous antenna stations that will map the low-frequency sky from Marion Island.
-One autonomous station was deployed in Marion Island in April 2019.
-The operating frequency range is \SIrange{1.2}{81}{\MHz} with baselines of $\approx \SI{20}{\km}$.
-A two element inteferometer, the ALBATROS - Exploratory Gizmo on the Ground (ALBATROS-EGG) was deployed in Marion Island in April 2018.
-\\
+\textcolor{red}{\bf text to be overhauled later...} \\
+The low frequency radio astronomy has the highest potential in
+discovering the history of the Universe, this includes observations
+of the first stars and the mapping of dark ages. The Array of Long
+Baseline Antennas for Taking Radio Observations from the
+Sub-Antarctic (ALBATROS) is a new interferometric array. It consists
+of autonomous antenna stations that will map the low-frequency sky
+from Marion Island. One autonomous station was deployed in Marion
+Island in April 2019. The operating frequency range is
+\SIrange{1.2}{81}{\MHz} with baselines of $\approx \SI{20}{\km}$. A
+two element pathfinder was deployed in Marion Island in April
+2018.
 \end{abstract}
@@
 Very few experiments have measured the radio sky at $\lesssim 30$~MHz.
-Comprehensive reviews exist elsewhere ({\bf citation?}), and here, we
-highlight only a few specific examples.  At the very lowest
-frequencies, the state of the art among ground-based measurements
-dates from the 1950s, when Reber and Ellis caught brief glimpses of
-the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an array of
-192~dipoles~\citep{reber, article, 1988A&A...195..372W}.  A few
-space-based missions have also performed measurements at similarly low
-frequency ranges; for example, the Radio Astronomy Explorer-2 operated
-at \SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
+Comprehensive reviews exist elsewhere (\textcolor{red}{\bf find a good
+  reference}), and here, we highlight only a few specific examples.
+At the very lowest frequencies, the state of the art among
+ground-based measurements dates from the 1950s, when Reber and Ellis
+caught brief glimpses of the $2.1$~MHz sky at $\sim
+5$\degree\ resolution, using an array of 192~dipoles~\citep{reber,
+  article, 1988A&A...195..372W}.  A few space-based missions have also
+performed measurements at similarly low frequency ranges; for example,
+the Radio Astronomy Explorer-2 operated at \SIrange{0.025}{13}{\MHz}
+with $\sim 10$\degree\ resolution at
 \SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
@@
 resolution measurements at the lowest frequencies.
+
+\textcolor{red}{\bf More text about the science case, including
+  Galactic astrophysics (Jon? Jeff?)}
 
@@
     \includegraphics[width=0.7\linewidth]{Figures/marion_map/marion_map_annotated.jpg}
-    \caption{Marion Island huts which are
-      potential stations for the ALBATROS. The ring-like pattern is
-      appropriate for imaging and produces a FWHM synthesized beam of
-      8' at 5 MHz.  {\bf add text here about which ones are huts vs current install sites}}
+    \caption{Map of Marion Island.  The \albatros\ pathfinder antennas
+      are currently installed at the \prizm\ site and at the hydro
+      shack.  The black markers denote the eight coastal huts, which
+      will be used for future \albatros\ antenna installations.  The
+      white markers denote other available infrastructure points that
+      will not be used for antennas.  \textcolor{red}{\bf Add new
+        synthesized beam figure (Jon)}}
     \label{Fig:marion}
@@
 required at few-MHz frequencies in order to improve upon the
-resolutions achieved to date.  {\bf More words here about RFI and
-  ionosphere.}
+resolutions achieved to date.  The experiment installation site must
+be remote to keep RFI to a minimum, and polar or near-polar latitiudes
+generally have lower ionospheric plasma frequency cutoffs.
+\textcolor{red}{\bf Add more ionosphere text here, plus IRI simulation
+  fig/numbers (Jon)}
 
-The final array will consist of $\approx$ 10 antennas operating at
-1.2-81 MHz with baselines up to 20 km. A two-element pathfinder was
-deployed in April 2018, the first autonomous station was deployed in
-April 2019.
+Marion Island is a research base that is located in the southern
+Indian Ocean at \ang{46;54;45}S, \ang{37;44;37}E and is operated by
+the South African National Antarctic Programme.  The island lies
+roughly \SI{2000}{\kilo\metre} from the nearest continental landmasses
+and has an exceptionally quiet RFI
+environment~\citep{2019JAI.....850004P}.  As illustrated in
+\autoref{Fig:marion}, Marion has an area of 335~km$^2$ and can
+therefore support antenna installations with $>10$-km baseline
+lengths.  The main Marion base is located on the northeast side of the
+island, and there are eight rest huts along the coast (Cape Davis,
+Grey-headed, Kildalkey, Mixed Pickle, Repettos, Rooks, Swartkops,
+Watertunnel) and one in the interior (Katedraal) that can serve as
+existing infrastructure points for antenna installations.  The planned
+\albatros\ installation sites include the coastal huts, but exclude
+the main base and Katedraal for RFI and accessibility reasons,
+respectively.  \autoref{Fig:marion} also shows the locations of the
+\albatros\ pathfinder antennas that are currently installed at the
+\prizm\ site and at the hydro shack.
 
-Marion Island is a research location managed by the South African
-National Antarctic Programme (SANAP) and is located at
-\ang{46;54;45}S, \ang{37;44;37}E on the sub-antarctic of the Southern
-Indian Ocean. It is $\approx$\SI{2000}{\kilo\metre} from the nearest
-continental landmass which is also an approximate maximum distance
-for meteor scattering. The island has an area of
-\SI{290}{\kilo\metre\squared} and is only accessible once in April of
-every year by means of the S. A. Agulhas vessel owned by the
-Department of Environmental Affairs.
-
-Marion Island huts which are potential stations for the ALBATROS have
-a ring-like pattern which is appropriate for imaging and produces a
-FWHM synthesized beam of 8' at 5 MHz as shown in
-\autoref{Fig:10}. This beam is a notable advancement over existing
-measurements to date.The ALBATROS main goal thus far will be to
-attempt to map high resolutions at low frequencies which is crucial
-before moving to measuring the dark ages.
+Using the eight coastal huts, the \prizm\ site, and the hydro shack as
+the nominal \albatros\ installation locations, the computed
+synthesized beam is as shown in \autoref{Fig:marion}.  The beam width
+at 5~MHz is roughly \SI{8}{\arcminute}, which represents over an order
+of magnitude improvement in resolution over other existing
+measurements.  One of the challenges in constructing an interferometer
+array on Marion Island is that the rugged terrain precludes the
+possibility of directly cabling and correlating antennas across large
+distances.  The final \albatros\ antenna stations will therefore
+operate {\it autonomously}, recording baseband data over extended
+periods of time for subsequent offline correlation.  We have conducted
+two enginering runs: 1) a two-element, directly correlated pathfinder
+to qualitatively understand the sky signal, and 2) a single station to
+test the readout and power handling technology that are required for
+autonomous operation.
 
@@
     \includegraphics[width=0.7\linewidth]{Figures/albatros_2elem/albatros_2elem.pdf}
-    \caption{The two-element \albatros\ pathfinder on Marion Island.
-      Two dual-polarization LWA antennas are separated by roughly
-      110~m on an east--west baseline. Coaxial cables connect the
-      antennas to an orange shipping container that houses the readout
-      electronics and serves as our ``command module.''}
+    \caption{The two-element, directly correlated
+      \albatros\ pathfinder installed at the \prizm\ site.  Two
+      dual-polarization antennas are separated by roughly 110~m on an
+      east--west baseline. Coaxial cables connect the antennas to a
+      shipping container that houses the readout electronics and
+      serves as the ``command module.'' \textcolor{red}{\bf Add FEE
+        and backend sub-pics here? (HCC)}}
     \label{Fig:albatros2}
@@
       Signals from two dual-polarzation LWA antennas are amplified by
-      front-end active baluns ({\bf citation for FEE}), and 100-m
-      coaxial cables connect the antennas to the back-end readout
-      electronics, which are housed in a Faraday cage denoted by the
-      dashed box.  Each of the four antenna outputs is passed to a
-      second-stage electronics chain consisting of a bias tee,
+      front-end active baluns (\textcolor{red}{\bf citation for FEE}),
+      and 100-m coaxial cables connect the antennas to the back-end
+      readout electronics, which are housed in a Faraday cage denoted
+      by the dashed box.  Each of the four antenna outputs is passed
+      to a second-stage electronics chain consisting of a bias tee,
       amplifier, and high- and low-pass filters.  The signals are
@@
 
-The ALBATROS-EGG is a two element inteferometer which is making
-exploratory measurements at a frequency range of \SI{1.2}{MHz}-
-\SI{81}{MHz} separated by a baseline of \SI{110}{m} as shown in
-\autoref{Fig:albatros2}. It was deployed in Marion Island in April
-2018. Its schematic is shown in \autoref{Fig:albatros2_schem}. The
-system uses the dual polarisation dipole like antennas which are
-omidirectional patterned. The front end electonics (FEE) are
-configured in a printed circuit board (PCB) which makes it easy for
-them to be mounted on the supporting structure of the antennas. From
-the FEE PCB, a coaxial cable sends the signal through to the bias tee
-which extracts both the RF and the DC without any degradation.
+The first exploratory \albatros\ measurements were conducted with a
+two-element pathfinder that employed direct correlation (without
+autonomous operation).  \autoref{Fig:albatros2} illustrates this
+pathfinder, which was installed at the \prizm\ site (\ang{46;53;13}S,
+\ang{37;49;10.7}E) in April 2018.  The system schematic is illustrated
+in \autoref{Fig:albatros2_schem}, and each of the subsystems is
+described in detail below.
 
-The high pass and the low pass filter rejects the low frequency
-signals and high frequency signals respectively. The signal is then
-amplified by a $\approx$20 dB amplifier which then send the amplified
-signals to the Smart Network ADC Processor (SNAP) board which does the
-readouts and does a series of processing step. The raspberry pi
-interacts with the SNAP board for data storage.
+\subsection{Antenna}	
+We employ two dual-polarization Long Wavelength Array (LWA) dipole
+antennas~\citep{Memo28}.  The LWA antennas have a long development
+history, are well characterized, and are simple to install and
+physically robust.  The antennas form an east--west baseline with a
+separation of \SI{110}{m}, and the polarizations are aligned with the
+cardinal directions.  Welded wire mesh screens, roughly 3~m on a side,
+are installed on the ground below the antennas.
+% do we want/need to say anything about the omnidirectional primary beam?
 
-The final project (ALBATROS) will consist of autonomous antenna stations that will map the low frequency sky.
-Since these experiments are exploratory, they are taking steps towards achieving the future objective of probing the Dark Ages.The ALBATROS stations (huts) will be separated by baselines of \SI{\approx {20}}{km} as shown in \autoref{Fig:Marion}.
-The two-element interferomentric pathfinder is not yet operating autonomously, it uses the direct cross correlation technique whereas the yet to be ALBATROS will write the lowest 10 - 20 MHz baseband to disk then gets correlated afterwards.
-One ALBATROS fully autonomous station was deployed in Marion Island in April 2019 as shown in \autoref{Fig:autonomous}.
-\\
+\textcolor{red}{\bf ALL TEXT BELOW HERE NEEDS WORK}
 
-The single antenna analog signal chain is shown in \autoref{Fig:Signal Chain}.
-The components of the system are discussed in detail as per the block diagram illustrated in \autoref{Fig:Signal Chain}.
-This analog signal chain is an illustration of how the first autonomous station is configured.
-There might be changes to the block diagram at a later stage should there be a need to revise it for the stations.
+\subsection{Front-end active balun}
+\textcolor{red}{\bf Tankiso, Eamon, Jeff?} \\
+All the front end components were incorporated for in a double sided
+printed circuit board (PCB) as shown in \autoref{Fig:Balun} and the
+block diagram is shown in \autoref{Fig:Balun Schematic}. The
+Monolithic Microwave Integrated Circuits (MMICs) is the used design
+for the PCB. One side of the PCB is populated with components and the
+other side is a solid copper ground plane aperiodically stitched to
+the grounded copper on the side populated with components. The
+receiver system is made up of the active balun, filter and the gain
+stage that connects to the \SI{100}{\metre} coaxial cable which is
+connected to the back end \cite{2012PASP..124.1090H}.
 
-\begin{figure}[h]
+The input impedance (Z\textsubscript{o}) of \SI{50}{\ohm} is
+introduced to the dipole by the active balun. The signal is then fed
+through an amplifier which amplifies it by \SI{+24}{\decibel} of
+gain. The balanced signal is then converted to unbalanced through a
+180 \degree hybrid coupler. The band pass filter (BPF) receives the
+single ended signal in order for it to reject all the frequencies
+which are not within the range of interest. The signal gets fed to a
+second amplifier which again amplies it by \SI{+24}{\decibel} of gain
+and the output impedance of the FEE is matched to a \SI{50}{\ohm}
+coaxial cable. The bias tee is responsible for providing power to the
+FEE and extracts the RF signal by the use of the coaxial cable. This
+unit has an overall gain of $\approx$ \SI{35}{\decibel} and an overall
+noise figure of $\approx$ \SI{2.7}{\decibel} to $\approx$
+\SI{2.9}{\decibel} \cite{Memo35}.
+
+\subsection{Back End Electronics}
+\textcolor{red}{\bf Nivek, HCC?} \\
+The back end electronics consists of the bias tee, high pass filter
+(HPF), low pass filter (LPF) and the Smart Network ADC Processor
+(SNAP) board.  The signals are band limited to \SI{1.2}{MHz}-\SI{81}{MHz}.
+
+\textbf{Bias Tee} - It is used to extract the RF signal from a
+\SI{100}{\metre} LMR400 coaxial cable which has a nominal attenuation
+of \SI{\approx 0.4}{\decibel/\SI{100}{m}} - \SI{\approx
+  3.7}{dB/\SI{100}{\metre}} at \SI{1.2}{MHz} - \SI{81}{MHz}
+respectively \footnote{https://www.timesmicrowave.com/documents/resources/LMR-400.pdf}. The
+bias tee which is used is the Mini Circuits device ZFBT-4R2GW-FT+
+which operates between \SI{0.14}{MHz} - \SI{4200}{MHz}. It has an
+insertion loss of \SI{0.16}{\decibel} at centre frequency of
+\SI{\approx 10}{MHz} as per the
+datasheet \footnote{https://www.minicircuits.com/pdfs/ZFBT-4R2GW-FT+.pdf}.
+
+\textbf{HPF} - The HPF rejects any signals with low frequencies and
+allow through signals with high
+frequencies \footnote{http://www.learningaboutelectronics.com/Articles/High-pass-filter.php}. The
+HPF used is the ZFHP-1R2+ Mini Circuits device which operates between
+\SI{1.2}{MHz} - \SI{800}{MHz}. It has a nominal insertion loss of
+$\approx$ \SI{0.2}{\decibel} at centre frequency of
+\SI{\approx10}{MHz} as per the
+datasheet \footnote{https://www.minicircuits.com/pdfs/ZFHP-1R2+.pdf}.
+
+\textbf{LPF} - The LPF rejects all signals with high frequencies and
+allows all signals with low
+frequencies \footnote{http://www.learningaboutelectronics.com/Articles/Low-pass-filter.php}. The
+LPF used is the SLP-90+ Mini Circuits device which operates between
+\SI{1}{MHz} - \SI{400}{MHz}. It has a nominal insertion loss of
+$\approx$ \SI{0.14}{\decibel} at the centre frequency of \SI{\approx
+  10}{MHz} \footnote{https://www.minicircuits.com/pdfs/SLP-90+.pdf}.
+
+\textbf{Amplifier} - The amplifier at the backend amplifies the signal
+which is sent through to the snapboard by the gain of
+\SI{+20}{\decibel}. The amplifier used is the Mini Circuits device
+ZX60-V63+ which operates at a frequency range of \SI{0.05}{GHz} -
+\SI{6}{GHz}. It has a noise figure of $\approx$ \SI{3.6}{\decibel} at
+its lowest operating frequency of \SI{\approx
+  50}{MHz} \footnote{https://www.minicircuits.com/pdfs/ZX60-V63+.pdf}.
+
+\textbf{SNAP Board} - The SNAP board used is specified by Xilinx
+Inc. \footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}. The
+SNAP board samples the signals it receives by 250 Msampl/s using
+internal ADCs where the signal of the clock is from the Valon 5007
+frerquency synthesizer module. This creates a frequency range between
+\SI{0}{MHz} - \SI{125}{MHz} which contains 2048 channels. A SNAP board
+interacts with a raspberry pi and that is where the data is saved.
+
+\subsection{Power}
+\textcolor{red}{\bf Tankiso?} \\
+Text here about generators.
+
+\section{Single autonomous station pathfinder}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.7\linewidth]{Figures/autonomous.jpg}
+    \caption{Single autonomous station pathfinder}
+    \label{Fig:autonomous}
+  \end{center}
+\end{figure}
+
+\begin{figure}
   \begin{center}
     \includegraphics[width=0.7\linewidth]{Figures/Signal-Chain.png}
-		\caption{Analog signal chain block diagram for the newly deployed autonomous station the ALBATROS}
+    \caption{Schematic for single autonomous station pathfinder.
+      \textcolor{red}{\bf Update this figure and make it similar to
+        the two-element schematic.  Tankiso, Nivek, HCC?}}
     \label{Fig:Signal Chain}
@@
 
-\subsection{Antenna}	
-The system uses the dual polarisation dipole like antennas which are omidirectionally patterned.
-The dipole like antennas are of high preference for this project because they are relatively simple and they are omnidirectionally patterned \cite{Memo28}.
+\textcolor{red}{\bf Nivek?} \\
 
-\subsection{Front End Electronics (FEE)}
-All the front end components were incorporated for in a double sided printed circuit board (PCB) as shown in \autoref{Fig:Balun} and the block diagram is shown in \autoref{Fig:Balun Schematic}.
-The Monolithic Microwave Integrated Circuits (MMICs) is the used design for the PCB.
-One side of the PCB is populated with components and the other side is a solid copper ground plane aperiodically stitched to the grounded copper on the side populated with components.
-The receiver system is made up of the active balun, filter and the gain stage that connects to the \SI{100}{\metre} coaxial cable which is connected to the back end \cite{2012PASP..124.1090H}.\\
-The input impedance (Z\textsubscript{o}) of \SI{50}{\ohm} is introduced to the dipole by the active balun.
-The signal is then fed through an amplifier which amplifies it by \SI{+24}{\decibel} of gain.
-The balanced signal is then converted to unbalanced through a 180 \degree hybrid coupler.
-The band pass filter (BPF) receives the single ended signal in order for it to reject all the frequencies which are not within the range of interest.
-The signal gets fed to a second amplifier which again amplies it by \SI{+24}{\decibel} of gain and the output impedance of the FEE is matched to a \SI{50}{\ohm} coaxial cable.
-The bias tee is responsible for providing power to the FEE and extracts the RF signal by the use of the coaxial cable.
-This unit has an overall gain of $\approx$ \SI{35}{\decibel} and an overall noise figure of $\approx$ \SI{2.7}{\decibel} to $\approx$ \SI{2.9}{\decibel} \cite{Memo35}.
+A single, autonomous station pathfinder was installed at the hydro
+shack (\ang{46;52.205;}S, \ang{37;50.612;}E) in April 2019.
 
-\begin{figure}[h]
-	\begin{center}
-		\includegraphics[width=0.5\linewidth]{Figures/balun.jpg}
-		\caption{Unenclosed FEE mounted on the ALBATROS-EGG antenna supporting structure.} 
-		\label{Fig:Balun}
-	\end{center}
-\end{figure}
+The final project (ALBATROS) will consist of autonomous antenna
+stations that will map the low frequency sky. Since these experiments
+are exploratory, they are taking steps towards achieving the future
+objective of probing the Dark Ages.The ALBATROS stations (huts) will
+be separated by baselines of \SI{\approx {20}}{km} as shown in
+\autoref{Fig:Marion}. The two-element interferomentric pathfinder is
+not yet operating autonomously, it uses the direct cross correlation
+technique whereas the yet to be ALBATROS will write the lowest 10 - 20
+MHz baseband to disk then gets correlated afterwards. One ALBATROS
+fully autonomous station was deployed in Marion Island in April 2019
+as shown in \autoref{Fig:autonomous}.
 
-\begin{figure}[h]
-	\begin{center}
-		\includegraphics[width=0.7\linewidth]{Figures/Balun_Block.png}
-		\caption{One Polarisation Block Diagram of the FEE \cite{2012PASP..124.1090H}}
-		\label{Fig:Balun Schematic}
-	\end{center}
-\end{figure}
+The single antenna analog signal chain is shown in \autoref{Fig:Signal
+  Chain}. The components of the system are discussed in detail as per
+the block diagram illustrated in \autoref{Fig:Signal Chain}. This
+analog signal chain is an illustration of how the first autonomous
+station is configured. There might be changes to the block diagram at
+a later stage should there be a need to revise it for the stations.
 
-\subsection{Back End Electronics}	
-The back end electronics consists of the bias tee, high pass filter (HPF), low pass filter (LPF) and the Smart Network ADC Processor (SNAP) board. \\
+% HCC: we probably don't need these figures below, or we can
+% incorporate them as subfigs into other places
 
-\textbf{Bias Tee} - It is used to extract the RF signal from a \SI{100}{\metre} LMR400 coaxial cable which has a nominal attenuation of \SI{\approx 0.4}{\decibel/\SI{100}{m}} - \SI{\approx 3.7}{dB/\SI{100}{\metre}} at \SI{1.2}{MHz} - \SI{81}{MHz} respectively \footnote{https://www.timesmicrowave.com/documents/resources/LMR-400.pdf}.
-The bias tee which is used is the Mini Circuits device ZFBT-4R2GW-FT+ which operates between \SI{0.14}{MHz} - \SI{4200}{MHz}.
-It has an insertion loss of \SI{0.16}{\decibel} at centre frequency of  \SI{\approx 10}{MHz} as per the datasheet \footnote{https://www.minicircuits.com/pdfs/ZFBT-4R2GW-FT+.pdf}.\\
+% \begin{figure}[h]
+% 	\begin{center}
+% 		\includegraphics[width=0.5\linewidth]{Figures/balun.jpg}
+% 		\caption{Unenclosed FEE mounted on the ALBATROS-EGG antenna supporting structure.} 
+% 		\label{Fig:Balun}
+% 	\end{center}
+% \end{figure}
+% 
+% \begin{figure}[h]
+% 	\begin{center}
+% 		\includegraphics[width=0.7\linewidth]{Figures/Balun_Block.png}
+% 		\caption{One Polarisation Block Diagram of the FEE \cite{2012PASP..124.1090H}}
+% 		\label{Fig:Balun Schematic}
+% 	\end{center}
+% \end{figure}
 
-\textbf{HPF} - The HPF rejects any signals with low frequencies and allow through signals with high frequencies \footnote{http://www.learningaboutelectronics.com/Articles/High-pass-filter.php}.
-The HPF used is the ZFHP-1R2+ Mini Circuits device which operates between  \SI{1.2}{MHz} - \SI{800}{MHz}.
-It has a nominal insertion loss of $\approx$ \SI{0.2}{\decibel} at centre frequency of  \SI{\approx10}{MHz} as per the datasheet \footnote{https://www.minicircuits.com/pdfs/ZFHP-1R2+.pdf}.\\
-
-\textbf{LPF} - The LPF rejects all signals with high frequencies and allows all signals with low frequencies \footnote{http://www.learningaboutelectronics.com/Articles/Low-pass-filter.php}.
-The LPF used is the SLP-90+ Mini Circuits device which operates between \SI{1}{MHz} - \SI{400}{MHz}.
-It has a nominal insertion loss of $\approx$ \SI{0.14}{\decibel} at the centre frequency of  \SI{\approx 10}{MHz} \footnote{https://www.minicircuits.com/pdfs/SLP-90+.pdf}.\\
-
-\textbf{Amplifier} - The amplifier at the backend amplifies the signal which is sent through to the snapboard by the gain of \SI{+20}{\decibel}.
-The amplifier used is the Mini Circuits device ZX60-V63+ which operates at a frequency range of \SI{0.05}{GHz} - \SI{6}{GHz}.
-It has a noise figure of $\approx$ \SI{3.6}{\decibel} at its lowest operating frequency of \SI{\approx 50}{MHz} \footnote{https://www.minicircuits.com/pdfs/ZX60-V63+.pdf}.\\
-
-\textbf{SNAP Board} - The SNAP board used is specified by Xilinx Inc.
-\footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}.
-The  SNAP board samples the signals it receives by 250 Msampl/s using internal ADCs where the signal of the clock is from the Valon 5007 frerquency synthesizer module.
-This creates a frequency range between \SI{0}{MHz} - \SI{125}{MHz} which contains 2048 channels.
-A SNAP board interacts with a raspberry pi and that is where the data is saved.\\
-
-\subsection{Solar Power Supply System}
+\subsection{Solar power system}
+\textcolor{red}{\bf Nivek, Tankiso, Eamon?} \\
 The power system of the ALBATROS-EGG uses generators to charge the batteries manually every once in a number of days.
@@
 
-\section{Pathfinder Installations and Preliminary Observations}
+\section{Preliminary observations}
 
- \subsection{Experiments}
- The ALBATROS-EGG shown in \autoref{Fig:ALBATROS-EGG} was installed on the PRI\textsuperscript{z}M \cite{2019JAI.....850004P} site which is located at \ang{46;53;13}S, \ang{37;49;10.7}E and the first ALBATROS station shown in \autoref{Fig:autonomous} is located \ang{46;52.205;}S, \ang{37;50.612;}E.\\
-
-	\begin{figure}[h]
-		\begin{center}
-			\includegraphics[width=0.7\linewidth]{Figures/autonomous.jpg}
-			\caption{}
-			\label{Fig:autonomous}
-		\end{center}
-	\end{figure}
-
- \subsection{Preliminary Observations}
+\textcolor{red}{\bf NEED UPDATED AND NEW PLOTS, NEED VOLUNTEERS FOR THIS:
+  \begin{itemize}
+    \item{Improved waterfall plots from 2-element pathfinder}
+    \item{Plot showing that the solar power works (sort of)}
+    \item{Some sort of...data...plot for the autonomous station.  Can
+      we say anything about baseband performance?}
+  \end{itemize}
+}
 

### 2020-04-02 albatros_paper.tex
HCC added a few more red edit notes
HCC started updating schematic for autonomous station

@@
 \keywords{cosmology: observations; dark ages; instrumentation: interferometers}
+
+\textcolor{red}{\bf Open task for any/all: fix references, make a proper bibtex file}
 
@@
 
-\subsection{Back End Electronics}
+\subsection{Back-end electronics}
 \textcolor{red}{\bf Nivek, HCC?} \\
@@
 interacts with a raspberry pi and that is where the data is saved.
+\textcolor{red}{\bf include text about firmware}
 
@@
 Text here about generators.
+
+\subsection{Software and data acquisition}
+\textcolor{red}{\bf Nivek?} \\
+Text goes here.
 
@@
     \includegraphics[width=0.7\linewidth]{Figures/autonomous.jpg}
-    \caption{Single autonomous station pathfinder}
+    \caption{Single autonomous station pathfinder.  \textcolor{red}{\bf Add command module and electronics glamor shots.}}
     \label{Fig:autonomous}
@@
   \begin{center}
-    \includegraphics[width=0.7\linewidth]{Figures/Signal-Chain.png}
+    \includegraphics[width=\linewidth]{Figures/albatros_single_schematic/albatros_single_schematic.pdf}
     \caption{Schematic for single autonomous station pathfinder.
-      \textcolor{red}{\bf Update this figure and make it similar to
-        the two-element schematic.  Tankiso, Nivek, HCC?}}
+      \textcolor{red}{\bf Finish updating this figure.  Tankiso, Nivek, HCC?}}
     \label{Fig:Signal Chain}

### 2020-04-02 albatros_paper.tex
HCC updated autonomous station schematic + caption

@@
       of all four inputs.  A Raspberry Pi controls the SNAP board and
-      also saves the computed spectra to an SD card.  Power to the
+      also saves the computed spectra to an SD card.  The clock signal
+      is provided by a Valon frequency synthesizer.  Power to the
       system is provided by a bank of 12~V batteries and several
@@
     \includegraphics[width=\linewidth]{Figures/albatros_single_schematic/albatros_single_schematic.pdf}
-    \caption{Schematic for single autonomous station pathfinder.
-      \textcolor{red}{\bf Finish updating this figure.  Tankiso, Nivek, HCC?}}
+    \caption{Schematic for the single autonomous station pathfinder.
+      Data and RF connections are outlined in black, and power
+      connections are outlined in red.  A dual-polarization LWA
+      antenna, equipped with an active balun, is connected 50-m
+      coaxial cables to the back-end readout electronics, which are
+      housed in a Faraday cage denoted by the dashed box.  Each of the
+      two antenna inputs is passed to a second-stage electronics chain
+      consisting of a bias tee, high- and low-pass filters, and
+      amplifier.  The signals are digitized at 250~Msamp/s by a SNAP
+      board, and the on-board FPGA is programmed with firmware that
+      computes averaged auto- and cross-spectra, as well as
+      channelized baseband.  A Raspberry Pi controls the SNAP board
+      and saves the data products to a combination of an SD card and
+      external hard drives.  Timing information is provided by a
+      GPS-discipined clock.  Power to the system is provided solar
+      panels that charges a 24-V battery bank, which is regulated down
+      to several other output levels.}
     \label{Fig:Signal Chain}
@@
 % \end{figure}
+
+\subsection{Readout electronics}
+\textcolor{red}{\bf Nivek, Jon?} \\
+Text here about one-bit stuff, pushing baseband through the RPi3,
+clock requirements, data rates, etc.
 

### 2020-04-02 albatros_paper.tex
HCC a few more text edits

@@
 \textcolor{red}{\bf Nivek, HCC?} \\
-The back end electronics consists of the bias tee, high pass filter
-(HPF), low pass filter (LPF) and the Smart Network ADC Processor
-(SNAP) board.  The signals are band limited to \SI{1.2}{MHz}-\SI{81}{MHz}.
+
+The back-end readout electronics are housed in a Faraday cage that is
+located $\sim 100$~m away from the antennas to reduce potential
+contamination from self-generated RFI.  Each of the four antenna
+signals is passed to a second-stage electronics chain consisting of a
+bias tee (Minicircuits ZFBT-4R2GW-FT+), amplifier (Minicircuits
+ZX60-V63+), and a pair of high- and low-pass filters (Minicircuits
+ZFHP-1R2+ and SLP-90+) that band limit the signal to
+1.2--\SI{81}{MHz}.  A Smart Network ADC Processor (SNAP) board
+digitizes the RF signals at 250~Msamp/s and calculates a full
+cross-correlation of the four inputs, producing four auto- and six
+cross-spectra as outputs.  \textcolor{red}{\bf finish merging text
+  below into the above paragraph}
 
@@
     \includegraphics[width=0.7\linewidth]{Figures/autonomous.jpg}
-    \caption{Single autonomous station pathfinder.  \textcolor{red}{\bf Add command module and electronics glamor shots.}}
+    \caption{Single autonomous station pathfinder installed at the
+      hydro shack site.  The system is powered by a bank of solar
+      panels that are visible in the background.  \textcolor{red}{\bf
+        Add command module and electronics glamor shots.}}
     \label{Fig:autonomous}
@@
       connections are outlined in red.  A dual-polarization LWA
-      antenna, equipped with an active balun, is connected 50-m
+      antenna, equipped with an active balun, is connected via 50-m
       coaxial cables to the back-end readout electronics, which are

### 2020-04-13 albatros_paper.tex
added correlator bits

@@
 
+\subsection{Correlation}
+While the basics of 1-bit correlation are well known in the limit where the signal level is much lower than the noise, ALBATROS may well be in the high-signal regime.
+We present the basics of 1-bit correlation here, and show that even in the high-signal limit, 1-bit correlation remains viable.
+The fundamental output of a 1-bit correlator for real data is $x_{ij} \equiv \left < \tilde{E}_i \tilde{E}_j \right >$.
+$ \tilde{E}_i$ is the quantized version of the underlying electric field $E_i$ where $ \tilde{E}_i=1$ for $E_i>0$ and $ \tilde{E}_i=-1$ for $E_i<0$.
+Note that complex data can be handled as the combination of real components.
+This output is non-linear in the underlying true signal and noise levels, since the output saturates at unity for perfectly correlated electric fields.
+To get at the true sky signals, we will need to undo this nonlinearity (the so-called Van Vleck corrections).
+For a 2-level correlator, the expected output can be related to the true signals as follows (Van Vleck \& Middleton, e.g.
+D'Addario):
+\begin{eqnarray}
+\label{eqn:1bit_output}
+\left < \sin(\frac{\pi}{2}x_{ij})\right > = \frac{V_{ij}}{\sqrt{V_{ij}+N_i}\sqrt{V_{ij}+N_j}}
+\end{eqnarray}
+where $V_{ij}$ is the true visibility, and $V_{ij}+N_{i,j}$ is the total noise power measured by antennas $i$ and $j$.
+Inverting this relation to get the true signal requires knowing the noise powers, which is not possible from the 1-bit data themselves.
+However, the SNAP board calculates these power levels on timescales of a few seconds, much faster than the power levels change, and so by combining the single-station power measurements with the cross-station cross correlation, we will be able to derive the true sky visibilities.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.7\linewidth]{Figures/corr_efficiency.png}
+    \caption{Correlator efficiency $\epsilon_{corr}$ for a 1-bit correlator as a function of signal-to-noise ratio (SNR).
+To get the expected SNR from a 1-bit correlator, multiply the SNR derived from the radiometer equation by $\epsilon_{corr}$.
+For low SNR, the efficiency is $2/\pi \sim 0.64$, and it drops monotonically as the SNR increases.
+The drop is relatively gentle, only changing by a factor of $\sim 2$ for SNR=2.
+For baseline separations of many wavelengths, the correlated component of the electric field is likely to be a small fraction of the total power, so ALBATROS is unlikely to lose more than a factor of $\sim 2$ by using 1-bit correlation.}
+    \label{Fig:1bit_efficiency}
+    \end{center}
+\end{figure}
+
+One might worry that at high signal levels, the saturation of the 1-bit cross correlation would lead to the noise exploding.
+In practice the rolloff in sensitivity is relatively mild, especially in the case of long baselines.
+It can be expressed in terms of the correlator efficiency $\epsilon_{corr}$, which is defined to be the ratio of the measured signal-to-noise ratio to the ideal (infinite precision) SNR.
+As seen in Figure \ref{fig:1bit_efficiency}, $\epsilon_{corr}$ only drops by a factor of $\sim$2 as the signal power goes from 0 to a few times the noise power.
+We stress that the signal level is question is the part that correlates between the two antennas.
+In the case of long baselines (where long means the fringe spacing is small compared to the primary beam/antenna response pattern) that are not dominated by a single bright source, the signal power will always be smaller than the noise power, and so $\epsilon_{corr}$ is unlikely to drop below $\sim$0.5\footnote{A quick estimate can be made by analogy to the behavior of dishes in the UV plane in the flat sky approximation.
+While all power in the UV plane (plus any system noise) goes into an individual antenna's electric field, the correlated part only has contribution from the area in the UV plane within the width of the UV-space primary beam of the UV-space coordinate.
+If the sky can be described as a Gaussian random field, in the most pessimistic case this is roughly the aperture filling factor of the antenna pair.
+In our case, where the antennas are approximately dipolar, the filling factor will be the square of the wavelength over the baseline length.
+As long as the baselines are several wavelengths or longer, the correlated power will be small, and the correlator efficiency will be close to the ideal 1-bit value of $\frac{2}{\pi}$.
+
 \subsection{Solar power system}

### 2020-04-14 albatros_paper.tex
forgot to close an argument

@@
 In our case, where the antennas are approximately dipolar, the filling factor will be the square of the wavelength over the baseline length.
-As long as the baselines are several wavelengths or longer, the correlated power will be small, and the correlator efficiency will be close to the ideal 1-bit value of $\frac{2}{\pi}$.
+As long as the baselines are several wavelengths or longer, the correlated power will be small, and the correlator efficiency will be close to the ideal 1-bit value of $\frac{2}{\pi}$.}.
 

### 2020-04-16 albatros_paper.tex
Add files via upload
Added some text under "Power" subsection.

@@
 \subsection{Power}
-\textcolor{red}{\bf Tankiso?} \\
-Text here about generators.
+
+In order to supply power to the whole two-element pathfinder sysytem, a bank of four \SI{12}{V}, \SI{200}{\ampere\hour} batteries were wired in parallel.
+The Honda EU30is generator is used for charging the battery bank and the fuel is kept in one of the shipping containers at the \prizm\ site.
+If the batteries are fully charged, the system can fully operate for approximately four days.
+The power from the battery bank is connected to the Faraday cage where the power regulation is performed.
+A DC/DC converter stabilises the \SI{12}{V} from the battery bank and further supplies it to the auxiliary regulators that provide step down voltages to various components in the system.
 
@@
 
-The final project (ALBATROS) will consist of autonomous antenna
-stations that will map the low frequency sky. Since these experiments
-are exploratory, they are taking steps towards achieving the future
+The final project (ALBATROS) will consist of autonomous antenna stations that will map the low frequency sky.
+Since these experiments are exploratory, they are taking steps towards achieving the future
 objective of probing the Dark Ages.The ALBATROS stations (huts) will

### 2020-05-06 albatros_paper.tex
Changes to front and backend electronics section (some previous text left in for reference but commented out)

@@
 \textcolor{red}{\bf Tankiso, Eamon, Jeff?} \\
+
+The LWA active-balun front-end electronics (FEE) circuit uses  a MiniCircuits GALI-74+ MMIC to amplify each dipole leg against ground, presenting each leg with a 50$\ohm$ impedance and providing a nominal gain of 25dB.
+The two GALI-74+ outputs are differenced using a passive {180\degree} hybrid coupler.
+The coupler output is filtered by a $\sim$150MHz lowpass, and receives an additional 12dB of gain from a MiniCircuits GALI-6+ MMIC.
+This last amplifier drives the output signal onto a $\sim$100m 50$\ohm$ coaxial cable.
+Thus, neglecting mismatch loss between the dipoles (electrically small in the frequency range of interest) and the 100{\ohm} input impedance, as well as the hybrid insertion loss ($<$1dB), the front-end electronics provide a gain of $\sim$37dB \cite{2012PASP..124.1090H}.
+
+Each FEE circuit is powered by 16V, fed on the coax through a bias tee.
+
+% EE citing the noise figure of the GALI-74+ is particulary misleading because of the large mismatch loss, which directly scales up the noise figure in the HF band.
+
+\iffalse
+
 All the front end components were incorporated for in a double sided
@@
 
+\fi
+
 \subsection{Back-end electronics}
@@
 The back-end readout electronics are housed in a Faraday cage that is
-located $\sim 100$~m away from the antennas to reduce potential
-contamination from self-generated RFI.  Each of the four antenna
-signals is passed to a second-stage electronics chain consisting of a
-bias tee (Minicircuits ZFBT-4R2GW-FT+), amplifier (Minicircuits
+located $\sim$100m away from the antennas to mitigate possible
+self-generated RFI.  Each of the four antenna
+signals is passed to a second-stage electronics chain consisting of 
+% EE bias tee is already described; it isn't really part of the signal chain since it doesn't do much of anything
+%a bias tee (Minicircuits ZFBT-4R2GW-FT+), 
+an
+amplifier (Minicircuits
 ZX60-V63+), and a pair of high- and low-pass filters (Minicircuits
-ZFHP-1R2+ and SLP-90+) that band limit the signal to
-1.2--\SI{81}{MHz}.  A Smart Network ADC Processor (SNAP) board
-digitizes the RF signals at 250~Msamp/s and calculates a full
+ZFHP-1R2+ and SLP-90+) that together  bandlimit the signal to
+1.2--\SI{81}{MHz}.  The amplifier has a nominal gain of 20dB, and the HPF and LPF contribute nominal insertion losses of 0.2dB and 0.14dB respectively.
+
+A Xilinx Kintex\footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html} based Smart Network ADC Processor (SNAP) board (\textcolor{red}{\bf citation for SNAP board?}), 
+clocked by a Valon 5007 frequency synthesizer module,
+digitizes the RF signals at 250~Msamp/s. It calculates a full
 cross-correlation of the four inputs, producing four auto- and six
-cross-spectra as outputs.  \textcolor{red}{\bf finish merging text
+cross-spectra as outputs, over 2048 channels spanning the frequency range 
+\SI{0}{MHz} - \SI{125}{MHz}. 
+(\textcolor{red}{\bf details about SNAP board frequency transform?})
+The SNAP board sends its output data via ethernet to a Raspberry Pi (\textcolor{red}{\bf version? citation?}), which saves it to a hard drive.
+
+\iffalse
+
+\textcolor{red}{\bf finish merging text
   below into the above paragraph}
@@
 \textbf{SNAP Board} - The SNAP board used is specified by Xilinx
-Inc. \footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}. The
+Inc. \footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}. 
+% EE it's unclear what this means. The reference is to the Kintex FPGA family, which says nothing about the SNAP board
+The
 SNAP board samples the signals it receives by 250 Msampl/s using
@@
 \textcolor{red}{\bf include text about firmware}
+
+\fi
 

### 2020-05-06 albatros_paper.tex
\attention macro added for flagging issues

@@
 \def\prizm{PRI$^{\rm Z}$M}
+\newcommand{\attention}[1]{\textcolor{red}{\bf {#1}}}
 
@@
 \begin{abstract}
-\textcolor{red}{\bf text to be overhauled later...} \\
+\attention {text to be overhauled later...} \\
 The low frequency radio astronomy has the highest potential in
@@
 
-\textcolor{red}{\bf Open task for any/all: fix references, make a proper bibtex file}
+\attention{Open task for any/all: fix references, make a proper bibtex file}
 
@@
 Very few experiments have measured the radio sky at $\lesssim 30$~MHz.
-Comprehensive reviews exist elsewhere (\textcolor{red}{\bf find a good
+Comprehensive reviews exist elsewhere (\attention{find a good
   reference}), and here, we highlight only a few specific examples.
@@
 
-\textcolor{red}{\bf More text about the science case, including
+\attention{More text about the science case, including
   Galactic astrophysics (Jon? Jeff?)}
@@
       white markers denote other available infrastructure points that
-      will not be used for antennas.  \textcolor{red}{\bf Add new
+      will not be used for antennas.  \attention{Add new
         synthesized beam figure (Jon)}}
@@
 generally have lower ionospheric plasma frequency cutoffs.
-\textcolor{red}{\bf Add more ionosphere text here, plus IRI simulation
+\attention{Add more ionosphere text here, plus IRI simulation
   fig/numbers (Jon)}
@@
 environment~\citep{2019JAI.....850004P}.  As illustrated in
-\autoref{Fig:marion}, Marion has an area of 335~km$^2$ and can
+\autoref{Fig:marion}, \attention{this points to the map, not the beam pattern} Marion has an area of 335~km$^2$ and can
 therefore support antenna installations with $>10$-km baseline
@@
       shipping container that houses the readout electronics and
-      serves as the ``command module.'' \textcolor{red}{\bf Add FEE
+      serves as the ``command module.'' \attention{Add FEE
         and backend sub-pics here? (HCC)}}
@@
       Signals from two dual-polarzation LWA antennas are amplified by
-      front-end active baluns (\textcolor{red}{\bf citation for FEE}),
+      front-end active baluns (\attention{citation for FEE}),
       and 100-m coaxial cables connect the antennas to the back-end
@@
 
-\textcolor{red}{\bf ALL TEXT BELOW HERE NEEDS WORK}
+\attention{ALL TEXT BELOW HERE NEEDS WORK}
 
 \subsection{Front-end active balun}
-\textcolor{red}{\bf Tankiso, Eamon, Jeff?} \\
+\attention{Tankiso, Eamon, Jeff?} \\
 
@@
 \subsection{Back-end electronics}
-\textcolor{red}{\bf Nivek, HCC?} \\
+\attention{Nivek, HCC?} \\
 
@@
 
-A Xilinx Kintex\footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html} based Smart Network ADC Processor (SNAP) board (\textcolor{red}{\bf citation for SNAP board?}), 
+A Xilinx Kintex\footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html} based Smart Network ADC Processor (SNAP) board (\attention{citation for SNAP board?}), 
 clocked by a Valon 5007 frequency synthesizer module,
@@
 \SI{0}{MHz} - \SI{125}{MHz}. 
-(\textcolor{red}{\bf details about SNAP board frequency transform?})
-The SNAP board sends its output data via ethernet to a Raspberry Pi (\textcolor{red}{\bf version? citation?}), which saves it to a hard drive.
+(\attention{details about SNAP board frequency transform?})
+The SNAP board sends its output data via ethernet to a Raspberry Pi (\attention{version? citation?}), which saves it to a hard drive.
 
@@
 
-\textcolor{red}{\bf finish merging text
+\attention{finish merging text
   below into the above paragraph}
@@
 interacts with a raspberry pi and that is where the data is saved.
-\textcolor{red}{\bf include text about firmware}
+\attention{include text about firmware}
 
@@
 \subsection{Software and data acquisition}
-\textcolor{red}{\bf Nivek?} \\
+\attention{Nivek?} \\
 Text goes here.
@@
       hydro shack site.  The system is powered by a bank of solar
-      panels that are visible in the background.  \textcolor{red}{\bf
+      panels that are visible in the background.  \attention{
         Add command module and electronics glamor shots.}}
@@
 
-\textcolor{red}{\bf Nivek?} \\
+\attention{Nivek?} \\
 
@@
 \subsection{Readout electronics}
-\textcolor{red}{\bf Nivek, Jon?} \\
+\attention{Nivek, Jon?} \\
 Text here about one-bit stuff, pushing baseband through the RPi3,
@@
 \subsection{Solar power system}
-\textcolor{red}{\bf Nivek, Tankiso, Eamon?} \\
+\attention{Nivek, Tankiso, Eamon?} \\
 The power system of the ALBATROS-EGG uses generators to charge the batteries manually every once in a number of days.
@@
 
-\textcolor{red}{\bf NEED UPDATED AND NEW PLOTS, NEED VOLUNTEERS FOR THIS:
+\attention{NEED UPDATED AND NEW PLOTS, NEED VOLUNTEERS FOR THIS:
   \begin{itemize}

### 2020-05-06 albatros_paper.tex
made a .bib file

@@
 \usepackage{url}
+\usepackage{natbib}
 
@@
 \newcommand{\attention}[1]{\textcolor{red}{\bf {#1}}}
+
+\newcommand{\aap}{Astronomy and Astrophysics}
+\newcommand{\aj}{Astronomical Journal}
+\newcommand{\pasp}{Proceedings of the Astronomical Society of the Pacific}
+\newcommand{\prd}{Physical Review D}
+\newcommand{\apj}{Astrophysical Journal}
+\newcommand{\aaps}{Astronomy and Astrophysics Supplements}
 
@@
 
-\begin{thebibliography}{9}
+\bibliographystyle{apj}
+\bibliography{albatros_paper}{}
 
-\bibitem[Alexander et al.(1975)]{1975A&A....40..365A} Alexander, J.~K., Kaiser, M.~L., Novaco, J.~C., et al.\ 1975, {\it aap\/}, {\bf 40}, 365
+%\begin{thebibliography}{9}
+%
+%\bibitem[Alexander et al.(1975)]{1975A&A....40..365A} Alexander, J.~K., Kaiser, M.~L., Novaco, J.~C., et al.\ 1975, {\it aap\/}, {\bf 40}, 365
+%
+%\bibitem[Chen {et al.}(2019)]{2019arXiv190710853C} Chen, X., Burns, J., Koopmans, L., {\it et al.} [2019], arXiv e-prints, arXiv:1907.10853
 
-\bibitem[Chen {et al.}(2019)]{2019arXiv190710853C} Chen, X., Burns, J., Koopmans, L., {\it et al.} [2019], arXiv e-prints, arXiv:1907.10853
+%\bibitem[Eastwood et al.(2018)]{2018AJ....156...32E} Eastwood, M.~W., Anderson, M.~M., Monroe, R.~M., et al.\ 2018, {\it aj\/}, {\bf 156}, 32
 
-\bibitem[Eastwood et al.(2018)]{2018AJ....156...32E} Eastwood, M.~W., Anderson, M.~M., Monroe, R.~M., et al.\ 2018, {\it aj\/}, {\bf 156}, 32
+%\bibitem[Ellingson and Kramer (2004)]{Memo28} Ellingson, S.~W., {Kramer}, W.~T. \ 2004, {\it Long Wavelength Array Memo (28)}
 
-\bibitem[Ellingson and Kramer (2004)]{Memo28} Ellingson, S.~W., {Kramer}, W.~T. \ 2004, {\it Long Wavelength Array Memo (28)}
+%\bibitem[George {et al.}(2018)] {article} George, M., Orchiston, W., Wielebinsk, R., {\it et al.} [2018], Journal of Astronomical History and Heritage, {\bf 21}, 37
 
-\bibitem[George {et al.}(2018)] {article} George, M., Orchiston, W., Wielebinsk, R., {\it et al.} [2018], Journal of Astronomical History and Heritage, {\bf 21}, 37
+%\bibitem[Hicks et al.(2012)]{2012PASP..124.1090H} Hicks, B.~C., Paravastu-Dalal, N., Stewart, K.~P., et al.\ 2012, {\it pasp\/}, {\bf 124}, 1090
 
-\bibitem[Hicks et al.(2012)]{2012PASP..124.1090H} Hicks, B.~C., Paravastu-Dalal, N., Stewart, K.~P., et al.\ 2012, {\it pasp\/}, {\bf 124}, 1090
+%\bibitem[Koopmans {et al.}(2019)]{2019arXiv190804296K} Koopmans, L., Barkana, R., Bentum, M., {\it et al.} [2019], arXiv e-prints, arXiv:1908.04296
 
-\bibitem[Koopmans {et al.}(2019)]{2019arXiv190804296K} Koopmans, L., Barkana, R., Bentum, M., {\it et al.} [2019], arXiv e-prints, arXiv:1908.04296
+%\bibitem[Liu {et al.}(2013)]{2013PhRvD..87d3002L} Liu, A., Pritchard, J.~R., Tegmark, M., {\it et al.} [2013], {\bf 87}, 043002
 
-\bibitem[Liu {et al.}(2013)]{2013PhRvD..87d3002L} Liu, A., Pritchard, J.~R., Tegmark, M., {\it et al.} [2013], {\bf 87}, 043002
+%\bibitem[Philip {et al.}(2019)]{2019JAI.....850004P} Philip, L., Abdurashidova, Z., Chiang, H.~C., {\it et al.} [2019], Journal of Astronomical Instrumentation, {\bf 8}, 19500
 
-\bibitem[Philip {et al.}(2019)]{2019JAI.....850004P} Philip, L., Abdurashidova, Z., Chiang, H.~C., {\it et al.} [2019], Journal of Astronomical Instrumentation, {\bf 8}, 19500
+%\bibitem[Pober {et al.}(2014)]{2014ApJ...782...66P} Pober, J.~C., Liu, A., Dillon, J.~S., {\it et al.} [2014], {\bf 782}, 66
 
-\bibitem[Pober {et al.}(2014)]{2014ApJ...782...66P} Pober, J.~C., Liu, A., Dillon, J.~S., {\it et al.} [2014], {\bf 782}, 66
+%\bibitem[Ray et al.(2006)]{Memo35} Ray, P.~S., Ellingson, S.~W., Fisher R., {\it et al.} [2006] {\it Long Wavelength Array Memo (35)}
 
-\bibitem[Ray et al.(2006)]{Memo35} Ray, P.~S., Ellingson, S.~W., Fisher R., {\it et al.} [2006] {\it Long Wavelength Array Memo (35)}
+%\bibitem[Roger et al.(1999)]{1999A&AS..137....7R} Roger, R.~S., Costain, C.~H., Landecker, T.~L., et al.\ 1999, {\it aaps\/}, {\bf 137}, 7
 
-\bibitem[Roger et al.(1999)]{1999A&AS..137....7R} Roger, R.~S., Costain, C.~H., Landecker, T.~L., et al.\ 1999, {\it aaps\/}, {\bf 137}, 7
+%\bibitem[Weiler {et al.}(1988)]{1988A&A...195..372W} Weiler, K.~W., Johnston, K.~J., Simon, R.~S., {\it et al.} [1988], {\it aap\/}, {\bf 195}, 372
 
-\bibitem[Weiler {et al.}(1988)]{1988A&A...195..372W} Weiler, K.~W., Johnston, K.~J., Simon, R.~S., {\it et al.} [1988], {\it aap\/}, {\bf 195}, 372
-
-\end{thebibliography}
+%\end{thebibliography}
 \end{document}

### 2020-05-12 albatros_paper.tex
Edits on 2 and 1 element pathfinder signal chain descriptions (and a bit about 1-element setup power)
* balance detail between caption (some removed) and text (added)
* Make the description style consistent between 2 and 1 element
configurations. And other edits.
* remove some commented-out text

@@
 
+% Two-element block diagram goes here
 \begin{figure}
-  \begin{center}
-    \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
-    \caption{Schematic for the two-element \albatros\ pathfinder.
+  \begin{center} \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
+    \caption{Two-element \albatros\ pathfinder block diagram.
       Signals from two dual-polarzation LWA antennas are amplified by
-      front-end active baluns (\attention{citation for FEE}),
-      and 100-m coaxial cables connect the antennas to the back-end
+      front-end active baluns (\attention{citation for FEE}).
+      Antennas are connected via 100m coax cables to the back-end 
       readout electronics, which are housed in a Faraday cage denoted
       by the dashed box.  Each of the four antenna outputs is passed
-      to a second-stage electronics chain consisting of a bias tee,
-      amplifier, and high- and low-pass filters.  The signals are
-      digitized at 250~Msamp/s by a SNAP board, and the on-board FPGA
-      is programmed with firmware to perform a full cross-correlation
-      of all four inputs.  A Raspberry Pi controls the SNAP board and
-      also saves the computed spectra to an SD card.  The clock signal
-      is provided by a Valon frequency synthesizer.  Power to the
-      system is provided by a bank of 12~V batteries and several
-      regulated voltage outputs.}
+      to a second-stage electronics chain consisting of filters and further amplfication.  The signals are
+      digitized at 250~Msamp/s by a SNAP board, which includes an on-board FPGA that computes auto and cross spectra
+      from and between the four inputs.  A Raspberry Pi controls the SNAP board and
+      saves the data.}
     \label{Fig:albatros2_schem}
@@
 pathfinder, which was installed at the \prizm\ site (\ang{46;53;13}S,
-\ang{37;49;10.7}E) in April 2018.  The system schematic is illustrated
+\ang{37;49;10.7}E) in April 2018.  The system block diagram is shown
 in \autoref{Fig:albatros2_schem}, and each of the subsystems is
@@
 \attention{Tankiso, Eamon, Jeff?} \\
+\label{section:FEE}
 
-The LWA active-balun front-end electronics (FEE) circuit uses  a MiniCircuits GALI-74+ MMIC to amplify each dipole leg against ground, presenting each leg with a 50$\ohm$ impedance and providing a nominal gain of 25dB.
-The two GALI-74+ outputs are differenced using a passive {180\degree} hybrid coupler.
-The coupler output is filtered by a $\sim$150MHz lowpass, and receives an additional 12dB of gain from a MiniCircuits GALI-6+ MMIC.
-This last amplifier drives the output signal onto a $\sim$100m 50$\ohm$ coaxial cable.
-Thus, neglecting mismatch loss between the dipoles (electrically small in the frequency range of interest) and the 100{\ohm} input impedance, as well as the hybrid insertion loss ($<$1dB), the front-end electronics provide a gain of $\sim$37dB \cite{2012PASP..124.1090H}.
+The LWA active-balun front-end electronics (FEE) circuit uses a MiniCircuits GALI-74+ MMIC 
+to amplify each dipole leg against ground, presenting each leg with a 50$\ohm$ impedance 
+and providing a nominal gain of 25dB. The two GALI-74+ outputs are differenced using a 
+passive {180\degree} hybrid coupler. The coupler output is filtered by a $\sim$150MHz lowpass, 
+and receives an additional 12dB of gain from a MiniCircuits GALI-6+ MMIC. This last amplifier 
+drives the output signal onto a 100m 50$\ohm$ coaxial cable. Thus, neglecting mismatch loss 
+between the dipoles (electrically small in the frequency range of interest) and the 100{\ohm} 
+input impedance, as well as the hybrid insertion loss ($<$1dB), the front-end electronics 
+provide a gain of $\sim$37dB \cite{2012PASP..124.1090H}.
 
@@
 
+% It seems to me that this is too much detail to go into in describing an already published design.
 \iffalse
@@
 
-The back-end readout electronics are housed in a Faraday cage that is
-located $\sim$100m away from the antennas to mitigate possible
+The back-end readout electronics are housed in a Faraday cage
+located 100m away from the antennas to mitigate possible
 self-generated RFI.  Each of the four antenna
@@
 (\attention{details about SNAP board frequency transform?})
-The SNAP board sends its output data via ethernet to a Raspberry Pi (\attention{version? citation?}), which saves it to a hard drive.
-
-\iffalse
-
-\attention{finish merging text
-  below into the above paragraph}
-
-\textbf{Bias Tee} - It is used to extract the RF signal from a
-\SI{100}{\metre} LMR400 coaxial cable which has a nominal attenuation
-of \SI{\approx 0.4}{\decibel/\SI{100}{m}} - \SI{\approx
-  3.7}{dB/\SI{100}{\metre}} at \SI{1.2}{MHz} - \SI{81}{MHz}
-respectively \footnote{https://www.timesmicrowave.com/documents/resources/LMR-400.pdf}. The
-bias tee which is used is the Mini Circuits device ZFBT-4R2GW-FT+
-which operates between \SI{0.14}{MHz} - \SI{4200}{MHz}. It has an
-insertion loss of \SI{0.16}{\decibel} at centre frequency of
-\SI{\approx 10}{MHz} as per the
-datasheet \footnote{https://www.minicircuits.com/pdfs/ZFBT-4R2GW-FT+.pdf}.
-
-\textbf{HPF} - The HPF rejects any signals with low frequencies and
-allow through signals with high
-frequencies \footnote{http://www.learningaboutelectronics.com/Articles/High-pass-filter.php}. The
-HPF used is the ZFHP-1R2+ Mini Circuits device which operates between
-\SI{1.2}{MHz} - \SI{800}{MHz}. It has a nominal insertion loss of
-$\approx$ \SI{0.2}{\decibel} at centre frequency of
-\SI{\approx10}{MHz} as per the
-datasheet \footnote{https://www.minicircuits.com/pdfs/ZFHP-1R2+.pdf}.
-
-\textbf{LPF} - The LPF rejects all signals with high frequencies and
-allows all signals with low
-frequencies \footnote{http://www.learningaboutelectronics.com/Articles/Low-pass-filter.php}. The
-LPF used is the SLP-90+ Mini Circuits device which operates between
-\SI{1}{MHz} - \SI{400}{MHz}. It has a nominal insertion loss of
-$\approx$ \SI{0.14}{\decibel} at the centre frequency of \SI{\approx
-  10}{MHz} \footnote{https://www.minicircuits.com/pdfs/SLP-90+.pdf}.
-
-\textbf{Amplifier} - The amplifier at the backend amplifies the signal
-which is sent through to the snapboard by the gain of
-\SI{+20}{\decibel}. The amplifier used is the Mini Circuits device
-ZX60-V63+ which operates at a frequency range of \SI{0.05}{GHz} -
-\SI{6}{GHz}. It has a noise figure of $\approx$ \SI{3.6}{\decibel} at
-its lowest operating frequency of \SI{\approx
-  50}{MHz} \footnote{https://www.minicircuits.com/pdfs/ZX60-V63+.pdf}.
-
-\textbf{SNAP Board} - The SNAP board used is specified by Xilinx
-Inc. \footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}. 
-% EE it's unclear what this means. The reference is to the Kintex FPGA family, which says nothing about the SNAP board
-The
-SNAP board samples the signals it receives by 250 Msampl/s using
-internal ADCs where the signal of the clock is from the Valon 5007
-frerquency synthesizer module. This creates a frequency range between
-\SI{0}{MHz} - \SI{125}{MHz} which contains 2048 channels. A SNAP board
-interacts with a raspberry pi and that is where the data is saved.
-\attention{include text about firmware}
-
-\fi
+The SNAP board sends its output data via ethernet to a Raspberry Pi (\attention{version?
+citation?}), which saves baseband data to a set of hard drives, while storing the less voluminous correlation data on its SD card.
 
@@
 
-In order to supply power to the whole two-element pathfinder sysytem, a bank of four \SI{12}{V}, \SI{200}{\ampere\hour} batteries were wired in parallel.
-The Honda EU30is generator is used for charging the battery bank and the fuel is kept in one of the shipping containers at the \prizm\ site.
-If the batteries are fully charged, the system can fully operate for approximately four days.
-The power from the battery bank is connected to the Faraday cage where the power regulation is performed.
-A DC/DC converter stabilises the \SI{12}{V} from the battery bank and further supplies it to the auxiliary regulators that provide step down voltages to various components in the system.
-
+A bank of four parallel \SI{12}{V}, \SI{200}{\ampere\hour} batteries serves to power to the two-element pathfinder sysytem.
+A Honda EU30is generator is run periodically to charge the battery bank, which can run the system for approximately four days on a full charge.
+DC/DC converters power the SNAP board, the FEE, the amplifiers and the clock.
+% Cuts (redundant or too much detail)
+% and the fuel is kept in one of the shipping containers at the \prizm\ site
+% The power from the battery bank is connected to the Faraday cage where the power regulation is performed.
 \subsection{Software and data acquisition}
@@
 
+% single element block diagram goes here
 \begin{figure}
@@
     \includegraphics[width=\linewidth]{Figures/albatros_single_schematic/albatros_single_schematic.pdf}
-    \caption{Schematic for the single autonomous station pathfinder.
+    \caption{Single-antenna autonomous station block diagram. 
       Data and RF connections are outlined in black, and power
-      connections are outlined in red.  A dual-polarization LWA
-      antenna, equipped with an active balun, is connected via 50-m
-      coaxial cables to the back-end readout electronics, which are
-      housed in a Faraday cage denoted by the dashed box.  Each of the
-      two antenna inputs is passed to a second-stage electronics chain
-      consisting of a bias tee, high- and low-pass filters, and
-      amplifier.  The signals are digitized at 250~Msamp/s by a SNAP
-      board, and the on-board FPGA is programmed with firmware that
-      computes averaged auto- and cross-spectra, as well as
-      channelized baseband.  A Raspberry Pi controls the SNAP board
-      and saves the data products to a combination of an SD card and
-      external hard drives.  Timing information is provided by a
-      GPS-discipined clock.  Power to the system is provided solar
-      panels that charges a 24-V battery bank, which is regulated down
-      to several other output levels.}
+      connections in red.  
+      A dual-polarization LWA
+      antenna, equipped with an active balun (described above in \ref{section:FEE}), connects via 50m
+      coaxial cables to the back-end readout electronics, 
+      housed in a Faraday cage denoted by the dashed box. 
+      The antenna signals are passed
+      to a second-stage electronics chain consisting of filters and further amplfication.  The signals are
+      digitized at 250~Msamp/s by a SNAP board, which includes an on-board FPGA that computes spectra from both antennas.  
+      A Raspberry Pi controls the SNAP board, receives the spectrum of interest from the SNAP, and saves it as baseband data.}
     \label{Fig:Signal Chain}
@@
 \end{figure}
-
 \attention{Nivek?} \\
 
-A single, autonomous station pathfinder was installed at the hydro
-shack (\ang{46;52.205;}S, \ang{37;50.612;}E) in April 2019.
-
-The final project (ALBATROS) will consist of autonomous antenna stations that will map the low frequency sky.
-Since these experiments are exploratory, they are taking steps towards achieving the future
-objective of probing the Dark Ages.The ALBATROS stations (huts) will
+The full ALBATROS configuration will comprise an array of 10 autonomous antenna stations, recording the lowest 10-20MHz baseband to disk, to be collected periodically and subsequently correlated offline.
+The ALBATROS stations (located at the eight coastal hut sites plus the hydro shack and \prizm\ site) will
 be separated by baselines of \SI{\approx {20}}{km} as shown in
-\autoref{Fig:Marion}. The two-element interferomentric pathfinder is
-not yet operating autonomously, it uses the direct cross correlation
-technique whereas the yet to be ALBATROS will write the lowest 10 - 20
-MHz baseband to disk then gets correlated afterwards. One ALBATROS
-fully autonomous station was deployed in Marion Island in April 2019
-as shown in \autoref{Fig:autonomous}.
-
-The single antenna analog signal chain is shown in \autoref{Fig:Signal
-  Chain}. The components of the system are discussed in detail as per
-the block diagram illustrated in \autoref{Fig:Signal Chain}. This
-analog signal chain is an illustration of how the first autonomous
-station is configured. There might be changes to the block diagram at
-a later stage should there be a need to revise it for the stations.
+\autoref{Fig:Marion}. One fully autonomous ALBATROS
+station, shown in \autoref{Fig:autonomous}, was deployed in April 2019 at the hydro shack location (\ang{46;52.205;}S, \ang{37;50.612;}E) on Marion Island, as a first step in testing the technology needed to establish this array.
 
@@
 \attention{Nivek, Jon?} \\
-Text here about one-bit stuff, pushing baseband through the RPi3,
-clock requirements, data rates, etc.
+
+The single antenna signal chain is shown in \autoref{Fig:Signal Chain}. 
+% start of copied text
+The back-end readout electronics are housed in a Faraday cage
+located 50m away from the antennas. The analog signal chain consists 
+a pair of high- and low-pass filters (Minicircuits
+ZFHP-1R2+ and SLP-90+) that, as in the two-element configuration, together bandlimit the signal to
+1.2--\SI{81}{MHz}.
+The filters are followed by a MiniCircuits ZFL-500+ amplifier.
+The HPF and LPF contribute nominal insertion losses of 0.2dB and 0.14dB respectively, and the amplifier has a nominal gain of 25dB.
+
+As with the dual-antenna configuration described above, a SNAP board digitizes the RF  at 250~Msamp/s.
+In this configuration, the SNAP board ADC is locked to a 10MHz reference produced by a Trimble Thunderbole E GPS disciplined clock module.
+The Raspberry Pi receives the spectrally decomposed baseband data \attention{which frequencies are we storing?} and stores it onto a set of hard drives.
+(\attention{reference the same frequency transform as in the 2-element case})
+%end of copied text
+
+\attention{Text here about one-bit stuff, pushing baseband through the RPi3,
+clock requirements, data rates, etc.}
 
@@
 As seen in Figure \ref{fig:1bit_efficiency}, $\epsilon_{corr}$ only drops by a factor of $\sim$2 as the signal power goes from 0 to a few times the noise power.
-We stress that the signal level is question is the part that correlates between the two antennas.
+We stress that the signal level in question is the part that correlates between the two antennas.
 In the case of long baselines (where long means the fringe spacing is small compared to the primary beam/antenna response pattern) that are not dominated by a single bright source, the signal power will always be smaller than the noise power, and so $\epsilon_{corr}$ is unlikely to drop below $\sim$0.5\footnote{A quick estimate can be made by analogy to the behavior of dishes in the UV plane in the flat sky approximation.

### 2020-05-12 albatros_paper.tex
HCC working on section 1

@@
 
-Very few experiments have measured the radio sky at $\lesssim 30$~MHz.
-Comprehensive reviews exist elsewhere (\attention{find a good
-  reference}), and here, we highlight only a few specific examples.
-At the very lowest frequencies, the state of the art among
-ground-based measurements dates from the 1950s, when Reber and Ellis
-caught brief glimpses of the $2.1$~MHz sky at $\sim
-5$\degree\ resolution, using an array of 192~dipoles~\citep{reber,
-  article, 1988A&A...195..372W}.  A few space-based missions have also
-performed measurements at similarly low frequency ranges; for example,
-the Radio Astronomy Explorer-2 operated at \SIrange{0.025}{13}{\MHz}
-with $\sim 10$\degree\ resolution at
+Very few experiments have measured the radio sky at $\lesssim 30$~MHz;
+here, we highlight only four specific examples.  At the very lowest
+frequencies, the state of the art among ground-based measurements
+dates from the 1950s, when Reber and Ellis caught brief glimpses of
+the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an array of
+192~dipoles~\citep{reber, article, 1988A&A...195..372W}.  A few
+space-based missions have also performed measurements at similarly low
+frequency ranges; for example, the Radio Astronomy Explorer-2 operated
+at \SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
 \SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
-resolution finer than few-degree scales exist only at higher
+resolution finer than few-degree scales exist mainly at higher
 frequencies.  For example, the Dominion Radio Astrophysical
@@
 information about the $\lesssim 30$~MHz sky and the lack of high
-resolution measurements at the lowest frequencies.
+resolution measurements at the lowest frequencies.  As a first step
+toward laying the groundwork for possible future cosmological
+measurements,...finish this sentence...
 

### 2020-05-12 albatros_paper.tex
HCC added a few more placeholder words in section 1

@@
 information about the $\lesssim 30$~MHz sky and the lack of high
-resolution measurements at the lowest frequencies.  As a first step
+resolution measurements at the lowest frequencies.  The first step
 toward laying the groundwork for possible future cosmological
-measurements,...finish this sentence...
-
-\attention{More text about the science case, including
-  Galactic astrophysics (Jon? Jeff?)}
+measurements is obtaining an improved map of Galactic foregrounds at
+$\lesssim 30$~MHz.  Maps at these frequencies can additionally shed
+new light on Galactic astrophysics, including cosmic ray structure
+along the line of sight (\attention{more words here about synchrotron
+  self-absorption}), \attention{words here about radio recombination
+  lines}.  \attention{More words here about possible ionospheric
+  studies.}
 

### 2020-05-12 albatros_paper.tex
minor edits before merging some stuff from Cynthia

--- 2020-05-12 albatros_paper.tex
@@
 
-A bank of four parallel \SI{12}{V}, \SI{200}{\ampere\hour} batteries serves to power to the two-element pathfinder sysytem.
+A bank of four parallel \SI{12}{V}, \SI{200}{\ampere\hour} batteries serves to power the two-element pathfinder system.
 A Honda EU30is generator is run periodically to charge the battery bank, which can run the system for approximately four days on a full charge.
@@
 \attention{Nivek, Tankiso, Eamon?} \\
+Although the first-deployed two-element pathfinder setup uses generators to periodically recharge batteries, the bulk of the antenna stations that will comprise the full array will be located at points farther removed from the main base, and will require a fully autonomous energy source.
+
 The power system of the ALBATROS-EGG uses generators to charge the batteries manually every once in a number of days.

### 2020-05-12 albatros_paper.tex
work on solar section, add some more detail

--- 2020-05-12 albatros_paper.tex
@@
 \attention{Nivek, Tankiso, Eamon?} \\
-The power system of the ALBATROS-EGG uses generators to charge the batteries manually every once in a number of days.
-From the observation that has been made, the batteries take $\approx$ 2 days to discharge to a point where the system shuts down.
-Because of the weather conditions in Marion Island, an individual can sometimes be unable to go to the site to charge the batteries, which means that if the weather does not allow, the system can be shut down for a long period.
-Thus, a solar power system solution was introduced to the ALBATROS so that the system can continously run without having to be recharged manually and often.\\
+Although the first-deployed two-element pathfinder is located at a reasonable walking distance from the main base and uses a generator to periodically recharge batteries, the bulk of the antenna stations that will comprise the full array will be located at points farther removed from the main base, and will require a fully autonomous energy source.
+So in deploying the autonomous station pathfinder, we developed a solar charging system to power the station.
 
+The autonomous station is powered by two series-connected 12V deep-cycle lead-acid batteries, charged by an array of nine  SunPower SPE-E-Flex-110 solar panels.
+These panels each have a standard test capacity of 110W.
+Although only $\sim$50W is required to run the station (and the station may typically be powered on only over night) the $\sim$1kW charging capacity is sized to allow the charge level to recover quickly on a short sunny day in winter if it runs down due to several consecutive overcast days.
+
+The nine solar panels are distributed between three custom-designed structures built from aluminum extrusion, with rigid metalized plastic panels backing the semi-flexible solar cells.
+The structures are oriented due north, and are designed to incline the solar panels at a relatively steep angle so as to maximize peformance under winter conditions, when sunlight hours will be at their minimum.
+The solar panel mounts have been designed to withstand frequent gale-force winds on Marion.
+While the mounting structures themselves appear to be strong enough, the greatest challenge in deployment has been to find an adequate anchoring technique in the volcanic ground.
+
+Each group of three panels is wired in series, and the three series strings are connected in parallel to a Victron BlueSolar MPPT 50$\vert$35 charge controller, which optimizes power transfer from the solar array when charging is required, and also monitors charge level, reducing charge current when the battery bank is fully charged.
+
+A power logging and control system runs on an Arduino, which logs information received from the Victron charge controller to an SD card, and switches power on and off to the receiver chassis.
+Logged power data will be used to refine powers system requirements for future autonomous station deployments.
+The on/off control is necessary to prevent battery system  damage from overly deep discharge.
+The system can also be configured to conserve battery power by running on a schedule between particular hours, typically overnight, since visibility may be better and ionosopheric noise levels lower.
+
+The power logging and control system, along with the Victron charge controller and an EMI filter, are housed together in an aluminum box.
+The EMI filter reduces conducted emissions on the photovoltaic side of the solar charge controller, which could radiate from the solar array and connecting wires.
+(It may be noted however, that signals collected at night, which are expected to be more valuable, are not at risk of solar charge controller EMI contamination.)
+
+\iffalse
 The ALBATROS system is powered using \SI{24}{\volt} power which is stored and provided by two series-connected \SI{12}{\volt} deep-cycle lead-acid storage batteries.
@@
 The observed parameters are then stored to the raspberry pi.
+\fi
 

### 2020-05-13 albatros_paper.tex
HCC editing section 1, added some references

@@
 \newcommand{\aap}{Astronomy and Astrophysics}
+\newcommand{\aaps}{Astronomy and Astrophysics Supplements}
 \newcommand{\aj}{Astronomical Journal}
+\newcommand{\apj}{Astrophysical Journal}
+\newcommand{\jgr}{Journal of Geophysical Research}
+\newcommand{\pasa}{Publications of the Astronomical Society of Australia}
 \newcommand{\pasp}{Proceedings of the Astronomical Society of the Pacific}
 \newcommand{\prd}{Physical Review D}
-\newcommand{\apj}{Astrophysical Journal}
-\newcommand{\aaps}{Astronomy and Astrophysics Supplements}
+\newcommand{\prl}{Physical Review Letters}
 
@@
 
-\attention{Open task for any/all: fix references, make a proper bibtex file}
+\attention{Open task for any/all: fix references}
 
@@
 the formation of large-scale structures (see,
-e.g.,~\citep{ska_physics,2013PhRvD..87d3002L,2014ApJ...782...66P}.
+e.g.,~\citep{2020PASA...37....2W,2013PhRvD..87d3002L,2014ApJ...782...66P}.
 The dark ages, which occurred after recombination and correspond to a
@@
 unexplored to date and represent one of the final observational
-frontiers in cosmology.  This epoch contains a potential wealth of
-cosmological information~\citep{loeb_zaldarriaga, 2019arXiv190710853C,
-  2019arXiv190804296K}, but the required redshifted frequencies of
-$\lesssim 30$~MHz are exceptionally difficult to observe.  The primary
-experimental challenges include Galactic foreground emission,
-ionospheric interference, and terrestrial radio-frequency interference
-(RFI).
+frontiers in cosmology.  The number of independent modes that are
+contained in the matter power spectrum in this epoch is orders of
+magnitude greater than the corresponding number for cosmic microwave
+background (CMB) measurements~\citep{2004PhRvL..92u1301L}.  Redshifted
+21-cm measurements of the dark ages therefore hold the potential to
+significantly improve cosmological parameter constraints over those
+currently derived from the CMB; however, the required observational
+frequencies of $\lesssim 30$~MHz are exceptionally difficult to
+access.  The primary experimental challenges include Galactic
+foreground emission, ionospheric interference, and terrestrial
+radio-frequency interference (RFI).
 
-Very few experiments have measured the radio sky at $\lesssim 30$~MHz;
-here, we highlight only four specific examples.  At the very lowest
-frequencies, the state of the art among ground-based measurements
-dates from the 1950s, when Reber and Ellis caught brief glimpses of
-the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an array of
-192~dipoles~\citep{reber, article, 1988A&A...195..372W}.  A few
-space-based missions have also performed measurements at similarly low
-frequency ranges; for example, the Radio Astronomy Explorer-2 operated
-at \SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
+Very few experiments have surveyed the radio sky at $\lesssim 30$~MHz,
+and here, we highlight only four specific examples.  At the very
+lowest frequencies, the state of the art among ground-based
+measurements dates from the 1950s, when Reber and Ellis caught brief
+glimpses of the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an
+array of 192~dipoles~\citep{1956JGR....61....1R}.  A few space-based
+missions have also performed measurements at similarly low frequency
+ranges; for example, the Radio Astronomy Explorer-2 operated at
+\SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
 \SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
@@
 resolution measurements at the lowest frequencies.  The first step
-toward laying the groundwork for possible future cosmological
-measurements is obtaining an improved map of Galactic foregrounds at
-$\lesssim 30$~MHz.  Maps at these frequencies can additionally shed
-new light on Galactic astrophysics, including cosmic ray structure
-along the line of sight (\attention{more words here about synchrotron
-  self-absorption}), \attention{words here about radio recombination
-  lines}.  \attention{More words here about possible ionospheric
-  studies.}
+toward laying the groundwork for possible measurements of the dark
+ages is obtaining an improved map of Galactic foregrounds at $\lesssim
+30$~MHz.  In addition to serving as a stepping stone for future
+cosmological constraints from the dark ages, maps at these frequencies
+can also shed new light on Galactic astrophysics.  Above $\sim30$~MHz,
+synchrotron emission from the Galaxy follows a power law with a
+frequency dependence of $\nu^{-5/2}$.  At lower frequencies,
+synchrotron self-absorption becomes non-negligible, and the spectrum
+transitions to $\nu^{5/3}$ dependence.  Since self-absorption causes
+the optical depth along the line of sight to depend on frequency,
+observations at $\lesssim 30$~MHz have the potential to probe the
+three-dimensional cosmic ray structure of the
+Galaxy~\citep{2002ApJ...575..217P}.
+
+\attention{Words here about radio recombination lines.}
+\attention{More words here about possible ionospheric studies.}
+
+% Words here about space-based concepts, and more words about doing
+% what we can from the ground first
 

### 2020-05-13 albatros_paper.tex
HCC overhauled abstract

@@
 \begin{abstract}
-\attention {text to be overhauled later...} \\
-The low frequency radio astronomy has the highest potential in
-discovering the history of the Universe, this includes observations
-of the first stars and the mapping of dark ages. The Array of Long
-Baseline Antennas for Taking Radio Observations from the
-Sub-Antarctic (ALBATROS) is a new interferometric array. It consists
-of autonomous antenna stations that will map the low-frequency sky
-from Marion Island. One autonomous station was deployed in Marion
-Island in April 2019. The operating frequency range is
-\SIrange{1.2}{81}{\MHz} with baselines of $\approx \SI{20}{\km}$. A
-two element pathfinder was deployed in Marion Island in April
-2018.
+Measurements of redshifted 21-cm emission of neutral hydrogen at
+$\lesssim30$~MHz have the potential to probe the cosmic ``dark ages,''
+a period of the universe's history that remains unobserved to date.
+Observations at these frequencies are exceptionally challenging
+because of bright Galactic foregrounds, ionospheric contamination, and
+terrestrial radio-frequency interference.  Very few sky maps exist at
+$\lesssim30$~MHz, and most have modest resolution.  We introduce the
+Array of Long Baseline Antennas for Taking Radio Observations from the
+Sub-Antarctic (\albatros), a new experiment that aims to image
+low-frequency Galactic emission with an order-of-magnitude improvement
+in resolution over existing data.  The \albatros\ array will consist
+of antenna stations that operate autonomously, each recording baseband
+data that will be interferometrically combined offline.  The array
+will be installed on Marion Island and will ultimately comprise 10
+stations, with an operating frequency range of 1.2--125~MHz and
+maximum baseline lengths of $\sim20$~km.  We present the
+\albatros\ instrument design and discuss pathfinder observations that
+were taken from Marion Island during 2018--2019.
 \end{abstract}
@@
 elucidate the universe's history from the cosmic ``dark ages'' up to
-the formation of large-scale structures (see,
-e.g.,~\citep{2020PASA...37....2W,2013PhRvD..87d3002L,2014ApJ...782...66P}.
+the formation of large-scale
+structures~\citep{2020PASA...37....2W,2013PhRvD..87d3002L,2014ApJ...782...66P}.
 The dark ages, which occurred after recombination and correspond to a

### 2020-05-13 albatros_paper.tex
added plot of synthesized beam

@@
 the nominal \albatros\ installation locations, the computed
-synthesized beam is as shown in \autoref{Fig:marion}.  The beam width
+synthesized beam is as shown in \autoref{Fig:beam}.  The beam width
 at 5~MHz is roughly \SI{8}{\arcminute}, which represents over an order
@@
 autonomous operation.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.7\linewidth]{Figures/marion_beam_huts_2020.pdf}
+    %/Users/sievers/hirax/outriggers/marion_beam_huts_2020.pdf
+    \caption{Synthesized beam at 5 MHz from the full \albatros\ array.
+      We use an octave of bandwidth (3.5 to 7 MHz), and find the
+      ensuing synthesized beam has a FWHM of about 7 arcminutes.}
+    \label{Fig:beam}
+  \end{center}
+\end{figure}
 

### 2020-05-13 albatros_paper.tex
HCC merged Marion map and synthesized beam figures

--- 2020-05-13 albatros_paper.tex
@@
 
+\begin{figure}
+    \centering
+    \begin{subfigure}[t]{0.6\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{Figures/marion_map/marion_map_annotated.jpg} 
+        \caption{} \label{Fig:marion_map}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{0.39\textwidth}
+      \centering
+        \includegraphics[width=\linewidth]{Figures/marion_beam_huts_2020.jpg}
+        \caption{} \label{Fig:marion_beam}
+    \end{subfigure}
+    \caption{{\bf (a)} Map of Marion Island.  The
+      \albatros\ pathfinder antennas are currently installed at the
+      \prizm\ site and at the hydro shack (gray markers).  The black
+      markers denote the eight coastal huts, which will be used for
+      future \albatros\ antenna installations.  The white markers
+      denote other available infrastructure points that will not be
+      used for antennas.  {\bf (b)} Synthesized beam at 5~MHz from the
+      full \albatros\ array, using the existing and planned
+      installation locations shown on the map.  Using an octave of
+      bandwidth spanning 3.5--7~MHz, we obtain a synthesized beam with
+      a full width of $\sim7'$.}\label{Fig:marion_map_beam}
+\end{figure}
+
 \section{ALBATROS overview}
 
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.7\linewidth]{Figures/marion_map/marion_map_annotated.jpg}
-    \caption{Map of Marion Island.  The \albatros\ pathfinder antennas
-      are currently installed at the \prizm\ site and at the hydro
-      shack.  The black markers denote the eight coastal huts, which
-      will be used for future \albatros\ antenna installations.  The
-      white markers denote other available infrastructure points that
-      will not be used for antennas.  \attention{Add new
-        synthesized beam figure (Jon)}}
-    \label{Fig:marion}
-  \end{center}
-\end{figure}
+% \begin{figure}
+%   \begin{center}
+%     \includegraphics[width=0.7\linewidth]{Figures/marion_map/marion_map_annotated.jpg}
+%     \caption{Map of Marion Island.  The \albatros\ pathfinder antennas
+%       are currently installed at the \prizm\ site and at the hydro
+%       shack.  The black markers denote the eight coastal huts, which
+%       will be used for future \albatros\ antenna installations.  The
+%       white markers denote other available infrastructure points that
+%       will not be used for antennas.  \attention{Add new
+%         synthesized beam figure (Jon)}}
+%     \label{Fig:marion}
+%   \end{center}
+% \end{figure}
 
@@
 environment~\citep{2019JAI.....850004P}.  As illustrated in
-\autoref{Fig:marion}, \attention{this points to the map, not the beam pattern} Marion has an area of 335~km$^2$ and can
+\autoref{Fig:marion_map}, Marion has an area of 335~km$^2$ and can
 therefore support antenna installations with $>10$-km baseline
@@
 the main base and Katedraal for RFI and accessibility reasons,
-respectively.  \autoref{Fig:marion} also shows the locations of the
-\albatros\ pathfinder antennas that are currently installed at the
+respectively.  \autoref{Fig:marion_map} also shows the locations of
+the \albatros\ pathfinder antennas that are currently installed at the
 \prizm\ site and at the hydro shack.
@@
 the nominal \albatros\ installation locations, the computed
-synthesized beam is as shown in \autoref{Fig:marion}.  The beam width
-at 5~MHz is roughly \SI{8}{\arcminute}, which represents over an order
-of magnitude improvement in resolution over other existing
+synthesized beam is as shown in \autoref{Fig:marion_beam}.  The beam
+width at 5~MHz is roughly \SI{7}{\arcminute}, which represents over an
+order of magnitude improvement in resolution over other existing
 measurements.  One of the challenges in constructing an interferometer
@@
 periods of time for subsequent offline correlation.  We have conducted
-two enginering runs: 1) a two-element, directly correlated pathfinder
+two engineering runs: 1) a two-element, directly correlated pathfinder
 to qualitatively understand the sky signal, and 2) a single station to
@@
 autonomous operation.
+
+% \begin{figure}
+%   \begin{center}
+%     \includegraphics[width=0.7\linewidth]{Figures/marion_beam_huts_2020.pdf}
+%     %/Users/sievers/hirax/outriggers/marion_beam_huts_2020.pdf
+%     \caption{Synthesized beam at 5 MHz from the full \albatros\ array.
+%       We use an octave of bandwidth (3.5 to 7 MHz), and find the
+%       ensuing synthesized beam has a FWHM of about 7 arcminutes.}
+%     \label{Fig:beam}
+%   \end{center}
+% \end{figure}
 
@@
 
-% Two-element block diagram goes here
 \begin{figure}
@@
 % do we want/need to say anything about the omnidirectional primary beam?
-
-\attention{ALL TEXT BELOW HERE NEEDS WORK}
 

### 2020-05-13 albatros_paper.tex
HCC added jpg version of synthesized beam image, with trimmed margins
HCC added a few sentences and references about RRLs

@@
 \newcommand{\jgr}{Journal of Geophysical Research}
+\newcommand{\mnras}{Monthly Notices of the Royal Astronomical Society}
+\newcommand{\nar}{New Astronomy Reviews}
 \newcommand{\pasa}{Publications of the Astronomical Society of Australia}
@@
 three-dimensional cosmic ray structure of the
-Galaxy~\citep{2002ApJ...575..217P}.
+Galaxy~\citep{2002ApJ...575..217P}.  Low-frequency observations can
+also be used to image radio recombination lines (RRLs), which provide
+a means for studying cool, low-density regions of the interstellar
+medium (ISM).  These absorption lines arise from Rydberg atoms and are
+highly sensitive to the surrounding environment.  The RRL spectrum and
+absorption profiles can therefore constrain the detailed properties of
+the ISM regions in which the Rydberg atoms are
+formed~\citep{2009NewAR..53..259G, 2007MNRAS.374..852S}.
 
-\attention{Words here about radio recombination lines.}
-\attention{More words here about possible ionospheric studies.}
+\attention{Words here about possible ionospheric studies.}
 
-% Words here about space-based concepts, and more words about doing
-% what we can from the ground first
+\attention{Words here about space-based concepts and complementarity
+  with ground-based measurements.}
 
@@
 
+We are extremely grateful for the anemic carrots on Marion.  Yum.
+
 \bibliographystyle{apj}

### 2020-05-13 albatros_paper.tex
HCC minor tweaks

@@
   \begin{center} \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
-    \caption{Two-element \albatros\ pathfinder block diagram.
-      Signals from two dual-polarzation LWA antennas are amplified by
-      front-end active baluns (\attention{citation for FEE}).
-      Antennas are connected via 100m coax cables to the back-end 
-      readout electronics, which are housed in a Faraday cage denoted
-      by the dashed box.  Each of the four antenna outputs is passed
-      to a second-stage electronics chain consisting of filters and further amplfication.  The signals are
-      digitized at 250~Msamp/s by a SNAP board, which includes an on-board FPGA that computes auto and cross spectra
-      from and between the four inputs.  A Raspberry Pi controls the SNAP board and
-      saves the data.}
+    \caption{Two-element \albatros\ pathfinder block diagram.  Signals
+      from two dual-polarzation LWA antennas are amplified by
+      front-end active baluns~\citep{2012PASP..124.1090H}.  Antennas
+      are connected via 100m coax cables to the back-end readout
+      electronics, which are housed in a Faraday cage denoted by the
+      dashed box.  Each of the four antenna outputs is passed to a
+      second-stage electronics chain consisting of filters and further
+      amplfication.  The signals are digitized at 250~Msamp/s by a
+      SNAP board, which includes an on-board FPGA that computes auto
+      and cross spectra from and between the four inputs.  A Raspberry
+      Pi controls the SNAP board and saves the data.}
     \label{Fig:albatros2_schem}
@@
 input impedance, as well as the hybrid insertion loss ($<$1dB), the front-end electronics 
-provide a gain of $\sim$37dB \cite{2012PASP..124.1090H}.
+provide a gain of $\sim$37~dB~\citep{2012PASP..124.1090H}.
 

### 2020-06-09 albatros_paper.tex
HCC added ionosphere stuff and discussion of space missions

@@
 \newcommand{\apj}{Astrophysical Journal}
+\newcommand{\grl}{Geophysical Research Letters}
 \newcommand{\jgr}{Journal of Geophysical Research}
@@
 synchrotron emission from the Galaxy follows a power law with a
-frequency dependence of $\nu^{-5/2}$.  At lower frequencies,
+frequency dependence of $\nu^{-0.7}$.  At lower frequencies,
 synchrotron self-absorption becomes non-negligible, and the spectrum
-transitions to $\nu^{5/3}$ dependence.  Since self-absorption causes
+transitions to $\nu^{+5/2}$ dependence.  Since self-absorption causes
 the optical depth along the line of sight to depend on frequency,
@@
 the ISM regions in which the Rydberg atoms are
-formed~\citep{2009NewAR..53..259G, 2007MNRAS.374..852S}.
+formed~\citep{2009NewAR..53..259G, 2007MNRAS.374..852S}.  Finally,
+observations at $\lesssim30$~MHz may provide new views of Earth's
+ionosphere, which absorbs and refracts at radio frequencies and
+becomes completely opaque below the plasma cutoff frequency.  The
+cutoff frequency and the levels of absorption and refraction are
+time-varying and spatially dependent.  Experiments that image the
+radio sky at multiple frequencies bracketing the plasma cutoff can
+therefore simultaneously image the ionosphere and provide spectral
+riometry data for space weather studies~\citep{2014GeoRL..41.5370K}.
 
-\attention{Words here about possible ionospheric studies.}
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.6\linewidth]{Figures/marion_domec_hobart.png}
+    \caption{Minimum plasma frequency predicted by the International
+      Reference Ionosphere model during the last solar minimum.  At
+      some locations on Earth, the plasma frequency may drop as low as
+      $\sim1.5$~MHz.}
+    \label{Fig:iri}
+  \end{center}
+\end{figure}
 
-\attention{Words here about space-based concepts and complementarity
-  with ground-based measurements.}
-
-Preliminary observations from Marion
-Island~\citep{2019JAI.....850004P} suggest that despite the
-present-day RFI environment, low-frequency observations may still be
-accessible from carefully selected locations and with new technology
-developments.  In this paper, we present the Array of Long Baseline
-Antennas for Taking Radio Observations from the Sub-Antarctic
-(\albatros), a new experimental effort that aims to map the
-low-frequency sky using an array of autonomous antenna stations.  We
-describe the overall instrument design and preliminary measurements
-from engineering runs that were performed on Marion Island during
-2018--2019.
+There are proposed efforts to perform new low-frequency measurements
+from space, where there is no contamination from the ionosphere, and
+the lunar farside can potentially block RFI from the
+Earth~\citep{2019arXiv190710853C, 2019arXiv190804296K}.  Although the
+combination of ionosphere and RFI significantly impedes low-frequency
+radio observations from most locations on Earth, preliminary
+observations from Marion Island~\citep{2019JAI.....850004P} suggest
+that such observations may still be accessible from carefully selected
+locations and with new technology developments.  In this paper, we
+present the Array of Long Baseline Antennas for Taking Radio
+Observations from the Sub-Antarctic (\albatros), a new experimental
+effort that aims to map the low-frequency sky using an array of
+autonomous antenna stations.  We describe the overall instrument
+design and preliminary measurements from engineering runs that were
+performed on Marion Island during 2018--2019.
 
@@
 
-% \begin{figure}
-%   \begin{center}
-%     \includegraphics[width=0.7\linewidth]{Figures/marion_map/marion_map_annotated.jpg}
-%     \caption{Map of Marion Island.  The \albatros\ pathfinder antennas
-%       are currently installed at the \prizm\ site and at the hydro
-%       shack.  The black markers denote the eight coastal huts, which
-%       will be used for future \albatros\ antenna installations.  The
-%       white markers denote other available infrastructure points that
-%       will not be used for antennas.  \attention{Add new
-%         synthesized beam figure (Jon)}}
-%     \label{Fig:marion}
-%   \end{center}
-% \end{figure}
-
 % Write text here about the overall final configuration.  Describe the
@@
 inversely with frequency, and therefore $\sim 10$-km lengths are
-required at few-MHz frequencies in order to improve upon the
-resolutions achieved to date.  The experiment installation site must
-be remote to keep RFI to a minimum, and polar or near-polar latitiudes
-generally have lower ionospheric plasma frequency cutoffs.
-\attention{Add more ionosphere text here, plus IRI simulation
-  fig/numbers (Jon)}
+required at few-MHz frequencies to improve upon the resolutions
+achieved to date.  The experiment installation site must be remote to
+keep RFI to a minimum, and polar or near-polar latitiudes generally
+have lower ionospheric plasma frequency cutoffs relative to other
+locations on Earth.  \autoref{Fig:iri} illustrates predictions from
+the International Reference Ionosphere
+model~\citep{2018AdRS...16....1B} for the minimum plasma frequency
+during the last solar minimum, which started in approximately 2007.
+Three locations are shown: Marion Island, the focus of this work;
+Dome~C in Antarctica, which is another isolated location used for
+astronomical observations; and Hobart, Tasmania, where Reber performed
+his $\sim2$~MHz observations.  The model predictions illustrate that
+the ionospheric plasma cutoff frequency at Marion Island may drop as
+low as $\sim1.5$~MHz during solar minima.  Since we are currently
+experiencing another solar minimum~\citep{2018NatCo...9.5209B}, the
+timing is opportune for new low-frequency observations.
 
@@
 autonomous operation.
-
-% \begin{figure}
-%   \begin{center}
-%     \includegraphics[width=0.7\linewidth]{Figures/marion_beam_huts_2020.pdf}
-%     %/Users/sievers/hirax/outriggers/marion_beam_huts_2020.pdf
-%     \caption{Synthesized beam at 5 MHz from the full \albatros\ array.
-%       We use an octave of bandwidth (3.5 to 7 MHz), and find the
-%       ensuing synthesized beam has a FWHM of about 7 arcminutes.}
-%     \label{Fig:beam}
-%   \end{center}
-% \end{figure}
 

### 2020-06-09 albatros_paper.tex
HCC tweaked schematic figures, added more 2-element text

@@
       shipping container that houses the readout electronics and
-      serves as the ``command module.'' \attention{Add FEE
-        and backend sub-pics here? (HCC)}}
+      serves as the ``command module.''}
     \label{Fig:albatros2}
@@
       from two dual-polarzation LWA antennas are amplified by
-      front-end active baluns~\citep{2012PASP..124.1090H}.  Antennas
-      are connected via 100m coax cables to the back-end readout
-      electronics, which are housed in a Faraday cage denoted by the
-      dashed box.  Each of the four antenna outputs is passed to a
-      second-stage electronics chain consisting of filters and further
-      amplfication.  The signals are digitized at 250~Msamp/s by a
-      SNAP board, which includes an on-board FPGA that computes auto
-      and cross spectra from and between the four inputs.  A Raspberry
-      Pi controls the SNAP board and saves the data.}
+      front-end active baluns~\citep{2012PASP..124.1090H}.  The
+      antennas are connected via 100-m coaxial cables to the back-end
+      readout electronics, which are housed in a Faraday cage denoted
+      by the dashed box.  Each of the four antenna outputs is passed
+      to a second-stage electronics chain consisting of filters and
+      further amplfication.  The signals are digitized at 250~Msamp/s
+      by a SNAP board, which includes an on-board FPGA that computes
+      auto- and cross-spectra from and between the four inputs.  A
+      Raspberry Pi controls the SNAP board and saves the data.}
     \label{Fig:albatros2_schem}
@@
 The first exploratory \albatros\ measurements were conducted with a
-two-element pathfinder that employed direct correlation (without
+two-element pathfinder that used direct correlation (without
 autonomous operation).  \autoref{Fig:albatros2} illustrates this
@@
 \subsection{Antenna}
+
 We employ two dual-polarization Long Wavelength Array (LWA) dipole
@@
 
-\subsection{Front-end active balun}
-\attention{Tankiso, Eamon, Jeff?} \\
-\label{section:FEE}
+\subsection{Front-end active balun}\label{section:FEE}
 
-The LWA active-balun front-end electronics (FEE) circuit uses a MiniCircuits GALI-74+ MMIC 
-to amplify each dipole leg against ground, presenting each leg with a 50$\ohm$ impedance 
-and providing a nominal gain of 25dB. The two GALI-74+ outputs are differenced using a 
-passive {180\degree} hybrid coupler. The coupler output is filtered by a $\sim$150MHz lowpass, 
-and receives an additional 12dB of gain from a MiniCircuits GALI-6+ MMIC. This last amplifier 
-drives the output signal onto a 100m 50$\ohm$ coaxial cable. Thus, neglecting mismatch loss 
-between the dipoles (electrically small in the frequency range of interest) and the 100{\ohm} 
-input impedance, as well as the hybrid insertion loss ($<$1dB), the front-end electronics 
-provide a gain of $\sim$37~dB~\citep{2012PASP..124.1090H}.
-
-Each FEE circuit is powered by 16V, fed on the coax through a bias tee.
+The LWA active-balun front-end electronics (FEE) circuit uses a
+MiniCircuits GALI-74+ MMIC to amplify each dipole leg against ground,
+presenting each leg with a 50$\ohm$ impedance and providing a nominal
+gain of 25~dB. The two GALI-74+ outputs are differenced using a
+passive {180\degree} hybrid coupler. The coupler output is filtered by
+a $\sim$150~MHz lowpass and receives an additional 12~dB of gain from
+a MiniCircuits GALI-6+ MMIC. This last amplifier drives the output
+signal onto a 100-m 50$\ohm$ coaxial cable. Thus, neglecting mismatch
+loss between the dipoles (electrically small in the frequency range of
+interest) and the 100{\ohm} input impedance, as well as the hybrid
+insertion loss ($<$1dB), the front-end electronics provide a gain of
+$\sim$37~dB~\citep{2012PASP..124.1090H}.  Each FEE circuit is powered
+by 16~V, which is fed on the coaxial cable through a bias tee.
 
@@
 
-% It seems to me that this is too much detail to go into in describing an already published design.
-\iffalse
+%% It seems to me that this is too much detail to go into in describing an already published design.
+% All the front end components were incorporated for in a double sided
+% printed circuit board (PCB) as shown in \autoref{Fig:Balun} and the
+% block diagram is shown in \autoref{Fig:Balun Schematic}. The
+% Monolithic Microwave Integrated Circuits (MMICs) is the used design
+% for the PCB. One side of the PCB is populated with components and
+% the other side is a solid copper ground plane aperiodically stitched
+% to the grounded copper on the side populated with components. The
+% receiver system is made up of the active balun, filter and the gain
+% stage that connects to the \SI{100}{\metre} coaxial cable which is
+% connected to the back end \cite{2012PASP..124.1090H}.
 
-All the front end components were incorporated for in a double sided
-printed circuit board (PCB) as shown in \autoref{Fig:Balun} and the
-block diagram is shown in \autoref{Fig:Balun Schematic}. The
-Monolithic Microwave Integrated Circuits (MMICs) is the used design
-for the PCB. One side of the PCB is populated with components and the
-other side is a solid copper ground plane aperiodically stitched to
-the grounded copper on the side populated with components. The
-receiver system is made up of the active balun, filter and the gain
-stage that connects to the \SI{100}{\metre} coaxial cable which is
-connected to the back end \cite{2012PASP..124.1090H}.
-
-The input impedance (Z\textsubscript{o}) of \SI{50}{\ohm} is
-introduced to the dipole by the active balun. The signal is then fed
-through an amplifier which amplifies it by \SI{+24}{\decibel} of
-gain. The balanced signal is then converted to unbalanced through a
-180 \degree hybrid coupler. The band pass filter (BPF) receives the
-single ended signal in order for it to reject all the frequencies
-which are not within the range of interest. The signal gets fed to a
-second amplifier which again amplies it by \SI{+24}{\decibel} of gain
-and the output impedance of the FEE is matched to a \SI{50}{\ohm}
-coaxial cable. The bias tee is responsible for providing power to the
-FEE and extracts the RF signal by the use of the coaxial cable. This
-unit has an overall gain of $\approx$ \SI{35}{\decibel} and an overall
-noise figure of $\approx$ \SI{2.7}{\decibel} to $\approx$
-\SI{2.9}{\decibel} \cite{Memo35}.
-
-\fi
+% The input impedance (Z\textsubscript{o}) of \SI{50}{\ohm} is
+% introduced to the dipole by the active balun. The signal is then fed
+% through an amplifier which amplifies it by \SI{+24}{\decibel} of
+% gain. The balanced signal is then converted to unbalanced through a
+% 180 \degree hybrid coupler. The band pass filter (BPF) receives the
+% single ended signal in order for it to reject all the frequencies
+% which are not within the range of interest. The signal gets fed to a
+% second amplifier which again amplies it by \SI{+24}{\decibel} of gain
+% and the output impedance of the FEE is matched to a \SI{50}{\ohm}
+% coaxial cable. The bias tee is responsible for providing power to the
+% FEE and extracts the RF signal by the use of the coaxial cable. This
+% unit has an overall gain of $\approx$ \SI{35}{\decibel} and an overall
+% noise figure of $\approx$ \SI{2.7}{\decibel} to $\approx$
+% \SI{2.9}{\decibel} \cite{Memo35}.
 
 \subsection{Back-end electronics}
-\attention{Nivek, HCC?} \\
 
-The back-end readout electronics are housed in a Faraday cage
-located 100m away from the antennas to mitigate possible
-self-generated RFI.  Each of the four antenna
-signals is passed to a second-stage electronics chain consisting of 
-% EE bias tee is already described; it isn't really part of the signal chain since it doesn't do much of anything
-%a bias tee (Minicircuits ZFBT-4R2GW-FT+), 
-an
-amplifier (Minicircuits
-ZX60-V63+), and a pair of high- and low-pass filters (Minicircuits
-ZFHP-1R2+ and SLP-90+) that together  bandlimit the signal to
-1.2--\SI{81}{MHz}.  The amplifier has a nominal gain of 20dB, and the HPF and LPF contribute nominal insertion losses of 0.2dB and 0.14dB respectively.
+The back-end readout electronics are housed in a Faraday cage located
+100~m away from the antennas to mitigate possible self-generated RFI.
+Each of the four antenna signals is passed to a second-stage
+electronics chain consisting of an amplifier (Minicircuits ZX60-V63+),
+and a pair of high- and low-pass filters (Minicircuits ZFHP-1R2+ and
+SLP-90+) that together band-limit the signal to 1.2--\SI{81}{MHz}.
+The amplifier has a nominal gain of 20~dB, and the high- and low-pass
+filters contribute nominal insertion losses of 0.2~dB and 0.14~dB,
+respectively.
 
-A Xilinx Kintex\footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html} based Smart Network ADC Processor (SNAP) board (\attention{citation for SNAP board?}), 
-clocked by a Valon 5007 frequency synthesizer module,
-digitizes the RF signals at 250~Msamp/s. It calculates a full
-cross-correlation of the four inputs, producing four auto- and six
-cross-spectra as outputs, over 2048 channels spanning the frequency range 
-\SI{0}{MHz} - \SI{125}{MHz}. 
-(\attention{details about SNAP board frequency transform?})
-The SNAP board sends its output data via ethernet to a Raspberry Pi (\attention{version?
-citation?}), which saves baseband data to a set of hard drives, while storing the less voluminous correlation data on its SD card.
+A Smart Network ADC Processor~\citep[SNAP;][]{2016JAI.....541001H}
+board digitizes the RF signals at 250~Msamp/s and uses a Xilinx
+Kintex~7\footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}
+FPGA to calculate full cross-correlations of the four inputs,
+producing four auto- and six cross-spectra as outputs, over 2048
+channels spanning the frequency range 0--125~MHz.  \attention{details
+  about channelization here} A Valon 5007 frequency synthesizer module
+provides the clock signal for the SNAP board.  A Raspberry Pi~3B+
+(RPi) single board computer controls the SNAP board and receives the
+spectra via GPIO connections, and the spectra are saved to an on-board
+SD card.  An Adafruit Ultimate GPS
+module\footnote{\url{https://www.adafruit.com/product/746}}, connected
+to an active external GPS antenna, provides absolute timing for the
+RPi.
 
@@
 
-A bank of four parallel \SI{12}{V}, \SI{200}{\ampere\hour} batteries serves to power the two-element pathfinder system.
-A Honda EU30is generator is run periodically to charge the battery bank, which can run the system for approximately four days on a full charge.
-DC/DC converters power the SNAP board, the FEE, the amplifiers and the clock.
-% Cuts (redundant or too much detail)
-% and the fuel is kept in one of the shipping containers at the \prizm\ site
-% The power from the battery bank is connected to the Faraday cage where the power regulation is performed.
+A bank of four 12-V, 200-Ah AGM batteries, connected in parallel,
+powers the two-element pathfinder system.  The batteries are manually
+charged with a Honda EU30is generator that is housed on site.  The
+total power draw of the two-element pathfinder is $\sim45$~W, and when
+fully charged, the battery bank can power the system for about a week.
+The raw battery voltage is passed to several DC/DC converters that
+supply regulated voltages to the SNAP board, FEE, amplifiers and the
+clock.
+
 \subsection{Software and data acquisition}
@@
     \caption{Single-antenna autonomous station block diagram. 
-      Data and RF connections are outlined in black, and power
-      connections in red.  
       A dual-polarization LWA

### 2020-06-10 albatros_paper.tex
HCC added figure of command module for single station

@@
 \begin{figure}
-  \begin{center}
-    \includegraphics[width=0.7\linewidth]{Figures/autonomous.jpg}
-    \caption{Single autonomous station pathfinder installed at the
-      hydro shack site.  The system is powered by a bank of solar
-      panels that are visible in the background.  \attention{
-        Add command module and electronics glamor shots.}}
-    \label{Fig:autonomous}
-  \end{center}
+    \centering
+    \begin{subfigure}[t]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{Figures/autonomous.jpg} 
+        \caption{} \label{Fig:autonomous_antenna}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{0.48\textwidth}
+      \centering
+        \includegraphics[width=\linewidth]{Figures/container.jpg}
+        \caption{} \label{Fig:autonomous_electronics}
+    \end{subfigure}
+    \caption{{\bf (a)} Single autonomous station pathfinder installed
+      at the hydro shack site.  The system is powered by a bank of
+      solar panels that are visible in the background. {\bf (b)} A
+      weather-proof container, which sits near the solar panels,
+      houses the batteries, solar charge controller, and readout
+      electronics.}\label{Fig:autonomous}
 \end{figure}
 
-% single element block diagram goes here
 \begin{figure}

### 2020-06-10 albatros_paper.tex
HCC working on text for single autonomous station

@@
 
-\subsection{Antenna}
+\subsection{Antenna}\label{s:antenna}
 
@@
 
-\subsection{Front-end active balun}\label{section:FEE}
+\subsection{Front-end active balun}\label{s:fee}
 
@@
 \subsection{Software and data acquisition}
-\attention{Nivek?} \\
-Text goes here.
+
+\attention{text goes here}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
 
@@
     \includegraphics[width=\linewidth]{Figures/albatros_single_schematic/albatros_single_schematic.pdf}
-    \caption{Single-antenna autonomous station block diagram. 
-      A dual-polarization LWA
-      antenna, equipped with an active balun (described above in \ref{section:FEE}), connects via 50m
-      coaxial cables to the back-end readout electronics, 
-      housed in a Faraday cage denoted by the dashed box. 
-      The antenna signals are passed
-      to a second-stage electronics chain consisting of filters and further amplfication.  The signals are
-      digitized at 250~Msamp/s by a SNAP board, which includes an on-board FPGA that computes spectra from both antennas.  
-      A Raspberry Pi controls the SNAP board, receives the spectrum of interest from the SNAP, and saves it as baseband data.}
-    \label{Fig:Signal Chain}
+    \caption{Single-antenna autonomous station block diagram.  A
+      dual-polarization LWA antenna, equipped with a front-end active
+      balun, connects via 50-m coaxial cables to the back-end readout
+      electronics, housed in a Faraday cage denoted by the dashed box.
+      Each of the two antenna signals is passed to a second-stage
+      electronics chain consisting of filters and further
+      amplfication.  The signals are digitized at 250~Msamp/s by a
+      SNAP board, which includes an on-board FPGA that computes
+      channelized baseband and spectra from both inputs.  A Raspberry
+      Pi controls the SNAP board and receives the baseband data and
+      spectra.  The baseband data are saved to external hard drives.
+      The system is powered by solar panels that charge a 24-V battery
+      bank.}
+    \label{Fig:albatros1_schem}
   \end{center}
 \end{figure}
-\attention{Nivek?} \\
 
-The full ALBATROS configuration will comprise an array of 10 autonomous antenna stations, recording the lowest 10-20MHz baseband to disk, to be collected periodically and subsequently correlated offline.
-The ALBATROS stations (located at the eight coastal hut sites plus the hydro shack and \prizm\ site) will
-be separated by baselines of \SI{\approx {20}}{km} as shown in
-\autoref{Fig:Marion}. One fully autonomous ALBATROS
-station, shown in \autoref{Fig:autonomous}, was deployed in April 2019 at the hydro shack location (\ang{46;52.205;}S, \ang{37;50.612;}E) on Marion Island, as a first step in testing the technology needed to establish this array.
+The full ALBATROS configuration will comprise an array of 10
+autonomous antenna stations, each recording baseband over a tunable
+10--20~MHz window within the full 0--125~MHz operating range.  The
+baseband data will be collected periodically and subsequently
+correlated offline.  The ALBATROS stations, located at the eight
+coastal hut sites plus the hydro shack and \prizm\ site, will be
+separated by baselines of $\sim20$~km as shown in
+\autoref{Fig:marion_map_beam}. One fully autonomous ALBATROS station,
+shown in \autoref{Fig:autonomous}, was deployed in April 2019 at the
+hydro shack location (\ang{46;52.205;}S, \ang{37;50.612;}E) on Marion
+Island as a first step in testing the technology needed to establish
+the full array.  The system block diagram is shown in
+\autoref{Fig:albatros1_schem}.  The antenna and front-end active balun
+in the single autonomous station are identical to those used in the
+two-element pathfinder (\S\ref{s:antenna} and \S\ref{s:fee}), and the
+back-end electronics and power system are described in detail below.
 
-% HCC: we probably don't need these figures below, or we can
-% incorporate them as subfigs into other places
-
+% HCC: we probably don't need this figure
 % \begin{figure}[h]
@@
 % \end{figure}
-% 
-% \begin{figure}[h]
-% 	\begin{center}
-% 		\includegraphics[width=0.7\linewidth]{Figures/Balun_Block.png}
-% 		\caption{One Polarisation Block Diagram of the FEE \cite{2012PASP..124.1090H}}
-% 		\label{Fig:Balun Schematic}
-% 	\end{center}
-% \end{figure}
 
-\subsection{Readout electronics}
-\attention{Nivek, Jon?} \\
+\subsection{Back-end electronics}
 
-The single antenna signal chain is shown in \autoref{Fig:Signal Chain}. 
-% start of copied text
-The back-end readout electronics are housed in a Faraday cage
-located 50m away from the antennas. The analog signal chain consists 
-a pair of high- and low-pass filters (Minicircuits
-ZFHP-1R2+ and SLP-90+) that, as in the two-element configuration, together bandlimit the signal to
-1.2--\SI{81}{MHz}.
-The filters are followed by a MiniCircuits ZFL-500+ amplifier.
-The HPF and LPF contribute nominal insertion losses of 0.2dB and 0.14dB respectively, and the amplifier has a nominal gain of 25dB.
+The back-end readout electronics are housed in a Faraday cage located
+50~m away from the antennas. The analog signal chain consists of a
+pair of high- and low-pass filters (Minicircuits ZFHP-1R2+ and
+SLP-150+) that together band-limit the signal to 1.2--140~MHz, and the
+filters are followed by a MiniCircuits ZFL-500+ amplifier.  In
+contrast to the two-element pathfinder, the low-pass cutoff is
+increased from 81~MHz to 140~MHz to capture downlink signals at
+137--138~MHz from the ORBCOMM satellite constellation.
+\attention{words here about how we'll use orbcomm for backup timing
+  information}
 
-As with the dual-antenna configuration described above, a SNAP board digitizes the RF  at 250~Msamp/s.
-In this configuration, the SNAP board ADC is locked to a 10MHz reference produced by a Trimble Thunderbole E GPS disciplined clock module.
-The Raspberry Pi receives the spectrally decomposed baseband data \attention{which frequencies are we storing?} and stores it onto a set of hard drives.
-(\attention{reference the same frequency transform as in the 2-element case})
-%end of copied text
-
-\attention{Text here about one-bit stuff, pushing baseband through the RPi3,
-clock requirements, data rates, etc.}
+As with the two-element pathfinder, a SNAP board digitizes each of the
+two RF signals at 250~Msamp/s. In the autonomous station
+configuration, the SNAP board ADCs are locked to a 10-MHz reference
+produced by a Trimble Thunderbolt~E GPS-disciplined clock module.  The
+SNAP board FPGA computes two data products: 1) channelized baseband
+data for each polarization over tunable frequency windows within the
+0--125~MHz operating range, with the options of 1-, 2-, or 4-bit
+compression, and 2) auto- and cross-spectra from the two polarizations
+over the full 0--125~MHz span, accumulated over few-second intervals.
+An RPi~3B+ controls the SNAP board and and receives the auto- and
+cross-spectra via GPIO connections, and the spectra are saved to an
+on-board SD card.  The baseband data are passed from the SNAP board to
+the RPi via ethernet and written to external hard drives.  The
+introduction of gigabit ethernet with the RPi~3B+ model has enabled
+the high data throughput associated with writing baseband.  As a
+benchmark, 1-bit baseband recording of two polarizations over 10~MHz
+of bandwidth yields an approximate data rate of 5~MB/s, or 0.4~TB/day.
 
 \subsection{Correlation}
+
 While the basics of 1-bit correlation are well known in the limit where the signal level is much lower than the noise, ALBATROS may well be in the high-signal regime.

### 2020-06-10 albatros_paper.tex
fixed 1bit reference
HCC tidied up power control section

@@
 \subsection{Solar power system}
-\attention{Nivek, Tankiso, Eamon?} \\
-Although the first-deployed two-element pathfinder is located at a reasonable walking distance from the main base and uses a generator to periodically recharge batteries, the bulk of the antenna stations that will comprise the full array will be located at points farther removed from the main base, and will require a fully autonomous energy source.
-So in deploying the autonomous station pathfinder, we developed a solar charging system to power the station.
 
-The autonomous station is powered by two series-connected 12V deep-cycle lead-acid batteries, charged by an array of nine  SunPower SPE-E-Flex-110 solar panels.
-These panels each have a standard test capacity of 110W.
-Although only $\sim$50W is required to run the station (and the station may typically be powered on only over night) the $\sim$1kW charging capacity is sized to allow the charge level to recover quickly on a short sunny day in winter if it runs down due to several consecutive overcast days.
+Although the first-deployed two-element pathfinder is located at a
+reasonable walking distance from the main base and uses a generator to
+periodically recharge batteries, the bulk of the antenna stations that
+will comprise the full array will be located at points farther removed
+from the main base and will therefore require fully autonomous energy
+sources.  For the autonomous station pathfinder, we developed a solar
+charging system to power the station, and we are investigating small
+wind turbines for future ALBATROS stations.
 
-The nine solar panels are distributed between three custom-designed structures built from aluminum extrusion, with rigid metalized plastic panels backing the semi-flexible solar cells.
-The structures are oriented due north, and are designed to incline the solar panels at a relatively steep angle so as to maximize peformance under winter conditions, when sunlight hours will be at their minimum.
-The solar panel mounts have been designed to withstand frequent gale-force winds on Marion.
-While the mounting structures themselves appear to be strong enough, the greatest challenge in deployment has been to find an adequate anchoring technique in the volcanic ground.
+The autonomous station is powered by two series-connected, 12~V, deep
+cycle, lead acid batteries, charged by an array of nine SunPower
+SPE-E-Flex-110 solar panels. These panels each have a standard test
+capacity of 110~W. Although only $\sim$50~W is required to run the
+station, the $\sim$1~kW charging capacity is intentionally oversized
+to account for the frequent overcast conditions on Marion.  The
+generous power margin allows the charge level to recover quickly on a
+short sunny day in winter in the event of charge loss over several
+consecutive overcast days.  The nine solar panels are distributed
+between three custom designed structures built from aluminum
+extrusion, with rigid metalized plastic panels backing the
+semi-flexible solar cells. The structures are oriented due north and
+are designed to incline the solar panels at a relatively steep angle
+to maximize peformance under winter conditions, when sunlight hours
+are at their minimum. The solar panel mounts have been designed to
+withstand frequent gale-force winds on Marion. While the mounting
+structures themselves appear to be strong enough, the greatest
+challenge in deployment has been to find adequate anchoring in the
+volcanic ground.  Each group of three panels is wired in series, and
+the three series strings are connected in parallel to a Victron
+BlueSolar MPPT 50$\vert$35 charge controller, which optimizes power
+transfer from the solar array when charging is required, and also
+monitors charge level, reducing output current when the battery bank
+is fully charged.
 
-Each group of three panels is wired in series, and the three series strings are connected in parallel to a Victron BlueSolar MPPT 50$\vert$35 charge controller, which optimizes power transfer from the solar array when charging is required, and also monitors charge level, reducing charge current when the battery bank is fully charged.
-
-A power logging and control system runs on an Arduino, which logs information received from the Victron charge controller to an SD card, and switches power on and off to the receiver chassis.
-Logged power data will be used to refine powers system requirements for future autonomous station deployments.
-The on/off control is necessary to prevent battery system  damage from overly deep discharge.
-The system can also be configured to conserve battery power by running on a schedule between particular hours, typically overnight, since visibility may be better and ionosopheric noise levels lower.
-
-The power logging and control system, along with the Victron charge controller and an EMI filter, are housed together in an aluminum box.
-The EMI filter reduces conducted emissions on the photovoltaic side of the solar charge controller, which could radiate from the solar array and connecting wires.
-(It may be noted however, that signals collected at night, which are expected to be more valuable, are not at risk of solar charge controller EMI contamination.)
-
-\iffalse
-The ALBATROS system is powered using \SI{24}{\volt} power which is stored and provided by two series-connected \SI{12}{\volt} deep-cycle lead-acid storage batteries.
-This power comes from the solar panel array consisting of nine flexible solar panels, each with a standard test condition capacity of \SI{110}{\watt}.
-The solar panel type is SunPower SPE-E-Flex-110.
-The panels are grouped in three parallel connected strings of three panels.
-Each group of three is mounted on its own structure.
-The panels include diodes to bypass shaded or defective cells, and also to prevent backwards current flow in the event an entire string of three panels is not illuminated while the others are producing power.
-\\
-
-The Victron BlueSolar MPPT 50$\vert$35 charge controller outputs a data packet every second, to an Arduino based data logger, which controls a switch that determines when the rest of the system runs.
-It also converts the solar panel voltage to \SI{24}{\volt} to control the battery charging.
-The observed parameters are then stored to the raspberry pi.
-\fi
+The power logging and control system runs on an Arduino, which logs
+information received from the Victron charge controller to an SD card,
+and switches power on and off to the readout electronics box. Logged
+power data will be used to refine power system requirements for future
+autonomous station deployments. The on/off control is necessary to
+prevent battery system damage from overly deep discharge. The system
+can also be configured to conserve battery power by running on a
+schedule between particular hours, typically overnight, when
+ionospheric conditions are more favorable.  The power logging and
+control system, along with the Victron charge controller and an EMI
+filter, are housed together in an aluminum box. The EMI filter reduces
+conducted emissions on the photovoltaic side of the solar charge
+controller, which could radiate from the solar array and connecting
+wires. (Data collected during the night are not at risk of solar
+charge controller EMI contamination.)
 

### 2020-06-12 albatros_paper.tex
HCC slowly hacking away at resolving more red text messages...

@@
 
-\attention{Open task for any/all: fix references}
-
 \section{Introduction}
@@
 the formation of large-scale
-structures~\citep{2020PASA...37....2W,2013PhRvD..87d3002L,2014ApJ...782...66P}.
-The dark ages, which occurred after recombination and correspond to a
-period when the universe was filled with neutral hydrogen, are
-unexplored to date and represent one of the final observational
-frontiers in cosmology.  The number of independent modes that are
-contained in the matter power spectrum in this epoch is orders of
-magnitude greater than the corresponding number for cosmic microwave
-background (CMB) measurements~\citep{2004PhRvL..92u1301L}.  Redshifted
-21-cm measurements of the dark ages therefore hold the potential to
+structures~\citep[e.g.,][]{2012RPPh...75h6901P}.  The dark ages, which
+occurred after recombination and correspond to a period when the
+universe was filled with neutral hydrogen, are unexplored to date and
+represent one of the final observational frontiers in cosmology.  The
+number of independent modes that are contained in the matter power
+spectrum in this epoch is orders of magnitude greater than the
+corresponding number for cosmic microwave background (CMB)
+measurements~\citep{2004PhRvL..92u1301L}.  Redshifted 21-cm
+measurements of the dark ages therefore hold the potential to
 significantly improve cosmological parameter constraints over those
@@
 board digitizes the RF signals at 250~Msamp/s and uses a Xilinx
-Kintex~7\footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}
+Kintex~7\footnote{\url{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}}
 FPGA to calculate full cross-correlations of the four inputs,
 producing four auto- and six cross-spectra as outputs, over 2048
-channels spanning the frequency range 0--125~MHz.  \attention{details
-  about channelization here} A Valon 5007 frequency synthesizer module
-provides the clock signal for the SNAP board.  A Raspberry Pi~3B+
-(RPi) single board computer controls the SNAP board and receives the
-spectra via GPIO connections, and the spectra are saved to an on-board
-SD card.  An Adafruit Ultimate GPS
+channels spanning the frequency range 0--125~MHz.  The channelization
+is performed with a
+CASPER\footnote{\url{https://casper.berkeley.edu/}}-based polyphase
+filter bank, and the spectra are accumulated over $\sim7$-s intervals.
+A Valon 5007 frequency synthesizer module provides the clock signal
+for the SNAP board.  A Raspberry Pi (RPi)~3B+ single board computer
+controls the SNAP board and receives the spectra via GPIO connections.
+The data rate of the averaged spectra is roughly 400~MB/day (with
+compression), and this low volume allows the spectra to be saved to
+the RPi on-board SD card.  An Adafruit Ultimate GPS
 module\footnote{\url{https://www.adafruit.com/product/746}}, connected
@@
 RPi.
+
+% data rate ~ 17MB/hour, with compressed scio files
 
@@
 clock.
-
-\subsection{Software and data acquisition}
-
-\attention{text goes here}
 
@@
 For baseline separations of many wavelengths, the correlated component of the electric field is likely to be a small fraction of the total power, so ALBATROS is unlikely to lose more than a factor of $\sim 2$ by using 1-bit correlation.}
-    \label{Fig:1bit_efficiency}
+    \label{fig:1bit_efficiency}
     \end{center}
@@
 
+\begin{figure}
+    \centering
+    \begin{subfigure}[t]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{Figures/Raw-ALBATROS-autospectra.PNG}
+        \caption{} \label{Fig:waterfall_auto}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{0.48\textwidth}
+      \centering
+        \includegraphics[width=\linewidth]{Figures/First-fringes-of-ALBATROS-EGG.PNG}
+        \caption{} \label{Fig:waterfall_phase}
+    \end{subfigure}
+    \caption{{\bf (a)} text goes here {\bf (b)} text goes
+      here}\label{Fig:waterfalls}
+\end{figure}
+
 \section{Preliminary observations}
 
-\attention{NEED UPDATED AND NEW PLOTS, NEED VOLUNTEERS FOR THIS:
-  \begin{itemize}
+\attention{\begin{itemize}
     \item{Improved waterfall plots from 2-element pathfinder}
@@
 
-\autoref{Fig:auto} and \autoref{Fig:fringes} shows the initial results from the two interferometric array.
-These results are an encouraging factor to proceed with the development of the autonomous stations.\autoref{Fig:auto} shows the raw ALBATROS-EGG autospectra which where the waterfall plot was taken from one polarization (pol0) over an interval of 3 days.
-The Galaxy rising/setting is clearly visible in the structure.
-There are also ripples in frequency because of uncalibrated data, and the ripples arise from reflections in the cables.
-There is a qualitative difference between daytime and nighttime data and this shows that the contamination from shortwave radio drops off significantly at night, when the ionosphere becomes quieter.
+\autoref{Fig:waterfall_auto} and \autoref{Fig:waterfall_phase} shows
+the initial results from the two interferometric array.
+\autoref{Fig:waterfall_auto} shows the raw ALBATROS-EGG autospectra
+which where the waterfall plot was taken from one polarization (pol0)
+over an interval of 3 days. The Galaxy rising/setting is clearly
+visible in the structure. There are also ripples in frequency because
+of uncalibrated data, and the ripples arise from reflections in the
+cables. There is a qualitative difference between daytime and
+nighttime data and this shows that the contamination from shortwave
+radio drops off significantly at night, when the ionosphere becomes
+quieter.
 
-\begin{figure}[h!]
-	\begin{center}
-		\includegraphics[width=0.8\linewidth]{Figures/Raw-ALBATROS-autospectra.PNG}
-		\caption{Raw ALBATROS-EGG Autospectra}
-		\label{Fig:auto}
-	\end{center}
-\end{figure}
+\autoref{Fig:waterfall_phase} shows the first fringes that were
+detected by the the ALBATROS-EGG. The fringes show recurrent structure
+down to a frequency of as low as 10 MHz without data processing or
+data cuts.
 
-\autoref{Fig:fringes} shows the first fringes that were detected by the the ALBATROS-EGG.
-It is dinstictly visible from \autoref{Fig:fringes} that fringes show recurrent structure down to a frequency of as low as 10 MHz without data processing or data cuts.
+\section{Conclusions}
 
-\begin{figure}[ht!]
-	\begin{center}
-		\includegraphics[width=0.7\linewidth]{Figures/First-fringes-of-ALBATROS-EGG.PNG}
-		\caption{First Fringes from ALBATROS-EGG}
-		\label{Fig:fringes}
-	\end{center}
-\end{figure}
-
-% \section{Future Work}
+\attention{text goes here}
 
@@
 
-%\begin{thebibliography}{9}
-%
-%\bibitem[Alexander et al.(1975)]{1975A&A....40..365A} Alexander, J.~K., Kaiser, M.~L., Novaco, J.~C., et al.\ 1975, {\it aap\/}, {\bf 40}, 365
-%
-%\bibitem[Chen {et al.}(2019)]{2019arXiv190710853C} Chen, X., Burns, J., Koopmans, L., {\it et al.} [2019], arXiv e-prints, arXiv:1907.10853
-
-%\bibitem[Eastwood et al.(2018)]{2018AJ....156...32E} Eastwood, M.~W., Anderson, M.~M., Monroe, R.~M., et al.\ 2018, {\it aj\/}, {\bf 156}, 32
-
-%\bibitem[Ellingson and Kramer (2004)]{Memo28} Ellingson, S.~W., {Kramer}, W.~T. \ 2004, {\it Long Wavelength Array Memo (28)}
-
-%\bibitem[George {et al.}(2018)] {article} George, M., Orchiston, W., Wielebinsk, R., {\it et al.} [2018], Journal of Astronomical History and Heritage, {\bf 21}, 37
-
-%\bibitem[Hicks et al.(2012)]{2012PASP..124.1090H} Hicks, B.~C., Paravastu-Dalal, N., Stewart, K.~P., et al.\ 2012, {\it pasp\/}, {\bf 124}, 1090
-
-%\bibitem[Koopmans {et al.}(2019)]{2019arXiv190804296K} Koopmans, L., Barkana, R., Bentum, M., {\it et al.} [2019], arXiv e-prints, arXiv:1908.04296
-
-%\bibitem[Liu {et al.}(2013)]{2013PhRvD..87d3002L} Liu, A., Pritchard, J.~R., Tegmark, M., {\it et al.} [2013], {\bf 87}, 043002
-
-%\bibitem[Philip {et al.}(2019)]{2019JAI.....850004P} Philip, L., Abdurashidova, Z., Chiang, H.~C., {\it et al.} [2019], Journal of Astronomical Instrumentation, {\bf 8}, 19500
-
-%\bibitem[Pober {et al.}(2014)]{2014ApJ...782...66P} Pober, J.~C., Liu, A., Dillon, J.~S., {\it et al.} [2014], {\bf 782}, 66
-
-%\bibitem[Ray et al.(2006)]{Memo35} Ray, P.~S., Ellingson, S.~W., Fisher R., {\it et al.} [2006] {\it Long Wavelength Array Memo (35)}
-
-%\bibitem[Roger et al.(1999)]{1999A&AS..137....7R} Roger, R.~S., Costain, C.~H., Landecker, T.~L., et al.\ 1999, {\it aaps\/}, {\bf 137}, 7
-
-%\bibitem[Weiler {et al.}(1988)]{1988A&A...195..372W} Weiler, K.~W., Johnston, K.~J., Simon, R.~S., {\it et al.} [1988], {\it aap\/}, {\bf 195}, 372
-
-%\end{thebibliography}
 \end{document}

### 2020-06-12 albatros_paper.tex
some edits

--- 2020-06-10 albatros_paper.tex
@@
 synchrotron emission from the Galaxy follows a power law with a
-frequency dependence of $\nu^{-0.7}$.  At lower frequencies,
+frequency dependence of $\sim \nu^{-0.7}$.  At lower frequencies,
 synchrotron self-absorption becomes non-negligible, and the spectrum
@@
       denote other available infrastructure points that will not be
-      used for antennas.  {\bf (b)} Synthesized beam at 5~MHz from the
+      used for antennas.  {\bf (b)} Synthesized beam at 5~MHz at zenith from the
       full \albatros\ array, using the existing and planned
       installation locations shown on the map.  Using an octave of
-      bandwidth spanning 3.5--7~MHz, we obtain a synthesized beam with
+      bandwidth spanning 3.5--7~MHz in a single snapshot, we obtain a synthesized beam with 
       a full width of $\sim7'$.}\label{Fig:marion_map_beam}
@@
 ionospheric conditions.  As a benchmark, an interferometer operating
-at 30~MHz requires order-of-magnitude baseline lengths of $\sim 1$~km
+at 30~MHz requires baseline lengths of $\sim 0.5-1$~km 
 to achieve a resolution of $\sim 1$\degree.  This length scales
 inversely with frequency, and therefore $\sim 10$-km lengths are
-required at few-MHz frequencies to improve upon the resolutions
+required at few-MHz frequencies to improve substantially upon the resolutions
 achieved to date.  The experiment installation site must be remote to
-keep RFI to a minimum, and polar or near-polar latitiudes generally
+keep RFI to a minimum.  , and polar or near-polar latitiudes generally
 have lower ionospheric plasma frequency cutoffs relative to other

### 2020-06-12 albatros_paper.tex
HCC small fixes

@@
 ionospheric conditions.  As a benchmark, an interferometer operating
-at 30~MHz requires baseline lengths of $\sim 0.5-1$~km 
+at 30~MHz requires baseline lengths of $\sim0.5$--1~km 
 to achieve a resolution of $\sim 1$\degree.  This length scales
@@
 achieved to date.  The experiment installation site must be remote to
-keep RFI to a minimum.  , and polar or near-polar latitiudes generally
+keep RFI to a minimum, and polar or near-polar latitiudes generally
 have lower ionospheric plasma frequency cutoffs relative to other

### 2020-06-12 albatros_paper.tex
HCC cleaning up correlator section

@@
 \section{ALBATROS overview}
-
-% Write text here about the overall final configuration.  Describe the
-% site, show synthesized beam, discuss high level system requirements
-% (power, data storage, etc).  Include deployment schedule and introduce
-% 2-element pathfinder in the following section.
 
@@
 
-While the basics of 1-bit correlation are well known in the limit where the signal level is much lower than the noise, ALBATROS may well be in the high-signal regime.
-We present the basics of 1-bit correlation here, and show that even in the high-signal limit, 1-bit correlation remains viable.
-The fundamental output of a 1-bit correlator for real data is $x_{ij} \equiv \left < \tilde{E}_i \tilde{E}_j \right >$.
-$ \tilde{E}_i$ is the quantized version of the underlying electric field $E_i$ where $ \tilde{E}_i=1$ for $E_i>0$ and $ \tilde{E}_i=-1$ for $E_i<0$.
-Note that complex data can be handled as the combination of real components.
-This output is non-linear in the underlying true signal and noise levels, since the output saturates at unity for perfectly correlated electric fields.
-To get at the true sky signals, we will need to undo this nonlinearity (the so-called Van Vleck corrections).
-For a 2-level correlator, the expected output can be related to the true signals as follows (Van Vleck \& Middleton, e.g.
-D'Addario):
+The autonomous station can be configured to record 1-, 2-, or 4-bit
+baseband.  Signal fidelity improves with higher numbers of bits, but
+the penalty is increased data volume.  Here we discuss the prospects
+of employing 1-bit correlation for the final \albatros\ array to keep
+the baseband data volume to a minimum.  While the basics of 1-bit
+correlation are well known in the limit where the signal level is much
+lower than the noise, \albatros\ may well be in the high-signal
+regime.  The fundamental output of a 1-bit correlator for real data is
+\begin{equation}
+  x_{ij} \equiv \left < \tilde{E}_i \tilde{E}_j \right >.
+\end{equation}
+Here $\tilde{E}_i$ is the quantized version of the underlying electric
+field $E_i$:
+\begin{equation}
+  \tilde{E}_i=
+  \begin{cases}
+    1 & \text{if}\ E_i > 0 \\
+    -1 & \text{if}\ E_i < 0.
+  \end{cases}
+\end{equation}
+Complex data can be handled as the combination of real components.
+This output is non-linear in the underlying true signal and noise
+levels, since the output saturates at unity for perfectly correlated
+electric fields.  To get at the true sky signals, we will need to undo
+this nonlinearity (the so-called Van Vleck corrections).  For a
+2-level correlator, the expected output can be related to the true
+signals as follows (Van Vleck \& Middleton, e.g. D'Addario):
 \begin{eqnarray}
@@
   \begin{center}
-    \includegraphics[width=0.7\linewidth]{Figures/corr_efficiency.png}
+    \includegraphics[width=0.7\linewidth]{Figures/corr_efficiency/corr_efficiency.png}
     \caption{Correlator efficiency $\epsilon_{corr}$ for a 1-bit correlator as a function of signal-to-noise ratio (SNR).
@@
 
+% We present the basics of 1-bit correlation here, and show that even in
+% the high-signal limit, 1-bit correlation remains viable.
+
 \section*{Acknowledgments}

### 2020-06-12 Figures/corr_efficiency/plot_efficiency_1bit.py

@@ -1,0 +1,43 @@
+import numpy as np
+from matplotlib import pyplot as plt
+
+N=1
+#S=np.linspace(0.1,1000,10000)
+
+smin=0.01
+smax=10
+S=np.exp(np.linspace(np.log(smin),np.log(smax),1000))
+
+x=2.0/np.pi*np.arcsin(S/(S+N))
+
+sigma_x=np.sqrt(1-x**2)
+sigma_rho=np.pi/2*np.cos(np.pi/2*x)*sigma_x
+sigma_s=(S+N)**2/N*sigma_rho
+
+ref=S/(S+N)
+corr_eff=(S+N)/sigma_s
+
+plt.clf()
+plt.plot(S,corr_eff, 'k-')
+plt.xlabel('SNR')
+plt.ylabel('$\epsilon_{corr}$')
+#plt.loglog(S,corr_eff)
+
+
+imin=(2*len(S))//3
+pp=np.polyfit(np.log(S[imin:]),np.log(corr_eff[imin:]),1)
+print(pp)
+
+#pred=1.0/(S)**(1/4)
+
+#pred=(S**pp[0])*np.exp(pp[1])
+#pred=pred/pred[-1]*corr_eff[-1]
+pred=(S**-0.25)/3
+
+#plt.plot(S,pred)
+#plt.plot(S,sigma_s/S)
+plt.savefig('corr_efficiency.png')
+
+
+
+

### 2020-06-12 albatros_paper.tex
added words on orbcomm synchronization

--- 2020-06-12 albatros_paper.tex
@@
 increased from 81~MHz to 140~MHz to capture downlink signals at
-137--138~MHz from the ORBCOMM satellite constellation.
-\attention{words here about how we'll use orbcomm for backup timing
-  information}
+137--138~MHz from the ORBCOMM satellite constellation.  Preliminary
+lab tests suggest that on time scales of 30 seconds, relative timing
+between systems can be measured to an accuracy of better than a few
+tenths of a nanosecond using a single satellite.  This corresponds to
+a phase error at 10 MHz of ~1 degree or less.  With publicly available
+orbits and multiple satellites typically within the field of view, we
+expect to be able to use ORBCOMM baseband data saved at the same time as the
+astronomical data to carry out offline synchronization of the
+different ALBATROS stations.
 

### 2020-06-12 albatros_paper.tex
HCC continuing to work on correlation

--- 2020-06-12 albatros_paper.tex
@@
 
-The full ALBATROS configuration will comprise an array of 10
+The full \albatros\ configuration will comprise an array of 10
 autonomous antenna stations, each recording baseband over a tunable
@@
 baseband data will be collected periodically and subsequently
-correlated offline.  The ALBATROS stations, located at the eight
+correlated offline.  The \albatros\ stations, located at the eight
 coastal hut sites plus the hydro shack and \prizm\ site, will be
 separated by baselines of $\sim20$~km as shown in
-\autoref{Fig:marion_map_beam}. One fully autonomous ALBATROS station,
+\autoref{Fig:marion_map_beam}. One fully autonomous \albatros\ station,
 shown in \autoref{Fig:autonomous}, was deployed in April 2019 at the
@@
 
-\subsection{Back-end electronics}
+\subsection{Back-end electronics}\label{s:autonomous_backend}
 
@@
 increased from 81~MHz to 140~MHz to capture downlink signals at
-137--138~MHz from the ORBCOMM satellite constellation.
-\attention{words here about how we'll use orbcomm for backup timing
-  information}
+137--138~MHz from the ORBCOMM satellite constellation.  For the final
+\albatros\ array, the ORBCOMM signals provide a convenient means for
+synchronization across the antenna stations, serving as a backup to
+the GPS timing discussed below.  Preliminary lab tests suggest that on
+time scales of $\sim30$~s, relative timing between different antenna
+stations can be measured to an accuracy of better than a few tenths of
+a nanosecond using a single satellite.  The corresponding phase error
+at 10~MHz is $\lesssim1^\circ$.  With publicly available orbits and
+multiple satellites typically within the field of view, we expect that
+ORBCOMM baseband data saved at the same time as the astronomical data
+can provide offline synchronization of the \albatros\ stations.
 
@@
 Here $\tilde{E}_i$ is the quantized version of the underlying electric
-field $E_i$:
+field $E_i$ for antenna index $i$:
 \begin{equation}
@@
 Complex data can be handled as the combination of real components.
-This output is non-linear in the underlying true signal and noise
-levels, since the output saturates at unity for perfectly correlated
-electric fields.  To get at the true sky signals, we will need to undo
-this nonlinearity (the so-called Van Vleck corrections).  For a
-2-level correlator, the expected output can be related to the true
-signals as follows (Van Vleck \& Middleton, e.g. D'Addario):
+The output is nonlinear in the underlying true signal and noise
+levels; in the limit of perfectly correlated electric fields, $x_{ij}$
+saturates at unity.  Recovering the true sky signals requires
+inverting this nonlinear relation using the Van Vleck corrections.
+For a 2-level correlator, the relationship between $x_{ij}$ and the
+sky signals is~\citep{1989ASPC....6...59D, 1446497}
 \begin{eqnarray}
 \label{eqn:1bit_output}
-\left < \sin(\frac{\pi}{2}x_{ij})\right > = \frac{V_{ij}}{\sqrt{V_{ij}+N_i}\sqrt{V_{ij}+N_j}}
+\left < \sin\left(\frac{\pi}{2}x_{ij}\right)\right > = \frac{V_{ij}}{\sqrt{V_{ij}+N_i}\sqrt{V_{ij}+N_j}},
 \end{eqnarray}
-where $V_{ij}$ is the true visibility, and $V_{ij}+N_{i,j}$ is the total noise power measured by antennas $i$ and $j$.
-Inverting this relation to get the true signal requires knowing the noise powers, which is not possible from the 1-bit data themselves.
-However, the SNAP board calculates these power levels on timescales of a few seconds, much faster than the power levels change, and so by combining the single-station power measurements with the cross-station cross correlation, we will be able to derive the true sky visibilities.
+where $V_{ij}$ is the true sky visibility, and $V_{ij}+N_{i}$ and
+$V_{ij}+N_{j}$ are the total, signal-plus-noise, power levels measured
+by antennas $i$ and $j$, respectively.  Inverting this relation to
+obtain $V_{ij}$ requires knowing the total power levels, which cannot
+be determined from 1-bit data alone.  However, as described in
+\S\ref{s:autonomous_backend}, the SNAP board calculates and records
+auto-spectrum data products, which provide power level information on
+few-second time scales.  Changes in the power levels occur on
+significantly longer time scales, so the true sky visibilities can be
+derived by combining cross-correlation data between different antenna
+stations and the auto-spectrum data from each individual station.
 
@@
 charging system to power the station, and we are investigating small
-wind turbines for future ALBATROS stations.
+wind turbines for future \albatros\ stations.
 
@@
 
+% discuss design changes for final stations: larger banks of hard
+% drives, possible wind power, etc.
+
 \section*{Acknowledgments}

### 2020-06-15 albatros_paper.tex
HCC tweaked correlator plot and text

@@
 correlation are well known in the limit where the signal level is much
-lower than the noise, \albatros\ may well be in the high-signal
-regime.  The fundamental output of a 1-bit correlator for real data is
+lower than the noise, \albatros\ may be in a regime where the signal
+level is non-negligible.  The fundamental output of a 1-bit correlator
+for real data is
 \begin{equation}
@@
 saturates at unity.  Recovering the true sky signals requires
-inverting this nonlinear relation using the Van Vleck corrections.
-For a 2-level correlator, the relationship between $x_{ij}$ and the
-sky signals is~\citep{1989ASPC....6...59D, 1446497}
+inverting this nonlinear relation using the Van Vleck
+corrections~\citep{1446497}.  For a 2-level correlator, the
+relationship between $x_{ij}$ and the sky signals
+is~\citep{1989ASPC....6...59D}
 \begin{eqnarray}
@@
     \includegraphics[width=0.7\linewidth]{Figures/corr_efficiency/corr_efficiency.png}
-    \caption{Correlator efficiency $\epsilon_{corr}$ for a 1-bit correlator as a function of signal-to-noise ratio (SNR).
-To get the expected SNR from a 1-bit correlator, multiply the SNR derived from the radiometer equation by $\epsilon_{corr}$.
-For low SNR, the efficiency is $2/\pi \sim 0.64$, and it drops monotonically as the SNR increases.
-The drop is relatively gentle, only changing by a factor of $\sim 2$ for SNR=2.
-For baseline separations of many wavelengths, the correlated component of the electric field is likely to be a small fraction of the total power, so ALBATROS is unlikely to lose more than a factor of $\sim 2$ by using 1-bit correlation.}
+    \caption{Correlator efficiency $\epsilon$ for a 1-bit correlator
+      as a function of signal-to-noise ratio (SNR).  The efficiency is
+      roughly 0.64 at low SNR and drops monotonically as the SNR
+      increases.  The decrease in $\epsilon$ is relatively gentle,
+      changing by only a factor of 2 for SNR $\sim2$.}
     \label{fig:1bit_efficiency}
@@
 
-One might worry that at high signal levels, the saturation of the 1-bit cross correlation would lead to the noise exploding.
-In practice the rolloff in sensitivity is relatively mild, especially in the case of long baselines.
-It can be expressed in terms of the correlator efficiency $\epsilon_{corr}$, which is defined to be the ratio of the measured signal-to-noise ratio to the ideal (infinite precision) SNR.
-As seen in Figure \ref{fig:1bit_efficiency}, $\epsilon_{corr}$ only drops by a factor of $\sim$2 as the signal power goes from 0 to a few times the noise power.
-We stress that the signal level in question is the part that correlates between the two antennas.
-In the case of long baselines (where long means the fringe spacing is small compared to the primary beam/antenna response pattern) that are not dominated by a single bright source, the signal power will always be smaller than the noise power, and so $\epsilon_{corr}$ is unlikely to drop below $\sim$0.5\footnote{A quick estimate can be made by analogy to the behavior of dishes in the UV plane in the flat sky approximation.
-While all power in the UV plane (plus any system noise) goes into an individual antenna's electric field, the correlated part only has contribution from the area in the UV plane within the width of the UV-space primary beam of the UV-space coordinate.
-If the sky can be described as a Gaussian random field, in the most pessimistic case this is roughly the aperture filling factor of the antenna pair.
-In our case, where the antennas are approximately dipolar, the filling factor will be the square of the wavelength over the baseline length.
-As long as the baselines are several wavelengths or longer, the correlated power will be small, and the correlator efficiency will be close to the ideal 1-bit value of $\frac{2}{\pi}$.}.
+% To get the expected SNR from a 1-bit correlator, multiply the SNR
+% derived from the radiometer equation by $\epsilon_{corr}$.
+
+To assess the loss of sensitivity as the signal level increases, we
+use \autoref{eqn:1bit_output} to derive the correlator efficiency
+$\epsilon$, which is the ratio of measured signal-to-noise ratio (SNR)
+to the ideal, infinite-precision SNR.  \autoref{fig:1bit_efficiency}
+illustrates that the decrease in $\epsilon$ as a function of SNR is
+relatively shallow.  When the SNR is near zero, $\epsilon \approx
+2/\pi = 0.64$, and if the signal level increases to two times the
+noise level, $\epsilon$ decreases by only a factor of $\sim2$.  The
+final \albatros\ array will have baselines that are long relative to
+the observing wavelength, and the correlated component of the electric
+field (which sets the relevant signal level) is likely a small
+fraction of the total received power.  This qualitative argument can
+by made by considering antennas in the $uv$ plane in the flat-sky
+approximation.  Any individual antenna receives all power present in
+the $uv$ plane (plus system noise), but the correlated contribution
+comes only from the portion of the $uv$ plane that is encompassed by
+the primary beam at the antenna's $uv$-space coordinate.  Assuming
+that the sky can be described as a Gaussian random field, the maximum
+correlated signal between two antennas is determined by the aperture
+filling factor of that pair.  For the case of dipole antennas, the
+filling factor is the square of the wavelength divided by the baseline
+length.  Therefore, in the long-baseline limit, the correlated signal
+is small in comparison to the total power received, and the correlator
+efficiency is unlikely to decrease significantly from the ideal
+$2/\pi$ value.
+
+% One might worry that at high signal levels, the saturation of the
+% 1-bit cross correlation would lead to the noise exploding.  In
+% practice the rolloff in sensitivity is relatively mild, especially in
+% the case of long baselines.  It can be expressed in terms of the
+% correlator efficiency $\epsilon_{corr}$, which is defined to be the
+% ratio of the measured signal-to-noise ratio to the ideal (infinite
+% precision) SNR.  As seen in Figure \ref{fig:1bit_efficiency},
+% $\epsilon_{corr}$ only drops by a factor of $\sim$2 as the signal
+% power goes from 0 to a few times the noise power.  We stress that the
+% signal level in question is the part that correlates between the two
+% antennas.  In the case of long baselines (where long means the fringe
+% spacing is small compared to the primary beam/antenna response
+% pattern) that are not dominated by a single bright source, the signal
+% power will always be smaller than the noise power, and so
+% $\epsilon_{corr}$ is unlikely to drop below $\sim$0.5\footnote{A quick
+%   estimate can be made by analogy to the behavior of dishes in the UV
+%   plane in the flat sky approximation.  While all power in the UV
+%   plane (plus any system noise) goes into an individual antenna's
+%   electric field, the correlated part only has contribution from the
+%   area in the UV plane within the width of the UV-space primary beam
+%   of the UV-space coordinate.  If the sky can be described as a
+%   Gaussian random field, in the most pessimistic case this is roughly
+%   the aperture filling factor of the antenna pair.  In our case, where
+%   the antennas are approximately dipolar, the filling factor will be
+%   the square of the wavelength over the baseline length.  As long as
+%   the baselines are several wavelengths or longer, the correlated
+%   power will be small, and the correlator efficiency will be close to
+%   the ideal 1-bit value of $\frac{2}{\pi}$.}.
 

### 2020-06-15 Figures/corr_efficiency/plot_efficiency_1bit.py

@@ -1,5 +1,12 @@
 import numpy as np
 from matplotlib import pyplot as plt
+import matplotlib
+
+font = {'family' : 'normal',
+        'weight' : 'normal',
+        'size'   : 14}
+
+matplotlib.rc('font', **font)
 
 N=1
 #S=np.linspace(0.1,1000,10000)
@@ -18,9 +25,15 @@ ref=S/(S+N)
 corr_eff=(S+N)/sigma_s
 
 plt.clf()
+plt.figure(figsize=(10,5))
 plt.plot(S,corr_eff, 'k-')
-plt.xlabel('SNR')
-plt.ylabel('$\epsilon_{corr}$')
+plt.hlines([0.64, 0.32], 0, 10, '#888888', linestyles='dashed')
+plt.text(8, 0.68, '$\epsilon = 0.64$', color='#888888')
+plt.text(8, 0.34, '$\epsilon = 0.32$', color='#888888')
+plt.xlim(0, 10)
+plt.ylim(0, 1)
+plt.xlabel('Signal-to-noise ratio')
+plt.ylabel('Correlator efficiency ($\epsilon$)')
 #plt.loglog(S,corr_eff)
 
 

### 2020-06-15 albatros_paper.tex
minor text corrections in correlator part

@@
 illustrates that the decrease in $\epsilon$ as a function of SNR is
-relatively shallow.  When the SNR is near zero, $\epsilon \approx
-2/\pi = 0.64$, and if the signal level increases to two times the
+relatively shallow.  When the SNR is near zero, $\epsilon$ approaches
+$2/\pi \approx 0.64$, and if the signal level increases to two times
+the  
 noise level, $\epsilon$ decreases by only a factor of $\sim2$.  The

### 2020-06-26 albatros_paper.tex
HCC fixed typo
HCC added disclaimer sentence about LWA antenna at low freqs

@@
     \caption{Two-element \albatros\ pathfinder block diagram.  Signals
-      from two dual-polarzation LWA antennas are amplified by
+      from two dual-polarization LWA antennas are amplified by
       front-end active baluns~\citep{2012PASP..124.1090H}.  The
@@
 cardinal directions.  Welded wire mesh screens, roughly 3~m on a side,
-are installed on the ground below the antennas.
+are installed on the ground below the antennas.  Although the LWA
+antenna is not optimized for observations below 10~MHz, using this
+standard antenna allowed an initial test of the site and of the
+interferometer systems.  For the final \albatros\ array, we are
+exploring alternative antenna designs that will that will cover the
+full frequency range.
+
 % do we want/need to say anything about the omnidirectional primary beam?

### 2020-07-04 albatros_paper.tex
HCC added new waterfall plots and text for 2-element results

@@
 
-\section{Two-element pathfinder}
+\section{Two-element pathfinder}\label{s:2elem}
 
@@
 fraction of the total received power.  This qualitative argument can
-by made by considering antennas in the $uv$ plane in the flat-sky
+by made by considering antennas in the $uv$~plane in the flat-sky
 approximation.  Any individual antenna receives all power present in
-the $uv$ plane (plus system noise), but the correlated contribution
-comes only from the portion of the $uv$ plane that is encompassed by
+the $uv$~plane (plus system noise), but the correlated contribution
+comes only from the portion of the $uv$~plane that is encompassed by
 the primary beam at the antenna's $uv$-space coordinate.  Assuming
@@
 %   the ideal 1-bit value of $\frac{2}{\pi}$.}.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.9\linewidth]{Figures/albatros2_waterfalls.jpg}
+    \caption{Spectra from a co-aligned polarization pair from the
+      two-element \albatros\ pathfinder, shown as a function of
+      frequency and time.  The auto- and cross-spectra are shown in
+      the top and bottom rows, respectively.  The spectrum magnitudes
+      are in uncalibrated ADC units on a logarithmic scale.
+      Repeatable structure from the Galaxy is visible over the
+      three-day time scale in all plots.}
+    \label{Fig:albatros2_waterfalls}
+  \end{center}
+\end{figure}
 
@@
 \begin{figure}
-    \centering
-    \begin{subfigure}[t]{0.48\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{Figures/Raw-ALBATROS-autospectra.PNG}
-        \caption{} \label{Fig:waterfall_auto}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[t]{0.48\textwidth}
-      \centering
-        \includegraphics[width=\linewidth]{Figures/First-fringes-of-ALBATROS-EGG.PNG}
-        \caption{} \label{Fig:waterfall_phase}
-    \end{subfigure}
-    \caption{{\bf (a)} text goes here {\bf (b)} text goes
-      here}\label{Fig:waterfalls}
+  \begin{center}
+    \includegraphics[width=0.6\linewidth]{Figures/albatros2_lst_phase.jpg}
+    \caption{Phases from the cross-correlation between two co-aligned
+      polarizations in the two-element \albatros\ pathfinder.  About
+      372 hours of data are shown here, binned in local sidereal
+      time.}
+    \label{Fig:albatros2_phase}
+  \end{center}
 \end{figure}
@@
 
-\attention{\begin{itemize}
-    \item{Improved waterfall plots from 2-element pathfinder}
-    \item{Plot showing that the solar power works (sort of)}
-    \item{Some sort of...data...plot for the autonomous station.  Can
-      we say anything about baseband performance?}
-  \end{itemize}
-}
+The primary goal of the two-element pathfinder described in
+\S\ref{s:2elem} was to qualitatively assess the level of RFI and
+ionospheric contamination at low frequenices.
+\autoref{Fig:albatros2_waterfalls} illustrates auto- and cross-spectra
+from one of the co-aligned polarization pairs from the two antennas.
+The data are shown over a three-day period (June 18--21, 2018), and no
+calibration or cuts have been applied.  The rising and setting of the
+Galaxy is visible in all of the spectrum magnitudes, and repeatable
+fringes are visible in the phases of the cross-spectra.  The RFI lines
+at $\lesssim20$~MHz arise primarily from shortwave radio transmission
+reflecting off the ionosphere.  During the night, when the ionospheric
+plasma cutoff frequency drops, the maximum frequency of the RFI
+contamination falls to $\sim10$~MHz.
 
-\autoref{Fig:waterfall_auto} and \autoref{Fig:waterfall_phase} shows
-the initial results from the two interferometric array.
-\autoref{Fig:waterfall_auto} shows the raw ALBATROS-EGG autospectra
-which where the waterfall plot was taken from one polarization (pol0)
-over an interval of 3 days. The Galaxy rising/setting is clearly
-visible in the structure. There are also ripples in frequency because
-of uncalibrated data, and the ripples arise from reflections in the
-cables. There is a qualitative difference between daytime and
-nighttime data and this shows that the contamination from shortwave
-radio drops off significantly at night, when the ionosphere becomes
-quieter.
+As a qualitative illustration of the sky signal repeatability,
+\autoref{Fig:albatros2_phase} shows the phases of the cross-spectra
+binned in local sidereal time.  About 372 hours of data are averaged
+into this plot, and no RFI excision has been performed.  A more
+detailed analysis of signal repeatability will be presented in a
+future paper, but the high signal-to-noise fringe pattern, which is
+even visible a little below $\sim10$~MHz, demonstrates the proof of
+concept for building the expanded \albatros\ array.
 
-\autoref{Fig:waterfall_phase} shows the first fringes that were
-detected by the the ALBATROS-EGG. The fringes show recurrent structure
-down to a frequency of as low as 10 MHz without data processing or
-data cuts.
+\attention{Do we want a plot showing solar power data of any sort?}
+
+% \autoref{Fig:waterfall_auto} and \autoref{Fig:waterfall_phase} shows
+% the initial results from the two interferometric array.
+% \autoref{Fig:waterfall_auto} shows the raw ALBATROS-EGG autospectra
+% which where the waterfall plot was taken from one polarization (pol0)
+% over an interval of 3 days. The Galaxy rising/setting is clearly
+% visible in the structure. There are also ripples in frequency because
+% of uncalibrated data, and the ripples arise from reflections in the
+% cables. There is a qualitative difference between daytime and
+% nighttime data and this shows that the contamination from shortwave
+% radio drops off significantly at night, when the ionosphere becomes
+% quieter.
+% 
+% \autoref{Fig:waterfall_phase} shows the first fringes that were
+% detected by the the ALBATROS-EGG. The fringes show recurrent structure
+% down to a frequency of as low as 10 MHz without data processing or
+% data cuts.
 

### 2020-07-04 albatros_paper.tex
HCC fixed small typo
HCC more small fixes

@@
 interferometer systems.  For the final \albatros\ array, we are
-exploring alternative antenna designs that will that will cover the
-full frequency range.
+exploring alternative antenna designs that will cover the full
+frequency range.
 
@@
 The full \albatros\ configuration will comprise an array of 10
-autonomous antenna stations, each recording baseband over a tunable
-10--20~MHz window within the full 0--125~MHz operating range.  The
-baseband data will be collected periodically and subsequently
-correlated offline.  The \albatros\ stations, located at the eight
-coastal hut sites plus the hydro shack and \prizm\ site, will be
-separated by baselines of $\sim20$~km as shown in
-\autoref{Fig:marion_map_beam}. One fully autonomous \albatros\ station,
-shown in \autoref{Fig:autonomous}, was deployed in April 2019 at the
-hydro shack location (\ang{46;52.205;}S, \ang{37;50.612;}E) on Marion
-Island as a first step in testing the technology needed to establish
-the full array.  The system block diagram is shown in
-\autoref{Fig:albatros1_schem}.  The antenna and front-end active balun
-in the single autonomous station are identical to those used in the
-two-element pathfinder (\S\ref{s:antenna} and \S\ref{s:fee}), and the
-back-end electronics and power system are described in detail below.
+autonomous antenna stations, each recording baseband over tunable
+frequency windows (with 10--20~MHz total bandwidth) within the full
+0--125~MHz operating range.  The baseband data will be collected
+periodically and subsequently correlated offline.  The
+\albatros\ stations, located at the eight coastal hut sites plus the
+hydro shack and \prizm\ site, will be separated by baselines of
+$\sim20$~km as shown in \autoref{Fig:marion_map_beam}. One fully
+autonomous \albatros\ station, shown in \autoref{Fig:autonomous}, was
+deployed in April 2019 at the hydro shack location (\ang{46;52.205;}S,
+\ang{37;50.612;}E) on Marion Island as a first step in testing the
+technology needed to establish the full array.  The system block
+diagram is shown in \autoref{Fig:albatros1_schem}.  The antenna and
+front-end active balun in the single autonomous station are identical
+to those used in the two-element pathfinder (\S\ref{s:antenna} and
+\S\ref{s:fee}), and the back-end electronics and power system are
+described in detail below.
 

### 2020-07-04 albatros_paper.tex
HCC added more text in section 5

@@
       the top and bottom rows, respectively.  The spectrum magnitudes
-      are in uncalibrated ADC units on a logarithmic scale.
-      Repeatable structure from the Galaxy is visible over the
-      three-day time scale in all plots.}
+      are in uncalibrated ADC units on a logarithmic scale, and the
+      cross-spectrum is about two orders of magnitude fainter than the
+      autospectra.  Repeatable structure from the Galaxy is visible
+      over the three-day time scale in all plots.}
     \label{Fig:albatros2_waterfalls}
@@
 Galaxy is visible in all of the spectrum magnitudes, and repeatable
-fringes are visible in the phases of the cross-spectra.  The RFI lines
-at $\lesssim20$~MHz arise primarily from shortwave radio transmission
+fringes are visible in the phases of the cross-spectra.  The signal
+drop-off below $\lesssim30$~MHz in the autospectra is caused largely
+by the combined response of the LWA antenna and FEE.  Although the LWA
+antenna is not optimized for the lowest \albatros\ observing
+frequencies, as described in \S\ref{s:antenna}, it is sufficient for
+these initial, exploratory measurements.  The RFI lines at
+$\lesssim20$~MHz arise primarily from shortwave radio transmission
 reflecting off the ionosphere.  During the night, when the ionospheric
@@
 future paper, but the high signal-to-noise fringe pattern, which is
-even visible a little below $\sim10$~MHz, demonstrates the proof of
+even visible slightly below $\sim10$~MHz, demonstrates the proof of
 concept for building the expanded \albatros\ array.
@@
 \attention{Do we want a plot showing solar power data of any sort?}
-
-% \autoref{Fig:waterfall_auto} and \autoref{Fig:waterfall_phase} shows
-% the initial results from the two interferometric array.
-% \autoref{Fig:waterfall_auto} shows the raw ALBATROS-EGG autospectra
-% which where the waterfall plot was taken from one polarization (pol0)
-% over an interval of 3 days. The Galaxy rising/setting is clearly
-% visible in the structure. There are also ripples in frequency because
-% of uncalibrated data, and the ripples arise from reflections in the
-% cables. There is a qualitative difference between daytime and
-% nighttime data and this shows that the contamination from shortwave
-% radio drops off significantly at night, when the ionosphere becomes
-% quieter.
-% 
-% \autoref{Fig:waterfall_phase} shows the first fringes that were
-% detected by the the ALBATROS-EGG. The fringes show recurrent structure
-% down to a frequency of as low as 10 MHz without data processing or
-% data cuts.
 

### 2020-07-16 albatros_paper.tex
HCC added placeholder figures for baseband/direct comparisons, added more references in intro section

@@
 Very few experiments have surveyed the radio sky at $\lesssim 30$~MHz,
-and here, we highlight only four specific examples.  At the very
-lowest frequencies, the state of the art among ground-based
-measurements dates from the 1950s, when Reber and Ellis caught brief
-glimpses of the $2.1$~MHz sky at $\sim 5$\degree\ resolution, using an
-array of 192~dipoles~\citep{1956JGR....61....1R}.  A few space-based
-missions have also performed measurements at similarly low frequency
-ranges; for example, the Radio Astronomy Explorer-2 operated at
+and here, we highlight only a subset.  At the very lowest frequencies,
+the state of the art among ground-based measurements dates from the
+1950s, when Reber and Ellis caught brief glimpses of the $2.1$~MHz sky
+at $\sim 5$\degree\ resolution, using an array of
+192~dipoles~\citep{1956JGR....61....1R}.  A few space-based missions
+have also performed measurements at similarly low frequency ranges;
+for example, the Radio Astronomy Explorer-2 operated at
 \SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
-\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Measurements with
-resolution finer than few-degree scales exist mainly at higher
-frequencies.  For example, the Dominion Radio Astrophysical
-Observatory surveyed the northern sky at \SI{22}{\MHz} with
-\SIrange{1.1}{1.7}{\degree} resolution~\citep{1999A&AS..137....7R},
-and most recently, the Owens Valley Long Wavelength Array mapped the
-sky with \SI{15}{\arcminute} resolution between 36.528~MHz and
+\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  More recent ground-based
+experiments include the Dominion Radio Astrophysical Observatory
+surveys of the northern sky at 10~MHz and 22~MHz, with
+$\sim2$\degree\ and 1.1--1.7\degree\ resolution,
+respectively~\citep{1976MNRAS.177..601C, 1999A&AS..137....7R}.
+Low-frequency imaging experiments that are currently operational or
+under construction include the Ukranian T-shaped Radio
+telescope~\citep{2016JAI.....541010Z}, with 0.5\degree\ resolution at
+the center of its 8--32~MHz operating range, and the New extension in
+Nan\c{c}ay upgrading LOFAR~\citep{7136773}, which operates at
+10--85~MHz with 1.5\degree\ resolution in standalone mode, and
+improved resolution at $>30$~MHz when combined with LOFAR.  Existing
+measurements with finer resolution are mainly at higher frequencies;
+for example, the Owens Valley Long Wavelength Array mapped the sky
+with \SI{15}{\arcminute} resolution between 36.528~MHz and
 73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
@@
 information about the $\lesssim 30$~MHz sky and the lack of high
-resolution measurements at the lowest frequencies.  The first step
-toward laying the groundwork for possible measurements of the dark
-ages is obtaining an improved map of Galactic foregrounds at $\lesssim
-30$~MHz.  In addition to serving as a stepping stone for future
-cosmological constraints from the dark ages, maps at these frequencies
-can also shed new light on Galactic astrophysics.  Above $\sim30$~MHz,
-synchrotron emission from the Galaxy follows a power law with a
-frequency dependence of $\sim \nu^{-0.7}$.  At lower frequencies,
-synchrotron self-absorption becomes non-negligible, and the spectrum
-transitions to $\nu^{+5/2}$ dependence.  Since self-absorption causes
-the optical depth along the line of sight to depend on frequency,
-observations at $\lesssim 30$~MHz have the potential to probe the
-three-dimensional cosmic ray structure of the
-Galaxy~\citep{2002ApJ...575..217P}.  Low-frequency observations can
-also be used to image radio recombination lines (RRLs), which provide
-a means for studying cool, low-density regions of the interstellar
-medium (ISM).  These absorption lines arise from Rydberg atoms and are
-highly sensitive to the surrounding environment.  The RRL spectrum and
-absorption profiles can therefore constrain the detailed properties of
-the ISM regions in which the Rydberg atoms are
+resolution measurements at the lowest frequencies, particularly in the
+southern hemisphere.  The first step toward laying the groundwork for
+possible measurements of the dark ages is obtaining an improved map of
+Galactic foregrounds at $\lesssim 30$~MHz.  In addition to serving as
+a stepping stone for future cosmological constraints from the dark
+ages, maps at these frequencies can also shed new light on Galactic
+astrophysics.  Above $\sim30$~MHz, synchrotron emission from the
+Galaxy follows a power law with a frequency dependence of $\sim
+\nu^{-0.7}$.  At lower frequencies, synchrotron self-absorption
+becomes non-negligible, and the spectrum transitions to $\nu^{+5/2}$
+dependence.  Since self-absorption causes the optical depth along the
+line of sight to depend on frequency, observations at $\lesssim
+30$~MHz have the potential to probe the three-dimensional cosmic ray
+structure of the Galaxy~\citep{2002ApJ...575..217P}.  Low-frequency
+observations can also be used to image radio recombination lines
+(RRLs), which provide a means for studying cool, low-density regions
+of the interstellar medium (ISM).  These absorption lines arise from
+Rydberg atoms and are highly sensitive to the surrounding environment.
+The RRL spectrum and absorption profiles can therefore constrain the
+detailed properties of the ISM regions in which the Rydberg atoms are
 formed~\citep{2009NewAR..53..259G, 2007MNRAS.374..852S}.  Finally,
@@
 
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_auto_compare.jpg}
+    \caption{Placeholder figure for comparison of auto-spectra from
+      baseband (4-bit), and directly computed/averaged by the SNAP.}
+    \label{Fig:baseband_direct_auto}
+  \end{center}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_phase_compare.jpg}
+    \caption{Placeholder figure for comparison of cross-spectrum phase from
+      baseband (4-bit), and directly computed/averaged by the SNAP.}
+    \label{Fig:baseband_direct_phase}
+  \end{center}
+\end{figure}
+
 \attention{Do we want a plot showing solar power data of any sort?}

### 2020-07-20 albatros_paper.tex
HCC added more observations text

@@
 
-\begin{figure}
+\begin{figure}[t]
   \begin{center}
@@
     \label{Fig:albatros2_waterfalls}
+  \end{center}
+\end{figure}
+
+\begin{figure}[t]
+  \begin{center}
+    \includegraphics[width=0.6\linewidth]{Figures/albatros2_lst_phase.jpg}
+    \caption{Phases from the cross-correlation between two co-aligned
+      polarizations in the two-element \albatros\ pathfinder.  About
+      372 hours of data are shown here, binned in local sidereal
+      time.}
+    \label{Fig:albatros2_phase}
   \end{center}
@@
 
-\begin{figure}
+\begin{figure}[t]
   \begin{center}
-    \includegraphics[width=0.6\linewidth]{Figures/albatros2_lst_phase.jpg}
-    \caption{Phases from the cross-correlation between two co-aligned
-      polarizations in the two-element \albatros\ pathfinder.  About
-      372 hours of data are shown here, binned in local sidereal
-      time.}
-    \label{Fig:albatros2_phase}
+    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_auto_compare.jpg}
+    \caption{Placeholder figure for comparison of auto-spectra from
+      baseband (4-bit), and directly computed/averaged by the SNAP.}
+    \label{Fig:baseband_direct_auto}
+  \end{center}
+\end{figure}
+
+\begin{figure}[t]
+  \begin{center}
+    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_phase_compare.jpg}
+    \caption{Placeholder figure for comparison of cross-spectrum phase from
+      baseband (4-bit), and directly computed/averaged by the SNAP.}
+    \label{Fig:baseband_direct_phase}
   \end{center}
@@
 
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_auto_compare.jpg}
-    \caption{Placeholder figure for comparison of auto-spectra from
-      baseband (4-bit), and directly computed/averaged by the SNAP.}
-    \label{Fig:baseband_direct_auto}
-  \end{center}
-\end{figure}
+% note to self: look up time of day that corresponds to LST period
+% where fringes appear to extend below 10 MHz, see if that's night
+% time
 
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_phase_compare.jpg}
-    \caption{Placeholder figure for comparison of cross-spectrum phase from
-      baseband (4-bit), and directly computed/averaged by the SNAP.}
-    \label{Fig:baseband_direct_phase}
-  \end{center}
-\end{figure}
+We have been unable to retrieve data from the single autonomous
+station pathfinder on Marion because of COVID-19 and limited bandwidth
+to the island, although we have confirmed that the solar power system
+has successfully met the power demands of the antenna station.  To
+demonstrate baseband writing capability in the absence of Marion data,
+we instead present a short observation that was taken by a separate
+\albatros\ pathfinder station that operated from the McGill Arctic
+Research Station (MARS; \ang{79;26;}N, \ang{90;46;}W) during
+July~2019.  The RF signal chain of the MARS installation had the same
+architecture as that shown in \autoref{Fig:albatros1_schem}, but the
+power was supplied by manually charged batteries, rather than a solar
+power system.  The MARS RFI environment is somewhat noisier than that
+of Marion Island, and because the data were taken during the height of
+Arctic summer, the ionospheric plasma cutoff frequency is higher than
+the typical cutoff reflected in the Marion data.
 
-\attention{Do we want a plot showing solar power data of any sort?}
+\autoref{Fig:baseband_direct_auto} shows autospectra for one
+polarization of the \albatros\ pathfinder installed at MARS, comparing
+the accumulated spectra that are directly computed by the SNAP board
+against spectra that are calculated from baseband data with 4-bit
+quantization.  (Autospectrum information is not preserved with 1-bit
+quantization.)  Baseband data were recorded over two frequency
+windows, 5.3--12.6~MHz and 12.6--20.0~MHz, at separate times, and the
+corresponding accumulated spectra from the SNAP board are shown for
+the same frequency and time ranges.  The waterfall plots have the same
+61-kHz frequency resolution, set by the resolution of the spectra
+computed by the SNAP board.  The overplotted mean spectra are shown
+with finer resolution (\attention{numbers go here}) from the baseband
+data to illustrate the additional information that is not retained in
+the accumulated spectra.  For these mean spectrum plots, the baseband
+data are processed by
+inverting\footnote{\url{https://github.com/jrs65/pfb-inverse}} the
+polyphase filter bank to recover time-domain data, and the forward
+polyphase filter bank is then applied to concatenated timestreams of
+an appropriate total length to set the desired frequency resolution.
+The spectra computed from baseband qualitatively agree with those
+directly accumulated by the SNAP board, up to small differences caused
+by the 4-bit quantization.
+
+\attention{more words to come here about phase plots}
 

### 2020-07-20 albatros_paper.tex
HCC added more text in observations and conclusions

@@
 
-\begin{figure}[t]
-  \begin{center}
-    \includegraphics[width=0.9\linewidth]{Figures/albatros2_waterfalls.jpg}
-    \caption{Spectra from a co-aligned polarization pair from the
-      two-element \albatros\ pathfinder, shown as a function of
-      frequency and time.  The auto- and cross-spectra are shown in
-      the top and bottom rows, respectively.  The spectrum magnitudes
-      are in uncalibrated ADC units on a logarithmic scale, and the
-      cross-spectrum is about two orders of magnitude fainter than the
-      autospectra.  Repeatable structure from the Galaxy is visible
-      over the three-day time scale in all plots.}
-    \label{Fig:albatros2_waterfalls}
-  \end{center}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{center}
-    \includegraphics[width=0.6\linewidth]{Figures/albatros2_lst_phase.jpg}
-    \caption{Phases from the cross-correlation between two co-aligned
-      polarizations in the two-element \albatros\ pathfinder.  About
-      372 hours of data are shown here, binned in local sidereal
-      time.}
-    \label{Fig:albatros2_phase}
-  \end{center}
-\end{figure}
-
 \subsection{Solar power system}
@@
   \begin{center}
-    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_auto_compare.jpg}
-    \caption{Placeholder figure for comparison of auto-spectra from
-      baseband (4-bit), and directly computed/averaged by the SNAP.}
-    \label{Fig:baseband_direct_auto}
+    \includegraphics[width=0.9\linewidth]{Figures/albatros2_waterfalls.jpg}
+    \caption{Spectra from a co-aligned polarization pair from the
+      two-element \albatros\ pathfinder, shown as a function of
+      frequency and time.  The auto- and cross-spectra are shown in
+      the top and bottom rows, respectively.  The spectrum magnitudes
+      are in uncalibrated ADC units on a logarithmic scale, and the
+      cross-spectrum is about two orders of magnitude fainter than the
+      autospectra.  Repeatable structure from the Galaxy is visible
+      over the three-day time scale in all plots.}
+    \label{Fig:albatros2_waterfalls}
   \end{center}
@@
   \begin{center}
-    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_phase_compare.jpg}
-    \caption{Placeholder figure for comparison of cross-spectrum phase from
-      baseband (4-bit), and directly computed/averaged by the SNAP.}
-    \label{Fig:baseband_direct_phase}
+    \includegraphics[width=0.6\linewidth]{Figures/albatros2_lst_phase.jpg}
+    \caption{Phases from the cross-correlation between two co-aligned
+      polarizations in the two-element \albatros\ pathfinder.  About
+      372 hours of data are shown here, binned in local sidereal
+      time.}
+    \label{Fig:albatros2_phase}
   \end{center}
@@
 
-\section{Preliminary observations}
+\section{Preliminary observations}\label{s:obs}
 
@@
 \S\ref{s:2elem} was to qualitatively assess the level of RFI and
-ionospheric contamination at low frequenices.
+ionospheric contamination at low frequencies.
 \autoref{Fig:albatros2_waterfalls} illustrates auto- and cross-spectra
@@
 \albatros\ pathfinder station that operated from the McGill Arctic
-Research Station (MARS; \ang{79;26;}N, \ang{90;46;}W) during
-July~2019.  The RF signal chain of the MARS installation had the same
-architecture as that shown in \autoref{Fig:albatros1_schem}, but the
-power was supplied by manually charged batteries, rather than a solar
-power system.  The MARS RFI environment is somewhat noisier than that
-of Marion Island, and because the data were taken during the height of
-Arctic summer, the ionospheric plasma cutoff frequency is higher than
-the typical cutoff reflected in the Marion data.
+Research Station (MARS; \ang{79;26;}N, \ang{90;46;}W) on Axel Heiberg
+Island, Nunavut, during July~2019.  The RF signal chain of the MARS
+installation had the same architecture as that shown in
+\autoref{Fig:albatros1_schem}, but the power was supplied by manually
+charged batteries, rather than a solar power system.  The MARS RFI
+environment is somewhat noisier than that of Marion Island, and
+because the data were taken during the height of Arctic summer, the
+ionospheric plasma cutoff frequency is higher than the typical cutoff
+reflected in the Marion data.  Despite the differences in the power
+configuration and RFI environment, the MARS installation is suitable
+for illustrating baseband data writing.
+
+\begin{figure}[t]
+  \begin{center}
+    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_auto_compare.jpg}
+    \caption{\attention{Placeholder figure} Autospectra for one
+      polarization from an \albatros\ pathfinder at MARS (see text for
+      details).  The top row shows spectra that are accumulated
+      directly by the SNAP board, and the middle row shows spectra
+      computed from baseband data with 4-bit quantization.  The two
+      frequency windows, 5.3--12.6~MHz and 12.6--20.0~MHz, are
+      recorded at two separate times, and all waterfall plots are
+      shown with 61-kHz resolution.  The bottom row compares the mean
+      autospectra, with finer, \attention{numbers here} resolution of
+      the baseband spectra.}
+    \label{Fig:baseband_direct_auto}
+  \end{center}
+\end{figure}
+
+\begin{figure}[t]
+  \begin{center}
+    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_phase_compare.jpg}
+    \caption{\attention{Placeholder figure} Phases from the
+      cross-correlation between two orthogonal polarizations from an
+      \albatros\ pathfinder at MARS (see text for details).  The top
+      row shows cross-spectrum phases that are accumulated directly by
+      the SNAP board, and the bottom row shows phases computed from
+      baseband data with 4-bit quantization.  The two frequency
+      windows, 5.3--12.6~MHz and 12.6--20.0~MHz, are recorded at two
+      separate times, and all waterfall plots are shown with 61-kHz
+      resolution.}
+    \label{Fig:baseband_direct_phase}
+  \end{center}
+\end{figure}
 
@@
 corresponding accumulated spectra from the SNAP board are shown for
-the same frequency and time ranges.  The waterfall plots have the same
-61-kHz frequency resolution, set by the resolution of the spectra
-computed by the SNAP board.  The overplotted mean spectra are shown
-with finer resolution (\attention{numbers go here}) from the baseband
-data to illustrate the additional information that is not retained in
-the accumulated spectra.  For these mean spectrum plots, the baseband
-data are processed by
+the same frequency and time ranges.  All of the waterfall plots have
+the same 61-kHz frequency resolution, set by the resolution of the
+spectra computed by the SNAP board.  The overplotted mean spectra are
+shown with finer resolution (\attention{numbers go here}) from the
+baseband data to illustrate the additional information that is not
+available in the accumulated spectra.  For these mean spectrum plots,
+the baseband data are processed by
 inverting\footnote{\url{https://github.com/jrs65/pfb-inverse}} the
-polyphase filter bank to recover time-domain data, and the forward
-polyphase filter bank is then applied to concatenated timestreams of
-an appropriate total length to set the desired frequency resolution.
-The spectra computed from baseband qualitatively agree with those
-directly accumulated by the SNAP board, up to small differences caused
-by the 4-bit quantization.
+polyphase filter bank to recover time-domain data, and the
+forward-direction polyphase filter bank is then applied to
+concatenated timestreams of an appropriate total length to set the
+desired frequency resolution.  \autoref{Fig:baseband_direct_phase}
+shows waterfall plots of phases computed from the cross-correlation
+between the two orthogonal polarizations of the \albatros\ pathfinder
+at MARS, comparing the directly accumulated and baseband data.  For
+both the autospectra and phases, the baseband data qualitatively agree
+with the data directly accumulated by the SNAP board, up to small
+differences caused by the 4-bit quantization.
 
-\attention{more words to come here about phase plots}
+\section{Summary and future outlook}
 
-\section{Conclusions}
+We have presented the design of \albatros, a new interferometer that
+will image the radio sky at $\lesssim30$~MHz using an array of
+autonomous antenna stations installed on Marion Island.  With a
+two-element, directly correlated pathfinder, we have demonstrated that
+clear, repeatable sky signal is visible from Marion down to
+$\lesssim10$~MHz with no data processing or cuts.  We have constructed
+the first prototype autonomous \albatros\ station powered by solar
+panels, and we have successfully tested the electronics and software
+for recording baseband data.
 
-\attention{text goes here}
+With the proof of concept demonstrated from the pathfinder instruments
+presented here, we plan to improve the design of the future
+\albatros\ stations that will be installed at the coastal huts on
+Marion.  The LWA antenna and FEE are currently not optimized for the
+lowest \albatros\ observing frequencies, and we are investigating
+possible modifications to the antenna and FEE designs to improve the
+low frequency response, as well as building in calibration circuitry.
+Because the future \albatros\ stations will be located farther from
+the base and will be more difficult to access on a regular basis, each
+station will require larger total hard drive volume to store baseband
+data over extended periods of time.  We are developing a custom
+low-power hard drive bank with $>100$~TB total storage capacity that
+will employ a USB multiplexer to select and power only one hard drive
+at a time.  The autonomous station pathfinder presented here uses
+solar panels to charge the batteries, and we are investigating the use
+of small wind turbines as a possible alternative for future stations.
 
-% We present the basics of 1-bit correlation here, and show that even in
-% the high-signal limit, 1-bit correlation remains viable.
-
-% discuss design changes for final stations: larger banks of hard
-% drives, possible wind power, etc.
+In addition to Marion Island, we are also planning on installing a
+second \albatros\ array at MARS in the high Arctic.  As described in
+\S\ref{s:obs}, a pathfinder antenna was installed in July 2019 and
+observed for about three weeks to assess the RFI environment and
+ionospheric conditions.  When fully operational, the Marion and MARS
+\albatros\ installations will provide new views of the low-frequency
+sky across both hemispheres.
 

### 2020-07-20 albatros_paper.tex
HCC added first draft of acknowledgments

@@
 
-We are extremely grateful for the anemic carrots on Marion.  Yum.
+We gratefully acknowledge the National Research Foundation (grant
+number 110929) and the South African National Antarctic Programme for
+providing funding and logistical support for our research program.
+The financial assistance of the South African SKA Project (SKA SA)
+towards this research is hereby acknowledged (\url{www.ska.ac.za}).
+We additionally extend our sincere gratitude to the staff at SKA SA
+for hosting our lab tests.  We thank the South African National Space
+Agency for their technical support, the crew of Ultimate Heli for
+safely delivering us and our cargo, and all of the Marion takeover and
+winter team members who provided invaluable advice and field help.
+The authors also wish to thank members of the LWA and RAPID
+collaborations for useful discussions.
 

### 2020-07-26 albatros_paper.tex
HCC fixed accumulation time

@@
 CASPER\footnote{\url{https://casper.berkeley.edu/}}-based polyphase
-filter bank, and the spectra are accumulated over $\sim7$-s intervals.
+filter bank, and the spectra are accumulated over $\sim4$-s intervals.
 A Valon 5007 frequency synthesizer module provides the clock signal

### 2020-07-26 albatros_paper.tex
HCC updated numbers for fine-res baseband spectra

@@
       shown with 61-kHz resolution.  The bottom row compares the mean
-      autospectra, with finer, \attention{numbers here} resolution of
+      autospectra, with finer, 14.6-kHz resolution of
       the baseband spectra.}
@@
 the same 61-kHz frequency resolution, set by the resolution of the
-spectra computed by the SNAP board.  The overplotted mean spectra are
-shown with finer resolution (\attention{numbers go here}) from the
-baseband data to illustrate the additional information that is not
-available in the accumulated spectra.  For these mean spectrum plots,
-the baseband data are processed by
+spectra computed by the SNAP board.  In the overplotted mean spectra,
+the baseband data are shown with finer, 14.6-kHz resolution to
+illustrate the additional information that is not available in the
+accumulated spectra.  For these mean spectrum plots, the baseband data
+are processed by
 inverting\footnote{\url{https://github.com/jrs65/pfb-inverse}} the

### 2020-07-26 albatros_paper.tex
HCC added new version of baseband/direct phase comparison plot

@@
   \begin{center}
-    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_phase_compare.jpg}
-    \caption{\attention{Placeholder figure} Phases from the
-      cross-correlation between two orthogonal polarizations from an
-      \albatros\ pathfinder at MARS (see text for details).  The top
-      row shows cross-spectrum phases that are accumulated directly by
-      the SNAP board, and the bottom row shows phases computed from
-      baseband data with 4-bit quantization.  The two frequency
-      windows, 5.3--12.6~MHz and 12.6--20.0~MHz, are recorded at two
-      separate times, and all waterfall plots are shown with 61-kHz
-      resolution.}
+    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_phase_compare.png}
+    \caption{Phases from the cross-correlation between two orthogonal
+      polarizations from an \albatros\ pathfinder at MARS (see text
+      for details).  The top row shows cross-spectrum phases that are
+      accumulated directly by the SNAP board, and the bottom row shows
+      phases computed from baseband data with 4-bit quantization.  The
+      two frequency windows, 5.3--12.6~MHz and 12.6--20.0~MHz, are
+      recorded at two separate times, and all waterfall plots are
+      shown with 61-kHz resolution.}
     \label{Fig:baseband_direct_phase}

### 2020-08-13 albatros_paper.tex
HCC embiggened the last figure
HCC updated baseband/direct autospectrum comparison figure and text

@@
 achieved to date.  The experiment installation site must be remote to
-keep RFI to a minimum, and polar or near-polar latitiudes generally
+keep RFI to a minimum, and polar or near-polar latitudes generally
 have lower ionospheric plasma frequency cutoffs relative to other
@@
       to a second-stage electronics chain consisting of filters and
-      further amplfication.  The signals are digitized at 250~Msamp/s
+      further amplification.  The signals are digitized at 250~Msamp/s
       by a SNAP board, which includes an on-board FPGA that computes
@@
       electronics chain consisting of filters and further
-      amplfication.  The signals are digitized at 250~Msamp/s by a
+      amplification.  The signals are digitized at 250~Msamp/s by a
       SNAP board, which includes an on-board FPGA that computes
@@
 are designed to incline the solar panels at a relatively steep angle
-to maximize peformance under winter conditions, when sunlight hours
+to maximize performance under winter conditions, when sunlight hours
 are at their minimum. The solar panel mounts have been designed to
@@
   \begin{center}
-    \includegraphics[width=0.9\linewidth]{Figures/albatros2_waterfalls.jpg}
+    \includegraphics[width=\linewidth]{Figures/albatros2_waterfalls.jpg}
     \caption{Spectra from a co-aligned polarization pair from the
@@
 We have been unable to retrieve data from the single autonomous
-station pathfinder on Marion because of COVID-19 and limited bandwidth
-to the island, although we have confirmed that the solar power system
-has successfully met the power demands of the antenna station.  To
-demonstrate baseband writing capability in the absence of Marion data,
-we instead present a short observation that was taken by a separate
-\albatros\ pathfinder station that operated from the McGill Arctic
-Research Station (MARS; \ang{79;26;}N, \ang{90;46;}W) on Axel Heiberg
-Island, Nunavut, during July~2019.  The RF signal chain of the MARS
-installation had the same architecture as that shown in
-\autoref{Fig:albatros1_schem}, but the power was supplied by manually
-charged batteries, rather than a solar power system.  The MARS RFI
-environment is somewhat noisier than that of Marion Island, and
-because the data were taken during the height of Arctic summer, the
-ionospheric plasma cutoff frequency is higher than the typical cutoff
-reflected in the Marion data.  Despite the differences in the power
-configuration and RFI environment, the MARS installation is suitable
-for illustrating baseband data writing.
+station pathfinder on Marion because of COVID-19 restrictions and
+limited bandwidth to the island, although we have confirmed that the
+solar power system has successfully met the power demands of the
+antenna station.  To demonstrate baseband writing capability in the
+absence of Marion data, we instead present a short observation that
+was taken by a separate, single-element \albatros\ pathfinder station
+that operated from the McGill Arctic Research Station (MARS;
+\ang{79;26;}N, \ang{90;46;}W) on Axel Heiberg Island, Nunavut, during
+July~2019.  The RF signal chain of the MARS installation had the same
+architecture as that shown in \autoref{Fig:albatros1_schem}, but the
+power was supplied by manually charged batteries, rather than a solar
+power system.  The MARS RFI environment is somewhat noisier than that
+of Marion Island, and because the data were taken during the height of
+Arctic summer, the ionospheric plasma cutoff frequency is higher than
+the typical cutoff reflected in the Marion data.  Despite the
+differences in the power configuration and RFI environment, the MARS
+installation is suitable for illustrating baseband data writing.
 
@@
   \begin{center}
-    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_auto_compare.jpg}
-    \caption{\attention{Placeholder figure} Autospectra for one
-      polarization from an \albatros\ pathfinder at MARS (see text for
-      details).  The top row shows spectra that are accumulated
-      directly by the SNAP board, and the middle row shows spectra
-      computed from baseband data with 4-bit quantization.  The two
-      frequency windows, 5.3--12.6~MHz and 12.6--20.0~MHz, are
-      recorded at two separate times, and all waterfall plots are
-      shown with 61-kHz resolution.  The bottom row compares the mean
-      autospectra, with finer, 14.6-kHz resolution of
-      the baseband spectra.}
+    \includegraphics[width=\linewidth]{Figures/baseband_direct_auto_compare.png}
+    \caption{Autospectra for one polarization from an
+      \albatros\ pathfinder at MARS (see text for details).  The top
+      row shows spectra that are accumulated directly by the SNAP
+      board, and the middle row shows spectra computed from baseband
+      data with 4-bit quantization.  The two frequency windows,
+      5.3--12.6~MHz and 12.6--20.0~MHz, are recorded at two separate
+      times, and all plots are shown with 61-kHz resolution.  The
+      waterfall plots are shown with a logarithmic color scale to
+      highlight the qualitative agreement in spectral features between
+      the directly-accumulated and baseband spectra.  The bottom row
+      compares the mean autospectra, which agree well when the
+      baseband data are not saturated by bright RFI emission.}
     \label{Fig:baseband_direct_auto}
@@
   \begin{center}
-    \includegraphics[width=0.8\linewidth]{Figures/baseband_direct_phase_compare.png}
+    \includegraphics[width=\linewidth]{Figures/baseband_direct_phase_compare.png}
     \caption{Phases from the cross-correlation between two orthogonal
@@
 the same 61-kHz frequency resolution, set by the resolution of the
-spectra computed by the SNAP board.  In the overplotted mean spectra,
-the baseband data are shown with finer, 14.6-kHz resolution to
-illustrate the additional information that is not available in the
-accumulated spectra.  For these mean spectrum plots, the baseband data
-are processed by
-inverting\footnote{\url{https://github.com/jrs65/pfb-inverse}} the
-polyphase filter bank to recover time-domain data, and the
-forward-direction polyphase filter bank is then applied to
-concatenated timestreams of an appropriate total length to set the
-desired frequency resolution.  \autoref{Fig:baseband_direct_phase}
-shows waterfall plots of phases computed from the cross-correlation
-between the two orthogonal polarizations of the \albatros\ pathfinder
-at MARS, comparing the directly accumulated and baseband data.  For
-both the autospectra and phases, the baseband data qualitatively agree
-with the data directly accumulated by the SNAP board, up to small
-differences caused by the 4-bit quantization.
+spectra computed by the SNAP board, and are normalized so that the
+maximum is unity.  The waterfall plots are shown with a logarithmic
+scale to highlight the qualitative agreement between the
+directly-accumulated and baseband spectra for bright and faint
+spectral features.  The bottom panels show the time-averaged spectra
+on a linear scale to illustrate differences in bright RFI features
+that saturate the the baseband data.  The fraction of baseband data
+with values at the 4-bit extrema are overplotted with spectra, and
+there is agreement between the directly-accumulated and baseband
+spectra except when saturation is present.
+
+% In the overplotted mean spectra, the baseband data are shown with
+% finer, 14.6-kHz resolution to illustrate the additional information
+% that is not available in the accumulated spectra.  For these mean
+% spectrum plots, the baseband data are processed by
+% inverting\footnote{\url{https://github.com/jrs65/pfb-inverse}} the
+% polyphase filter bank to recover time-domain data, and the
+% forward-direction polyphase filter bank is then applied to
+% concatenated timestreams of an appropriate total length to set the
+% desired frequency resolution.  \autoref{Fig:baseband_direct_phase}
+% shows waterfall plots of phases computed from the cross-correlation
+% between the two orthogonal polarizations of the \albatros\ pathfinder
+% at MARS, comparing the directly accumulated and baseband data.  For
+% both the autospectra and phases, the baseband data qualitatively agree
+% with the data directly accumulated by the SNAP board, up to small
+% differences caused by the 4-bit quantization.
 
@@
 of small wind turbines as a possible alternative for future stations.
+We are also developing analysis tools to compute time-domain data from
+the recorded channelized baseband by inverting the polyphase filter
+bank while minimizing artifacts from quantization and saturation.
 
@@
 second \albatros\ array at MARS in the high Arctic.  As described in
-\S\ref{s:obs}, a pathfinder antenna was installed in July 2019 and
-observed for about three weeks to assess the RFI environment and
+\S\ref{s:obs}, a single pathfinder antenna was installed in July 2019
+and observed for about three weeks to assess the RFI environment and
 ionospheric conditions.  When fully operational, the Marion and MARS

### 2020-08-13 albatros_paper.tex
HCC added author list

@@
 
-\markboth{Author's Name}{ALBATROS instrument}
+\markboth{H.~C.~Chiang et al.}{ALBATROS instrument}
 
@@
 
-\author{First Author$^{2}$, Second Author$^{3}$, Third Author$^{3}$ and Fourth Author$^{4}$}
+\author{H.~C.~Chiang$^{1,2,\dagger}$, T.~Dyson$^{1}$, E.~Egan$^{1}$,
+  S.~Eyono$^{2}$, N.~Ghazi$^{2}$, J.~Hickish$^{3}$,
+  J.~M.~J\'auregui--Garcia$^{4}$, V.~Manukha$^{5}$, T.~Moso$^{2}$,
+  J.~Peterson$^{4}$, L.~Philip$^{6}$, J.~L.~Sievers$^{1,6}$,
+  S.~Tartakovsky$^{1}$}
 
 \address{
-$^{2}$Department, University Name, City, State ZIP/Zone, Country, fauthor@university.com\\
-$^{3}$Group, Company, Address, City, State ZIP/Zone, Country\\
-$^{4}$Group, Company, Address, City, State ZIP/Zone, Country, fauthor@company.com
+$^{1}$Department of Physics, McGill University, Montr\'eal, Quebec H3A 2T8, Canada\\
+$^{2}$School of Mathematics, Statistics, and Computer Science,
+  University of KwaZulu--Natal, Durban 4000, South Africa\\
+$^{3}$Department of Astronomy, University of California, Berkeley,
+  California 94720, USA\\
+$^{4}$Department of Physics, Carnegie Mellon University,
+  Pittsburgh, Pennsylvania 15213, USA\\
+$^{5}$South African National Space Agency, Hermanus 7200, South Africa\\
+$^{6}$School of Chemistry and Physics,
+  University of KwaZulu--Natal, Durban 4000, South Africa
 }
@@
 
-\corres{$^{2}$Corresponding author.}
+\corres{$^{\dagger}$Corresponding author: hsin.chiang@mcgill.ca}
 
@@
 radio-frequency interference (RFI).
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.63\linewidth]{Figures/marion_domec_hobart.png}
+    \caption{Minimum plasma frequency predicted by the International
+      Reference Ionosphere model during the last solar minimum.  At
+      some locations on Earth, the plasma frequency may drop as low as
+      $\sim1.5$~MHz.}
+    \label{Fig:iri}
+  \end{center}
+\end{figure}
 
@@
 riometry data for space weather studies~\citep{2014GeoRL..41.5370K}.
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.6\linewidth]{Figures/marion_domec_hobart.png}
-    \caption{Minimum plasma frequency predicted by the International
-      Reference Ionosphere model during the last solar minimum.  At
-      some locations on Earth, the plasma frequency may drop as low as
-      $\sim1.5$~MHz.}
-    \label{Fig:iri}
-  \end{center}
-\end{figure}
 
@@
 
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.75\linewidth]{Figures/corr_efficiency/corr_efficiency.png}
+    \caption{Correlator efficiency $\epsilon$ for a 1-bit correlator
+      as a function of signal-to-noise ratio (SNR).  The efficiency is
+      roughly 0.64 at low SNR and drops monotonically as the SNR
+      increases.  The decrease in $\epsilon$ is relatively gentle,
+      changing by only a factor of 2 for SNR $\sim2$.}
+    \label{fig:1bit_efficiency}
+    \end{center}
+\end{figure}
+
 The autonomous station can be configured to record 1-, 2-, or 4-bit
@@
 stations and the auto-spectrum data from each individual station.
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.7\linewidth]{Figures/corr_efficiency/corr_efficiency.png}
-    \caption{Correlator efficiency $\epsilon$ for a 1-bit correlator
-      as a function of signal-to-noise ratio (SNR).  The efficiency is
-      roughly 0.64 at low SNR and drops monotonically as the SNR
-      increases.  The decrease in $\epsilon$ is relatively gentle,
-      changing by only a factor of 2 for SNR $\sim2$.}
-    \label{fig:1bit_efficiency}
-    \end{center}
-\end{figure}
 
@@
   \begin{center}
-    \includegraphics[width=0.6\linewidth]{Figures/albatros2_lst_phase.jpg}
+    \includegraphics[width=0.8\linewidth]{Figures/albatros2_lst_phase.jpg}
     \caption{Phases from the cross-correlation between two co-aligned

### 2020-08-13 albatros_paper.tex
HCC added acknowledgment to Raul
HCC added acknowledgments to NSERC and PCSP

@@
 We gratefully acknowledge the National Research Foundation (grant
-number 110929) and the South African National Antarctic Programme for
+number 110929), the South African National Antarctic Programme, the
+Natural Sciences and Engineering Research Council of Canada (grant
+number RGPNS-2019-534549), and the Polar Continental Shelf Program for
 providing funding and logistical support for our research program.
@@
 The authors also wish to thank members of the LWA and RAPID
-collaborations for useful discussions.
+collaborations for useful discussions, and Raul Monsalve for helping
+make our first MARS campaign a success.
 

### 2020-08-26 albatros_paper.tex
HCC added back missing text referencing figure 11

@@
       times, and all plots are shown with 61-kHz resolution.  The
-      waterfall plots are shown with a logarithmic color scale to
-      highlight the qualitative agreement in spectral features between
-      the directly-accumulated and baseband spectra.  The bottom row
+      waterfall plots are normalized so that the maximum is unity and
+      are shown with a logarithmic color scale to highlight the
+      qualitative agreement in spectral features between the
+      directly-accumulated and baseband spectra.  The bottom row
       compares the mean autospectra, which agree well when the
@@
 
-\autoref{Fig:baseband_direct_auto} shows autospectra for one
-polarization of the \albatros\ pathfinder installed at MARS, comparing
-the accumulated spectra that are directly computed by the SNAP board
-against spectra that are calculated from baseband data with 4-bit
-quantization.  (Autospectrum information is not preserved with 1-bit
-quantization.)  Baseband data were recorded over two frequency
-windows, 5.3--12.6~MHz and 12.6--20.0~MHz, at separate times, and the
-corresponding accumulated spectra from the SNAP board are shown for
-the same frequency and time ranges.  All of the waterfall plots have
-the same 61-kHz frequency resolution, set by the resolution of the
-spectra computed by the SNAP board, and are normalized so that the
-maximum is unity.  The waterfall plots are shown with a logarithmic
+We present short segments of baseband data that were recorded over two
+adjacent frequency windows, 5.3--12.6~MHz and 12.6--20.0~MHz, at
+separate times.  The baseband data were recorded with 4-bit
+quantization to preserve autospectrum information, which is not
+available with 1-bit quantization.  \autoref{Fig:baseband_direct_auto}
+shows autospectra for one polarization of the \albatros\ pathfinder
+installed at MARS, comparing the accumulated spectra that are directly
+computed by the SNAP board against spectra that are calculated from
+baseband data.  All of the waterfall plots have the same 61-kHz
+frequency resolution, set by the resolution of the spectra computed by
+the SNAP board.  The waterfall plots are shown with a logarithmic
 scale to highlight the qualitative agreement between the
@@
 on a linear scale to illustrate differences in bright RFI features
-that saturate the the baseband data.  The fraction of baseband data
-with values at the 4-bit extrema are overplotted with spectra, and
-there is agreement between the directly-accumulated and baseband
-spectra except when saturation is present.
+that saturate the baseband data.  The fraction of baseband data with
+values at the 4-bit extrema are overplotted with spectra, and there is
+agreement between the directly-accumulated and baseband spectra except
+when significant saturation is present.
+\autoref{Fig:baseband_direct_phase} shows waterfall plots of phases
+computed from the cross-correlation between the two orthogonal
+polarizations of the \albatros\ pathfinder at MARS, comparing the
+directly accumulated and baseband data.  Both sets of recorded data
+qualitatively agree, up to small differences caused by the 4-bit
+quantization.
 
@@
 % concatenated timestreams of an appropriate total length to set the
-% desired frequency resolution.  \autoref{Fig:baseband_direct_phase}
-% shows waterfall plots of phases computed from the cross-correlation
-% between the two orthogonal polarizations of the \albatros\ pathfinder
-% at MARS, comparing the directly accumulated and baseband data.  For
-% both the autospectra and phases, the baseband data qualitatively agree
-% with the data directly accumulated by the SNAP board, up to small
-% differences caused by the 4-bit quantization.
+% desired frequency resolution.
 

### 2020-08-26 albatros_paper.tex
HCC fixed "Mini-Circuits" and Jose-Miguel's affiliation

@@
   J.~M.~J\'auregui--Garcia$^{4}$, V.~Manukha$^{5}$, T.~Moso$^{2}$,
-  J.~Peterson$^{4}$, L.~Philip$^{6}$, J.~L.~Sievers$^{1,6}$,
+  J.~Peterson$^{6}$, L.~Philip$^{7}$, J.~L.~Sievers$^{1,7}$,
   S.~Tartakovsky$^{1}$}
@@
   California 94720, USA\\
-$^{4}$Department of Physics, Carnegie Mellon University,
+$^{4}$Canadian Institute for Theoretical Astrophysics, Toronto, Ontario M5R 2M8, Canada \\
+$^{5}$South African National Space Agency, Hermanus 7200, South Africa\\
+$^{6}$Department of Physics, Carnegie Mellon University,
   Pittsburgh, Pennsylvania 15213, USA\\
-$^{5}$South African National Space Agency, Hermanus 7200, South Africa\\
-$^{6}$School of Chemistry and Physics,
+$^{7}$School of Chemistry and Physics,
   University of KwaZulu--Natal, Durban 4000, South Africa
@@
 The LWA active-balun front-end electronics (FEE) circuit uses a
-MiniCircuits GALI-74+ MMIC to amplify each dipole leg against ground,
+Mini-Circuits GALI-74+ MMIC to amplify each dipole leg against ground,
 presenting each leg with a 50$\ohm$ impedance and providing a nominal
@@
 a $\sim$150~MHz lowpass and receives an additional 12~dB of gain from
-a MiniCircuits GALI-6+ MMIC. This last amplifier drives the output
+a Mini-Circuits GALI-6+ MMIC. This last amplifier drives the output
 signal onto a 100-m 50$\ohm$ coaxial cable. Thus, neglecting mismatch
@@
 Each of the four antenna signals is passed to a second-stage
-electronics chain consisting of an amplifier (Minicircuits ZX60-V63+),
-and a pair of high- and low-pass filters (Minicircuits ZFHP-1R2+ and
+electronics chain consisting of an amplifier (Mini-Circuits ZX60-V63+),
+and a pair of high- and low-pass filters (Mini-Circuits ZFHP-1R2+ and
 SLP-90+) that together band-limit the signal to 1.2--\SI{81}{MHz}.
@@
 50~m away from the antennas. The analog signal chain consists of a
-pair of high- and low-pass filters (Minicircuits ZFHP-1R2+ and
+pair of high- and low-pass filters (Mini-Circuits ZFHP-1R2+ and
 SLP-150+) that together band-limit the signal to 1.2--140~MHz, and the
-filters are followed by a MiniCircuits ZFL-500+ amplifier.  In
+filters are followed by a Mini-Circuits ZFL-500+ amplifier.  In
 contrast to the two-element pathfinder, the low-pass cutoff is

### 2020-08-27 albatros_paper.tex
HCC fixed one dangler to pretty up the spacing
HCC removed hypen from title for consistency

@@
 
-\title{The Array of Long-Baseline Antennas for Taking Radio
+\title{The Array of Long Baseline Antennas for Taking Radio
   Observations from the Sub-Antarctic}
@@
   \begin{center}
-    \includegraphics[width=0.63\linewidth]{Figures/marion_domec_hobart.png}
+    \includegraphics[width=0.6\linewidth]{Figures/marion_domec_hobart.png}
     \caption{Minimum plasma frequency predicted by the International

### 2020-08-27 albatros_paper.tex
HCC minor edits

@@
 the nominal \albatros\ installation locations, the computed
-synthesized beam is as shown in \autoref{Fig:marion_beam}.  The beam
+synthesized beam is shown in \autoref{Fig:marion_beam}.  The beam
 width at 5~MHz is roughly \SI{7}{\arcminute}, which represents over an
@@
 
-\section{Single autonomous station pathfinder}
+\section{Single autonomous station pathfinder}\label{s:autonomous}
 
@@
 frequency windows (with 10--20~MHz total bandwidth) within the full
-0--125~MHz operating range.  The baseband data will be collected
-periodically and subsequently correlated offline.  The
-\albatros\ stations, located at the eight coastal hut sites plus the
-hydro shack and \prizm\ site, will be separated by baselines of
-$\sim20$~km as shown in \autoref{Fig:marion_map_beam}. One fully
-autonomous \albatros\ station, shown in \autoref{Fig:autonomous}, was
-deployed in April 2019 at the hydro shack location (\ang{46;52.205;}S,
+0--125~MHz operating range.  Baseband data will be periodically
+physically retrieved from each station and subsequently correlated
+offline.  The \albatros\ stations, located at the eight coastal hut
+sites plus the hydro shack and \prizm\ site, will be separated by
+baselines of $\sim20$~km as shown in
+\autoref{Fig:marion_map_beam}. One fully autonomous
+\albatros\ station, shown in \autoref{Fig:autonomous}, was deployed in
+April 2019 at the hydro shack location (\ang{46;52.205;}S,
 \ang{37;50.612;}E) on Marion Island as a first step in testing the
@@
 Although the first-deployed two-element pathfinder is located at a
-reasonable walking distance from the main base and uses a generator to
-periodically recharge batteries, the bulk of the antenna stations that
-will comprise the full array will be located at points farther removed
-from the main base and will therefore require fully autonomous energy
-sources.  For the autonomous station pathfinder, we developed a solar
-charging system to power the station, and we are investigating small
-wind turbines for future \albatros\ stations.
+reasonable walking distance from the main base and uses a manually
+operated generator to periodically recharge batteries, the bulk of the
+antenna stations that will comprise the full array will be located at
+points farther removed from the main base and will therefore require
+fully autonomous energy sources.  For the autonomous station
+pathfinder, we developed a solar charging system to power the station,
+and we are investigating small wind turbines for future
+\albatros\ stations.
 
@@
 We have been unable to retrieve data from the single autonomous
-station pathfinder on Marion because of COVID-19 restrictions and
-limited bandwidth to the island, although we have confirmed that the
-solar power system has successfully met the power demands of the
-antenna station.  To demonstrate baseband writing capability in the
-absence of Marion data, we instead present a short observation that
-was taken by a separate, single-element \albatros\ pathfinder station
-that operated from the McGill Arctic Research Station (MARS;
-\ang{79;26;}N, \ang{90;46;}W) on Axel Heiberg Island, Nunavut, during
-July~2019.  The RF signal chain of the MARS installation had the same
-architecture as that shown in \autoref{Fig:albatros1_schem}, but the
-power was supplied by manually charged batteries, rather than a solar
-power system.  The MARS RFI environment is somewhat noisier than that
-of Marion Island, and because the data were taken during the height of
-Arctic summer, the ionospheric plasma cutoff frequency is higher than
-the typical cutoff reflected in the Marion data.  Despite the
-differences in the power configuration and RFI environment, the MARS
-installation is suitable for illustrating baseband data writing.
+station pathfinder on Marion (\S\ref{s:autonomous}) because of
+COVID-19 restrictions and limited bandwidth to the island, although we
+have confirmed that the solar power system has successfully met the
+power demands of the antenna station.  To demonstrate baseband writing
+capability in the absence of Marion data, we instead present a short
+observation that was taken by a separate, single-element
+\albatros\ pathfinder station that operated from the McGill Arctic
+Research Station (MARS; \ang{79;26;}N, \ang{90;46;}W) on Axel Heiberg
+Island, Nunavut, during July~2019.  The RF signal chain of the MARS
+installation had the same architecture as that shown in
+\autoref{Fig:albatros1_schem}, but the power was supplied by manually
+charged batteries, rather than a solar power system.  The MARS RFI
+environment is somewhat noisier than that of Marion Island, and
+because the data were taken during the height of Arctic summer, the
+ionospheric plasma cutoff frequency is higher than the typical cutoff
+reflected in the Marion data.  Despite the differences in the power
+configuration and RFI environment, the MARS installation is suitable
+for illustrating baseband data writing.
 

### 2020-10-08 albatros_paper.tex
HCC removed old comments from main latex file, removed unused references from bib file
added acknowledgement
started responses to referee

@@
 
-% do we want/need to say anything about the omnidirectional primary beam?
-
 \subsection{Front-end active balun}\label{s:fee}
@@
 by 16~V, which is fed on the coaxial cable through a bias tee.
-
-% EE citing the noise figure of the GALI-74+ is particulary misleading because of the large mismatch loss, which directly scales up the noise figure in the HF band.
-
-%% It seems to me that this is too much detail to go into in describing an already published design.
-% All the front end components were incorporated for in a double sided
-% printed circuit board (PCB) as shown in \autoref{Fig:Balun} and the
-% block diagram is shown in \autoref{Fig:Balun Schematic}. The
-% Monolithic Microwave Integrated Circuits (MMICs) is the used design
-% for the PCB. One side of the PCB is populated with components and
-% the other side is a solid copper ground plane aperiodically stitched
-% to the grounded copper on the side populated with components. The
-% receiver system is made up of the active balun, filter and the gain
-% stage that connects to the \SI{100}{\metre} coaxial cable which is
-% connected to the back end \cite{2012PASP..124.1090H}.
-
-% The input impedance (Z\textsubscript{o}) of \SI{50}{\ohm} is
-% introduced to the dipole by the active balun. The signal is then fed
-% through an amplifier which amplifies it by \SI{+24}{\decibel} of
-% gain. The balanced signal is then converted to unbalanced through a
-% 180 \degree hybrid coupler. The band pass filter (BPF) receives the
-% single ended signal in order for it to reject all the frequencies
-% which are not within the range of interest. The signal gets fed to a
-% second amplifier which again amplies it by \SI{+24}{\decibel} of gain
-% and the output impedance of the FEE is matched to a \SI{50}{\ohm}
-% coaxial cable. The bias tee is responsible for providing power to the
-% FEE and extracts the RF signal by the use of the coaxial cable. This
-% unit has an overall gain of $\approx$ \SI{35}{\decibel} and an overall
-% noise figure of $\approx$ \SI{2.7}{\decibel} to $\approx$
-% \SI{2.9}{\decibel} \cite{Memo35}.
 
@@
 
-% data rate ~ 17MB/hour, with compressed scio files
-
 \subsection{Power}
@@
 clock.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
 
@@
 
-% HCC: we probably don't need this figure
-% \begin{figure}[h]
-% 	\begin{center}
-% 		\includegraphics[width=0.5\linewidth]{Figures/balun.jpg}
-% 		\caption{Unenclosed FEE mounted on the ALBATROS-EGG antenna supporting structure.} 
-% 		\label{Fig:Balun}
-% 	\end{center}
-% \end{figure}
-
 \subsection{Back-end electronics}\label{s:autonomous_backend}
@@
 can provide offline synchronization of the \albatros\ stations.
+Because the ORBCOMM and science data are taken at the same time by the
+same system, improvements to the ORBCOMM calibration can be
+immediately carried over into improving the science data calibration,
+even if said improvements take years to realize.
 
@@
 over the full 0--125~MHz span, accumulated over few-second intervals.
+The reduction in bit depth happens only \textit{after} the SNAP board
+has channelized the baseband, and so cross-channel leakage (due to
+\textit{e.g.} RFI and slopes in RF power as seen by the ADCs) is
+unaffected by the low bit depth.  
 An RPi~3B+ controls the SNAP board and and receives the auto- and
@@
 
-% To get the expected SNR from a 1-bit correlator, multiply the SNR
-% derived from the radiometer equation by $\epsilon_{corr}$.
-
 To assess the loss of sensitivity as the signal level increases, we
@@
 $2/\pi$ value.
-
-% One might worry that at high signal levels, the saturation of the
-% 1-bit cross correlation would lead to the noise exploding.  In
-% practice the rolloff in sensitivity is relatively mild, especially in
-% the case of long baselines.  It can be expressed in terms of the
-% correlator efficiency $\epsilon_{corr}$, which is defined to be the
-% ratio of the measured signal-to-noise ratio to the ideal (infinite
-% precision) SNR.  As seen in Figure \ref{fig:1bit_efficiency},
-% $\epsilon_{corr}$ only drops by a factor of $\sim$2 as the signal
-% power goes from 0 to a few times the noise power.  We stress that the
-% signal level in question is the part that correlates between the two
-% antennas.  In the case of long baselines (where long means the fringe
-% spacing is small compared to the primary beam/antenna response
-% pattern) that are not dominated by a single bright source, the signal
-% power will always be smaller than the noise power, and so
-% $\epsilon_{corr}$ is unlikely to drop below $\sim$0.5\footnote{A quick
-%   estimate can be made by analogy to the behavior of dishes in the UV
-%   plane in the flat sky approximation.  While all power in the UV
-%   plane (plus any system noise) goes into an individual antenna's
-%   electric field, the correlated part only has contribution from the
-%   area in the UV plane within the width of the UV-space primary beam
-%   of the UV-space coordinate.  If the sky can be described as a
-%   Gaussian random field, in the most pessimistic case this is roughly
-%   the aperture filling factor of the antenna pair.  In our case, where
-%   the antennas are approximately dipolar, the filling factor will be
-%   the square of the wavelength over the baseline length.  As long as
-%   the baselines are several wavelengths or longer, the correlated
-%   power will be small, and the correlator efficiency will be close to
-%   the ideal 1-bit value of $\frac{2}{\pi}$.}.
 
@@
 
-% note to self: look up time of day that corresponds to LST period
-% where fringes appear to extend below 10 MHz, see if that's night
-% time
-
 We have been unable to retrieve data from the single autonomous
@@
 
-% In the overplotted mean spectra, the baseband data are shown with
-% finer, 14.6-kHz resolution to illustrate the additional information
-% that is not available in the accumulated spectra.  For these mean
-% spectrum plots, the baseband data are processed by
-% inverting\footnote{\url{https://github.com/jrs65/pfb-inverse}} the
-% polyphase filter bank to recover time-domain data, and the
-% forward-direction polyphase filter bank is then applied to
-% concatenated timestreams of an appropriate total length to set the
-% desired frequency resolution.
-
 \section{Summary and future outlook}
@@
 providing funding and logistical support for our research program.
-The financial assistance of the South African SKA Project (SKA SA)
-towards this research is hereby acknowledged (\url{www.ska.ac.za}).
-We additionally extend our sincere gratitude to the staff at SKA SA
-for hosting our lab tests.  We thank the South African National Space
-Agency for their technical support, the crew of Ultimate Heli for
-safely delivering us and our cargo, and all of the Marion takeover and
-winter team members who provided invaluable advice and field help.
-The authors also wish to thank members of the LWA and RAPID
-collaborations for useful discussions, and Raul Monsalve for helping
-make our first MARS campaign a success.
+This research was undertaken, in part, thanks to funding from the
+Canada 150 Program.  The financial assistance of the South
+African SKA Project (SKA SA) towards this research is hereby
+acknowledged (\url{www.ska.ac.za}).  We additionally extend our
+sincere gratitude to the staff at SKA SA for hosting our lab tests.
+We thank the South African National Space Agency for their technical
+support, the crew of Ultimate Heli for safely delivering us and our
+cargo, and all of the Marion takeover and winter team members who
+provided invaluable advice and field help.  The authors also wish to
+thank members of the LWA and RAPID collaborations for useful
+discussions, and Raul Monsalve for helping make our first MARS
+campaign a success.
 

### 2020-10-27 albatros_paper.tex
started responses to referees
added some more comment responses

@@
 resolution measurements at the lowest frequencies, particularly in the
-southern hemisphere.  The first step toward laying the groundwork for
+southern hemisphere.
+
+The first step toward laying the groundwork for
 possible measurements of the dark ages is obtaining an improved map of
@@
 efficiency is unlikely to decrease significantly from the ideal
-$2/\pi$ value.
+$2/\pi$ value.  This remains true even when the brightest radio
+sources in the sky are in the beam (the sun is irrelevant since
+ionospheric effects restrict \albatros\ to night-time observing).
+Centaurus A \citep{culgoora1} and M1 \citep{Braude1969} only affect
+the total power expected from the Global Sky Model \citep{gsm2008} at
+the $\sim$10\% level.  Additionally, as will be shown later in this
+work, preliminary ALBATROS data show that visibilities are only a few
+percent of the total power amplitude, consistent with our expectation
+that diffuse emission dominates even the brightest sources given the
+$\sim$steradian solid angle of the primary beam.
 
@@
       cross-spectrum is about two orders of magnitude fainter than the
-      autospectra.  Repeatable structure from the Galaxy is visible
+      autospectra (.  Repeatable structure from the Galaxy is visible
       over the three-day time scale in all plots.}

### 2020-10-29 albatros_paper.tex
added scinet acknowledgement
HCC updated some responses

--- 2020-10-08 albatros_paper.tex
@@
 \SIrange{0.025}{13}{\MHz} with $\sim 10$\degree\ resolution at
-\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  More recent ground-based
+\SI{4.7}{\MHz}~\citep{1975A&A....40..365A}.  Subsequent ground-based
 experiments include the Dominion Radio Astrophysical Observatory
-surveys of the northern sky at 10~MHz and 22~MHz, with
+(DRAO) surveys of the northern sky at 10~MHz and 22~MHz, with
 $\sim2$\degree\ and 1.1--1.7\degree\ resolution,
@@
 with \SI{15}{\arcminute} resolution between 36.528~MHz and
-73.152~MHz~\citep{2018AJ....156...32E}.  Although this experimental
-list is not comprehensive, it does illustrate the dearth of
-information about the $\lesssim 30$~MHz sky and the lack of high
-resolution measurements at the lowest frequencies, particularly in the
-southern hemisphere.  The first step toward laying the groundwork for
+73.152~MHz~\citep{2018AJ....156...32E}.  The dearth of information
+about the $\lesssim 30$~MHz sky, particularly in the southern
+hemisphere, is illustrated by the Global Sky
+Model~\citep{2017MNRAS.464.3486Z}, which incorporates the DRAO 10~MHz
+and 22~MHz data as the only two inputs at these low frequencies with
+sufficiently meaningful sky coverage and resolution.
+% Although this experimental list is not comprehensive, it does
+% illustrate the dearth of information about the $\lesssim 30$~MHz sky
+% and the lack of high resolution measurements at the lowest
+% frequencies, particularly in the southern hemisphere.
+
+The first step toward laying the groundwork for
 possible measurements of the dark ages is obtaining an improved map of
@@
 can provide offline synchronization of the \albatros\ stations.
-Because the ORBCOMM and science data are taken at the same time by the
-same system, improvements to the ORBCOMM calibration can be
-immediately carried over into improving the science data calibration,
-even if said improvements take years to realize.
+Because the ORBCOMM and science data are recorded at the same time by
+the same system, improvements to the timing calibration can be applied
+in post-processing.
 
@@
 The reduction in bit depth happens only \textit{after} the SNAP board
-has channelized the baseband, and so cross-channel leakage (due to
-\textit{e.g.} RFI and slopes in RF power as seen by the ADCs) is
-unaffected by the low bit depth.  
-An RPi~3B+ controls the SNAP board and and receives the auto- and
-cross-spectra via GPIO connections, and the spectra are saved to an
-on-board SD card.  The baseband data are passed from the SNAP board to
-the RPi via ethernet and written to external hard drives.  The
-introduction of gigabit ethernet with the RPi~3B+ model has enabled
-the high data throughput associated with writing baseband.  As a
-benchmark, 1-bit baseband recording of two polarizations over 10~MHz
-of bandwidth yields an approximate data rate of 5~MB/s, or 0.4~TB/day.
+has channelized the baseband, and the cross-channel leakage (due to,
+e.g., RFI and slopes in RF power as seen by the ADCs) is therefore
+unaffected by the low bit depth.  An RPi~3B+ controls the SNAP board
+and and receives the auto- and cross-spectra via GPIO connections, and
+the spectra are saved to an on-board SD card.  The baseband data are
+passed from the SNAP board to the RPi via ethernet and written to
+external hard drives.  The introduction of gigabit ethernet with the
+RPi~3B+ model has enabled the high data throughput associated with
+writing baseband.  As a benchmark, 1-bit baseband recording of two
+polarizations over 10~MHz of bandwidth yields an approximate data rate
+of 5~MB/s, or 0.4~TB/day.
 

### 2020-10-29 albatros_paper.tex

@@
 This research was undertaken, in part, thanks to funding from the
-Canada 150 Program.  The financial assistance of the South
+Canada 150 Program.  This research was enabled in part by support
+provided by SciNet(https://www.scinethpc.ca/) and Compute Canada
+(www.computecanada.ca).  The financial assistance of the South
 African SKA Project (SKA SA) towards this research is hereby

### 2020-10-29 albatros_paper.tex
HCC added new figure, updated comments

--- 2020-10-29 albatros_paper.tex
@@
   S.~Eyono$^{2}$, N.~Ghazi$^{2}$, J.~Hickish$^{3}$,
-  J.~M.~J\'auregui--Garcia$^{4}$, V.~Manukha$^{5}$, T.~Moso$^{2}$,
-  J.~Peterson$^{6}$, L.~Philip$^{7}$, J.~L.~Sievers$^{1,7}$,
-  S.~Tartakovsky$^{1}$}
+  J.~M.~J\'auregui--Garcia$^{4}$, V.~Manukha$^{5}$, T.~M\'enard$^{1}$,
+  T.~Moso$^{2}$, J.~Peterson$^{6}$, L.~Philip$^{7}$,
+  J.~L.~Sievers$^{1,7}$, S.~Tartakovsky$^{1}$}
 
@@
 
-\section{Two-element pathfinder}\label{s:2elem}
-
 \begin{figure}
@@
 \end{figure}
+
+\section{Two-element pathfinder}\label{s:2elem}
 
@@
 $2/\pi \approx 0.64$, and if the signal level increases to two times
-the  
-noise level, $\epsilon$ decreases by only a factor of $\sim2$.  The
-final \albatros\ array will have baselines that are long relative to
-the observing wavelength, and the correlated component of the electric
-field (which sets the relevant signal level) is likely a small
-fraction of the total received power.  This qualitative argument can
-by made by considering antennas in the $uv$~plane in the flat-sky
+the noise level, $\epsilon$ decreases by only a factor of $\sim2$.
+The final \albatros\ array will have baselines that are long relative
+to the observing wavelength, and the correlated component of the
+electric field (which sets the relevant signal level) is likely a
+small fraction of the total received power.  This qualitative argument
+can by made by considering antennas in the $uv$~plane in the flat-sky
 approximation.  Any individual antenna receives all power present in
@@
 efficiency is unlikely to decrease significantly from the ideal
-$2/\pi$ value.
+$2/\pi$ value.  This efficiency behavior remains true even when the
+brightest radio sources are visible, since the primary beam
+encompasses more than a steradian solid angle (the sun is irrelevant
+since ionospheric effects restrict \albatros\ to night-time
+observing).  Centaurus~A~\citep{culgoora1} and M1~\citep{Braude1969}
+affect the total power expected from the Global Sky
+Model~\citep{gsm2008} at only the $\sim$10\% level.  Additionally, as
+will be shown in \S\ref{s:obs}, preliminary \albatros\ data
+demonstrate that the visibilities are only a few percent of the total
+power amplitude, thus indicating that diffuse emission dominates even
+the brightest sources over the large primary beam.
+
+\begin{figure}[t]
+  \begin{center}
+    \includegraphics[width=\linewidth]{Figures/albatros2_waterfalls.jpg}
+    \caption{Spectra from a co-aligned polarization pair from the
+      two-element \albatros\ pathfinder, shown as a function of
+      frequency and time.  The auto- and cross-spectra are shown in
+      the top and bottom rows, respectively.  The spectrum magnitudes
+      are in uncalibrated ADC units on a logarithmic scale, and the
+      cross-spectrum amplitude is about two orders of magnitude
+      fainter than the autospectra.  The cross-spectrum phase is shown
+      in radians.  Repeatable structure from the Galaxy is visible
+      over the three-day time scale in all plots.}
+    \label{Fig:albatros2_waterfalls}
+  \end{center}
+\end{figure}
 
@@
   \begin{center}
-    \includegraphics[width=\linewidth]{Figures/albatros2_waterfalls.jpg}
-    \caption{Spectra from a co-aligned polarization pair from the
-      two-element \albatros\ pathfinder, shown as a function of
-      frequency and time.  The auto- and cross-spectra are shown in
-      the top and bottom rows, respectively.  The spectrum magnitudes
-      are in uncalibrated ADC units on a logarithmic scale, and the
-      cross-spectrum is about two orders of magnitude fainter than the
-      autospectra.  Repeatable structure from the Galaxy is visible
-      over the three-day time scale in all plots.}
-    \label{Fig:albatros2_waterfalls}
+    \includegraphics[width=0.7\linewidth]{Figures/albatros2_auto_model.png}
+    \caption{Top panel: simulated $S11$ for the LWA antenna,
+      illustrating the steep signal loss below $\sim30$~MHz.  Bottom
+      panel: median uncalibrated autospectrum for one of the
+      polarizations in the two-element \albatros\ pathfinder, compared
+      against a crude sky signal estimate given by the product of $(1
+      - S11)$ with a nominal $\nu^{-2.6}$ synchrotron spectrum.  This
+      simple model qualitatively demonstrates that the decrease in
+      autospectrum power below $\sim30$~MHz is caused primarily by the
+      antenna response.}
+    \label{Fig:albatros2_auto_model}
   \end{center}
@@
 drop-off below $\lesssim30$~MHz in the autospectra is caused largely
-by the combined response of the LWA antenna and FEE.  Although the LWA
-antenna is not optimized for the lowest \albatros\ observing
-frequencies, as described in \S\ref{s:antenna}, it is sufficient for
-these initial, exploratory measurements.  The RFI lines at
-$\lesssim20$~MHz arise primarily from shortwave radio transmission
-reflecting off the ionosphere.  During the night, when the ionospheric
-plasma cutoff frequency drops, the maximum frequency of the RFI
-contamination falls to $\sim10$~MHz.
+by the combined response of the LWA antenna and FEE, as illustrated in
+\autoref{Fig:albatros2_auto_model}.  Although the LWA antenna is not
+optimized for the lowest \albatros\ observing frequencies, as
+described in \S\ref{s:antenna}, it is sufficient for these initial,
+exploratory measurements.  The RFI lines at $\lesssim20$~MHz arise
+primarily from shortwave radio transmission reflecting off the
+ionosphere.  During the night, when the ionospheric plasma cutoff
+frequency drops, the maximum frequency of the RFI contamination falls
+to $\sim10$~MHz.
 

### 2020-10-30 response_to_referee.tex
HCC moved referee report responses into a proper latex file

\documentclass[11pt]{article}
\usepackage{palatino}
\usepackage{url}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[square,sort&compress]{natbib}
\usepackage[small,compact]{titlesec}
\usepackage[margin=0.7in]{geometry}

\setlength{\parskip}{0.07in}
\setlength{\bibsep}{0.05in}

\bibpunct{[}{]}{,}{n}{}{}

\makeatletter
\def\subsize{\@setsize\subsize{12pt}\xipt\@xipt}
\def\section{\@startsection {section}{1}{\z@}{1.0ex plus 
1ex minus .2ex}{.2ex plus .2ex}{\normalsize\bf}}
\def\subsection{\@startsection {subsection}{2}{\z@}{.2ex 
plus 1ex} {.2ex plus .2ex}{\subsize\bf}}
\makeatother

\def\scihi{{\sc SCI-HI}}
\def\albatros{ALBATROS}
\def\prizm{PRI$^{\rm Z}$M}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\noindent Dear Referees:

Thank you for your comments and constructive feedback on our paper.
Below are our responses to your comments, as well as descriptions of
corresponding manuscript changes.

\noindent \textcolor{blue}{1) Starting with the antenna, the authors
  mention this is not optimised for lower than 10MHz and another
  antenna needs to be developed but there is hardly any discussion on
  this. Just from the plots in figure 8, it is clear the performance
  of the antenna drops pretty rapidly below 30MHz, thus implying this
  antenna is pretty poorly matched at the primary frequencies of
  interest here. I would have liked to see at least some information
  about this antenna in the paper, perhaps even a plot of S11 which
  surely the authors have access to. }

We have included a new figure (9) that illustrates the simulated $S11$
for the antenna, in addition to an overplot of the median autospectrum
with a crude sky signal estimate given by $(1-S11)$ multiplied with a
$\nu^{-2.6}$ spectrum.

\noindent \textcolor{blue}{2) To develop an antenna to work
  effectively below 30MHz down to a few MHz, you will need to make it
  significantly larger, implying there will be major challenges in how
  you construct and deploy an antenna which may be 5m wide. If this is
  not the case and you are using an electrically short, albeit fat
  dipole, then the antenna is horribly mismatched at the lower
  frequencies. In my view this will have a major impact on 1-bit
  quantisation. How will that work when there is a 30dB or even 40dB
  slope across the band?}

\noindent \textcolor{blue}{3) Further on the 1-bit quantisation
  approach, would you not only need a better matched antenna but also
  an equalised analogue system to remove the extremely high slope from
  the synchrotron emission at low frequencies. This can be up to 20dB
  at these frequencies. Furthermore, despite talking about 1-bit
  quantisation, as far as I know the plots in the paper are all using
  4 or more bit? Has this been tested in the field or in the lab. I do
  not doubt it will work but it will need careful levelling and
  testing and ideally should be coupled with a noise injection signal
  for calibration.}

In response to both comments above, the SNAP processes the baseband
data using the full resolution of the ADCs (8-bit, with a 14-bit
version possibly in the future) and internally works at 18 bits.  It
is only after channelization that the data are downsampled, so
happily, concerns about cross-channel leakage (either due to RFI,
slopes across the band, antenna performance etc.) aren't affected by
the bit depth at which we save the data.  We have now clarified this
point in section 4.1 of the text and thank the referee for catching
the omission.

\noindent \textcolor{blue}{4) Regarding calibration of this
  instrument, there is virtually no mention of it. This is supposed to
  be a precision cosmology instrument and therefore I would have
  expected some more discussion on calibration. Even if not going down
  the route of an EDGES-style approach, having e.g. a Dicke switch in
  there would allow some measure of the scale and offset.}

First, we stress ALBATROS is not meant to be a precision cosmology
instrument---that will have to wait for future telescope generations.
Dicke switching, at least as part of regular operations, won't add
very much because we can calibrate gain variations off the Galactic
signal.  Each station saves total power autospectra, which have
enormous SNR and are repeated day-to-day.  ({\bf RESPOND TO THIS:} say
something about measuring total power offset - presumably by
comparison to PRIZM, and something about beam calibration?)

\noindent \textcolor{blue}{5) An important aspect of developing an
  autonomous instrument like this is timing. I can see the authors
  have thought about this and discussed it in the paper but have there
  been any experiments of running such systems for months on end and
  analysing the drifts. It seems like something that could be done
  fairly easily in the lab for extended periods of time. If there is
  no data to present on this, then some discussion about such possible
  plans would help.}

Unfortunately all we have are the preliminary lab tests.  The setup
was literally a few pieces of wire hanging off an LWA front end
sitting inside the lab, not even next to a window.  With just a few
minutes of that, we were able to synchronize the EW and NS
polarizations to about 0.1ns.  Our plan was to then go to the roof and
carry out proper tests (exactly the ones the referee suggests), but
unfortunately COVID shut down lab access just a couple of days after
the lab tests.  Similarly, we should have timing infomation from the
data on disk at Marion, but all science efforts were cancelled during
the 2020 voyage, so we have been unable to retrieve the data.  A
talented undergraduate is doing this work for his thesis, now that
labs are slowly opening back up, but the results will not be ready on
the timescale of resubmission.  We have added text in section 4.1
clarifying that the ORBCOMM and science data are recorded
simultaneously, and we can therefore interatively improve the timing
calibration in post-processing.  Otherwise we cast ourselves on the
mercy of the journal and the referee to let us defer to a future paper
the analysis we would have loved to have been able to put here.

\noindent \textcolor{blue}{p.2: ``recent ground-based experiments''
  include a 1976 reference. Doesn't seem very recent.}

Changed wording from ``recent'' to ``subsequent.''

\noindent \textcolor{blue}{Could add 45 MHz efforts of Alvarez and
  Guzman.}

Since our discussion focuses on observations below 30 MHz, we feel
that these 45 MHz observations are beyond the scope of our
introductory text.

\noindent \textcolor{blue}{The statement ``Although this experimental
  list is not comprehensive, it does illustrate the dearth of
  information about ..'' is a bit self-defeating. A smaller list would
  illustrate an even larger dearth! I think it would be good to make
  this a complete list, given the fact that it is very short.}

Although we would love to one day write a review article (or read one;
to the best of our knowledge, such a review article doesn't presently
exist), compiling a comprehensive list that's 100\% accurate is a
non-trivial exercise.  We nevertheless agree that the text should be
revised, so we have now included a reference to the Global Sky Model,
which uses only the DRAO 10 MHz and 22 MHz maps as suitable model
inputs below 30 MHz.

\noindent \textcolor{blue}{para 2 is a bit long - split at ``The first step toward...''?}

Done.

\noindent \textcolor{blue}{These sections seem fine, but some more
  information about the LWA antenna below 10 MHz would be useful. The
  sentence ``LWA antenna is not optimized for observations below 10
  MHz...'' seems an understatement given that $<10$ MHz is outside the
  published frequency capability of the antenna. A more informed
  statement about sensitivity (or lack thereof would be useful). For
  example, the lack of Galactic Plane and RFI signal below 8 MHz in
  various plots (eg Figs 8, 11) looks more like there might be
  complete loss of sensitivity. Please clarify.}

We have included a new figure (9) that illustrates the simulated $S11$
for the antenna, in addition to an overplot of the median autospectrum
with a crude sky signal estimate given by $(1-S11)$ multiplied with a
$\nu^{-2.6}$ spectrum.

\noindent \textcolor{blue}{The review of 2-level correlator efficiency
  vs S/N ratio is interesting and a nice reminder to radio astronomers
  about the very different regime such a telescope could be
  operating. But the last paragraph of Section 4.2 dismisses the
  suggestion that the S/N ratio could be non-zero with a weird
  argument about Gaussian random fields. But the reality is if there
  is a massive continuum source in the field of view (Crab Nebula,
  Sun, Galactic Plane which all have structure on size scales $<1$
  deg), then this might indeed be a huge concern. The radio continuum
  sky is obviously not a Gaussian random field.}

We agree that the sky is certainly not a Gaussian random field, but to
get well away from the SNR<1 regime requires that a compact source
dominate the total power coming into the antenna, not just the power
in the visibility.  For most radio telescopes this would absolutely be
a concern, but the primary beam of ALBATROS is huge.  We already know
from e.g.\ EDGES that the total power is dominated by the Galactic
signal, and in PRIZM, the Crab (and typically the sun) are not obvious
in total power.  Due to ionospheric effects ALBATROS will not
generally be conducting daytime observing, and using the GSM and Crab
fluxes in the 10-80 MHz range, we expect the Crab is only a $~10$\%
effect in the total power, as long as the Galaxy is not self-absorbed.
Similarly, in Fig. 8, for a 100m baseline, the visibilities seen by
ALBATROS are only a few percent of the total power.  The text in
section 4.2 has been updated to include these details.

\noindent \textcolor{blue}{The waterfall plots are all fairly
  interesting, but of not much practical value without
  calibration. What is the frequency response of the system? How much
  fainter is the RFI in the cross-correlations than the
  autocorrelations? These simple questions can be answered with a
  simple model of how the system noise changes with frequency or
  utilising the nice Galactic plane drift scans in combination with a
  crude model.}

{\bf RESPOND TO THIS}

\noindent \textcolor{blue}{Fig.8 caption: mention if the amplitude
  units are linear or log (the latter I think?). Also phase (radians I
  think?), although the latter has too much wrapping to be useful.}

We have added this information to the caption.

\noindent \textcolor{blue}{I suggest extracting some 1-d plots of
  amplitude and phase - these would be a great complement to the
  waterfall plots as they will contain features more difficult to see
  than on simple images.}

With the addition of figure 9, a 1D plot of the median autospectrum is
now present.  1D plots of the phase are somewhat more difficult to
meaningfully extract since the structure changes dramatically with
time, and figure 10 (formerly 9) is meant to highlight the features
that are repeatable.

\noindent \textcolor{blue}{Perhaps mention (I didn't see) information
  about the frequency dependent beam size of the antenna, and the
  location of the phase centre of the interferometer (fixed at
  zenith?).}

{\bf RESPOND TO THIS}

\noindent \textcolor{blue}{wind turbines have been investigated for
  potential use in several observatories before. Good idea potentially
  for the Marion site, but they are RFI sources and their motor parts
  or turbine blades may act as modulated reflectors or dielectrics.}

We agree, and investigating low-RFI solutions for wind turbines is
work in progress.  We are aware that low-RFI wind turbines are already
being developed for e.g.\ the ARIANNA experiment (arXiv:1903.01609).

\noindent\rule{\textwidth}{0.7pt}

Final note: we have added T.~M\'enard to the author list because he
contributed the $S11$ simulation in Figure~9.

\end{document}

### 2020-10-30 response_to_referee.tex
HCC added beam solid angle and phase center bits

@@
 generally be conducting daytime observing, and using the GSM and Crab
-fluxes in the 10-80 MHz range, we expect the Crab is only a $~10$\%
+fluxes in the 10-80 MHz range, we expect the Crab is only a $\sim10$\%
 effect in the total power, as long as the Galaxy is not self-absorbed.
@@
 
-{\bf RESPOND TO THIS}
+We have added a sentence about the beam size variation (2.2--2.7
+steradians over 5--100~MHz) and the phase center (at zenith) in
+sections 3.1 and 3.2, respectively.
 

### 2020-10-30 albatros_paper.tex
HCC added beam solid angle and phase center bits

@@
 cardinal directions.  Welded wire mesh screens, roughly 3~m on a side,
-are installed on the ground below the antennas.  Although the LWA
-antenna is not optimized for observations below 10~MHz, using this
-standard antenna allowed an initial test of the site and of the
-interferometer systems.  For the final \albatros\ array, we are
-exploring alternative antenna designs that will cover the full
-frequency range.
+are installed on the ground below the antennas.  The beam pattern is
+roughly omnidirectional with a solid angle that varies between 2.2 and
+2.7 steradians over 5--100~MHz.  Although the LWA antenna is not
+optimized for observations below 10~MHz, using this standard antenna
+allowed an initial test of the site and of the interferometer systems.
+For the final \albatros\ array, we are exploring alternative antenna
+designs that will cover the full frequency range.
 
@@
 $\sim$37~dB~\citep{2012PASP..124.1090H}.  Each FEE circuit is powered
-by 16~V, which is fed on the coaxial cable through a bias tee.
+by 16~V, which is fed on the coaxial cable through a bias tee.  The
+lengths of the coaxial cables are the same for both antennas, thus
+placing the phase center at zenith.
 
@@
       372 hours of data are shown here, binned in local sidereal
-      time.}
+      time, and the color stretch is in radians.}
     \label{Fig:albatros2_phase}

### 2020-10-30 response_to_referee.tex
HCC added unwrapped phase plot to referee response

@@
 \usepackage{palatino}
+\usepackage{graphicx}
 \usepackage{url}
@@
 With the addition of figure 9, a 1D plot of the median autospectrum is
-now present.  1D plots of the phase are somewhat more difficult to
-meaningfully extract since the structure changes dramatically with
-time, and figure 10 (formerly 9) is meant to highlight the features
-that are repeatable.
+now present.  We have extracted a few 1D plots of the unwrapped phase
+along the time axis (scaled by frequency), and we feel that the
+results are not sufficiently interesting to add to the paper, although
+we include the plot here for reference.
+\begin{figure}[h]
+  \vspace{-5pt}
+  \begin{center}
+    \includegraphics*[angle=0,width=0.5\textwidth]{Figures/unwrapped_phase_3freq.png}
+  \end{center}
+  \vspace{-5pt}
+\end{figure}
 

### 2020-10-30 response_to_referee.tex
HCC...one more comment to go...

@@
 
-{\bf RESPOND TO THIS}
+We prefer to defer proper calibration to a future paper since the
+instrumentation presented here is intended as a proof of concept, and
+crude calibration that isn't fully thought out is also of limited
+practical value.  The frequency response of the system is roughly
+illustrated with the new addition of figure~9.  To address the
+question about RFI, we have added an extra phrase in section~5
+explaining that the cross-spectrum RFI is about a factor of two
+fainter than the autospectrum RFI.
 

### 2020-10-30 albatros_paper.tex
HCC...one more comment to go...

@@
 primarily from shortwave radio transmission reflecting off the
-ionosphere.  During the night, when the ionospheric plasma cutoff
-frequency drops, the maximum frequency of the RFI contamination falls
-to $\sim10$~MHz.
+ionosphere and are roughly a factor of two fainter in the
+cross-spectrum magnitude in comparison to the autospectrum.  During
+the night, when the ionospheric plasma cutoff frequency drops, the
+maximum frequency of the RFI contamination falls to $\sim10$~MHz.
 

### 2020-10-30 response_to_referee.tex
HCC fixed a stray <

@@
 We agree that the sky is certainly not a Gaussian random field, but to
-get well away from the SNR<1 regime requires that a compact source
+get well away from the SNR$<$1 regime requires that a compact source
 dominate the total power coming into the antenna, not just the power

### 2020-10-30 response_to_referee.tex
added more responses on calibration

--- 2020-10-30 response_to_referee.tex
@@
 signal.  Each station saves total power autospectra, which have
-enormous SNR and are repeated day-to-day.  ({\bf RESPOND TO THIS:} say
-something about measuring total power offset - presumably by
-comparison to PRIZM, and something about beam calibration?)
+enormous SNR and are repeated day-to-day.  We find the instrument is
+very stable, with RMS gain fluctuations \<0.6\% over several days,
+and typical gain calibration errors of \<0.04\% on 3-second timescales
+based on the galactic signal.  Any noise offsets will in general not
+contribute to cross-correlations and so the chief concern is to remove
+them when developing a galactic model.  PRIZM, which has several
+levels of calibration switching, is co-located with ALBATROS, has
+similar beams, and operates in a similar frequency range (\>30 MHz).
+We can derive an approximate absolute calibration by comparing the
+diurnal variation in galactic signal (which is insensitive to any
+offsets) bewteen PRIZM and ALBATROS.  We have updated the text to
+reflect these numbers.
 

### 2020-10-30 albatros_paper.tex
added more responses on calibration

@@
 affect the total power expected from the Global Sky
-Model~\citep{gsm2008} at only the $\sim$10\% level.  Additionally, as
+Model (GSM)~\citep{gsm2008} at only the $\sim$10\% level.  Additionally, as
 will be shown in \S\ref{s:obs}, preliminary \albatros\ data
@@
 
-As a qualitative illustration of the sky signal repeatability,
+We can estimate the instrumental gain stability by comparing the total
+power between the different days shown in
+\autoref{Fig:albatros2_waterfalls}.  We find that the RMS gain
+fluctuations between 30 and 40~MHz (where the Galactic signal peaks in the
+data) are less than 1\%.  Further, we find that the typical noise on
+$\sim$3-second timescales is 0.04\% of the power.  The low noise suggests that we
+can carry out relative calibration with sub-percent accuracy by using
+the autospectra recorded by each autonomous station (absolute calibration
+could be carried out by comparison to either \prizm\, which is
+co-located and absolutely calibrated, or \textit{e.g.} the GSM).
+As a qualitative illustration of the smaller-scale sky signal repeatability,
 \autoref{Fig:albatros2_phase} shows the phases of the cross-spectra

### 2020-10-30 response_to_referee.tex
HCC final changes!!!!

--- 2020-10-30 response_to_referee.tex
@@
 \usepackage[small,compact]{titlesec}
-\usepackage[margin=0.7in]{geometry}
+\usepackage[margin=0.85in]{geometry}
 
@@
 signal.  Each station saves total power autospectra, which have
-enormous SNR and are repeated day-to-day.  ({\bf RESPOND TO THIS:} say
-something about measuring total power offset - presumably by
-comparison to PRIZM, and something about beam calibration?)
+enormous SNR and are repeated day-to-day.  We find the instrument is
+very stable, with RMS gain fluctuations $<$0.6\% over several days,
+and typical gain calibration errors of $<$0.04\% on 3-second
+timescales based on the Galactic signal.  Any noise offsets will in
+general not contribute to cross-correlations and so the chief concern
+is to remove them when developing a Galactic model.  PRIZM, which has
+several levels of calibration switching, is co-located with ALBATROS,
+has similar beams, and operates in a similar frequency range ($>$30
+MHz).  We can derive an approximate absolute calibration by comparing
+the diurnal variation in Galactic signal (which is insensitive to any
+offsets) between PRIZM and ALBATROS.  We have updated the text in
+section~5 to reflect these numbers.
 
@@
 unfortunately COVID shut down lab access just a couple of days after
-the lab tests.  Similarly, we should have timing infomation from the
+the lab tests.  Similarly, we should have timing information from the
 data on disk at Marion, but all science efforts were cancelled during
@@
 clarifying that the ORBCOMM and science data are recorded
-simultaneously, and we can therefore interatively improve the timing
+simultaneously, and we can therefore iteratively improve the timing
 calibration in post-processing.  Otherwise we cast ourselves on the
@@
 
+\pagebreak
+
 \noindent \textcolor{blue}{Perhaps mention (I didn't see) information

### 2020-10-30 albatros_paper.tex
HCC final changes!!!!

--- 2020-10-30 albatros_paper.tex
@@
 
-As a qualitative illustration of the sky signal repeatability,
-\autoref{Fig:albatros2_phase} shows the phases of the cross-spectra
-binned in local sidereal time.  About 372 hours of data are averaged
-into this plot, and no RFI excision has been performed.  A more
-detailed analysis of signal repeatability will be presented in a
-future paper, but the high signal-to-noise fringe pattern, which is
+We can estimate the instrumental gain stability by comparing the total
+power between the different days shown in
+\autoref{Fig:albatros2_waterfalls}.  We find that the RMS gain
+fluctuations between 30 and 40~MHz (where the Galactic signal peaks in
+the data) are less than 1\%.  The typical noise on $\sim$3-second time
+scales is roughly 0.04\% of the power.  The low noise suggests that
+relative calibration, using autospectra recorded by each autonomous
+station, can yield sub-percent accuracy.  (Absolute calibration in the
+future will be derived by comparing autospectra against \prizm, which
+is co-located and absolutely calibrated, or the Global Sky Model.)  As
+a qualitative illustration of the sky signal repeatability on smaller
+scales, \autoref{Fig:albatros2_phase} shows the phases of the
+cross-spectra binned in local sidereal time.  About 372 hours of data
+are averaged into this plot, and no RFI excision has been performed.
+A more detailed analysis of signal repeatability will be presented in
+a future paper, but the high signal-to-noise fringe pattern, which is
 even visible slightly below $\sim10$~MHz, demonstrates the proof of
@@
   \begin{center}
-    \includegraphics[width=\linewidth]{Figures/baseband_direct_phase_compare.png}
+    \includegraphics[width=0.9\linewidth]{Figures/baseband_direct_phase_compare.png}
     \caption{Phases from the cross-correlation between two orthogonal
